### 2024-02-13 outputs/paper/paper.qmd
Update Paper

---
title: "Harmful Anti-Foreign Sentiments based on Concern for Competition Should be Recognized and Addressed"
author: "Jayden Jung, Finn Korol, Sofia Sellitto"
thanks: "Code and data are available at: https://github.com/jj-andj/mate-comp-hate ; Replication on Social Science Reproduction platform available at: https://doi.org/10.48152/ssrp-qg85-cb34"
date: "February 17, 2023"
date-format: long
format: 
  pdf: 
    include-in-header: 
      text: |
        \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
    documentclass: article
    geometry: margin = 1in
    abstract: "Immigration and asylum-seeking are common topics of discussion in our globalized world, about which many Westerners hold opinions due to certain personal justifications. This paper replicates data analysis of the perceptions of non-immigrant German males towards refugees in municipalities where males overpopulate females. We apply secondary research regarding Canadian rates of immigration and gender imbalances in Alberta and raise concerns regarding the possibly generalizable nature of the findings in Germany. As this issue specifically affects minority groups experiencing prejudice, we place great emphasis on the weight of this discussion and call for future investigations of this field to inform policies and initiatives to address racism and hate crimes."
    number-sections: true
output: 
  bookdown::pdf_document2
toc: false
fig_caption: yes
nocite: '@*'
bibliography: references.bib
---

```{r setup}
#| echo: false
#| message: false
#| warning: false
# install.packages('readr')
# install.packages('here')
# install.packages("readstata13")  #  readstata13_0.9.2
# install.packages("MASS") # MASS_7.3-51.6  
# install.packages("sandwich")  # sandwich_2.5-1 
# install.packages("lmtest") # lmtest_0.9-37 
# install.packages("pBrackets") # pBrackets_1.0  
# install.packages("dplyr") 
# install.packages("tidyverse")
# install.packages("list)
# install.packages("knitr")
# install.packages("kableExtra")

library(readr) # read_csv
library(here) # here
library(readstata13) #  readstata13_0.9.2
library(MASS) # MASS_7.3-51.6  
library(sandwich)  # sandwich_2.5-1 
library(lmtest) # lmtest_0.9-37  
library(dplyr)
library(tidyverse)
library(jtools)
library(huxtable)
library(list)
library(knitr)
library(kableExtra)
```

# Introduction

In Canada, hate crimes based on race and ethnicity increased by 80% in 2020, with the highest number of incidents targeting black individuals, followed by east and southeast Asians, indigenous individuals, and the lowest number of victims being South Asian individuals [@moreau_wang_2022]. Seeing that Canada is one of the most diverse countries in the world, welcoming 405,999 permanent immigrants in 2021 [@government_of_canada_2022] and 130,125 refugees in 2020 [@macrotrends], these statistics concerning the increase of hate crimes pose a real and visceral threat to a large proportion of Canadian residents.

There are many factors that contribute to the increase in hate crimes in Canada. However, with the rise of far-right discourse in the United States, anti-immigrant and anti-refugee rhetoric is becoming more prevalent in Canada. These negative attitudes and actions towards immigrants, refugees, and marginalized individuals can be the result of various structural and personal factors, including increased competition in the job and housing markets, resource scarcity, misguided beliefs about crime rates, illness, welfare dependency, and fears of losing national identity. Despite this, one factor that has received little attention until recently is the impact of mate competition in dating and marriage markets on anti-refugee sentiments. A [-@main_paper] paper by Dancygier, Egami, Jamal, and Rischke published in the American Journal of Political Science delves into this potentially important and often-overlooked fusion of social science with ecology.

In studying the opinions of German males living in municipalities with excess male populations, they find that a portion of non-immigrant German men hold the belief that refugees pose a threat to their ability to pursue German women [@main_paper]. The study population is primarily non-immigrant German males in highly male populated municipalities. The estimand which we intend to replicate is the effect of mate competition on anti-refugee sentiments. Their finding suggests that hate crimes increase where non-immigrant German men are disadvantaged in their local dating markets [@main_paper]. Using ecological evidence and originally curated survey data, the paper concludes that competition in dating and marriage markets where men outnumber women increases anti-refugee sentiments and violence [@main_paper].

Our paper will follow a reproduction of Dancygier, Egami, Jamal, and Rischke's findings and apply a Canadian-facing lens to discuss its implications on local Canadian populations and increased anti-refugee/ immigrant sentiments and violence. Our paper seeks to replicate their two following research claims, (1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats and (2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians. Our reproduction was conducted using the statistical programming language R [@citeR]. To further enable our analysis we employed the use of the following packages: readr [@readr], here [@here], readstata13 [@readstata13], MASS [@MASS], sandwich [@sandwich], lmtest [@lmtest], dplyr [@dplyr], tidyverse [@tidyverse], jtools [@jtools], huxtable [@huxtable], list [@list], knitr [@knitr] and kableExtra [@kableExtra].

We begin our paper with a discussion of the data source, the methodologies employed in the original paper and a review of the variables used for our reproduction. We will then conduct a reproduction of select results to verify their findings and improve upon their accessibility. Our paper will conclude with a discussion of our findings where we conduct a case study to apply our findings to Alberta, Canada's only Province with a greater population of males, a discussion of ethical biases, limitations and a push for future research.

# Data

## Source

The paper used for replication is from the American Journal of Political Science which follows a discussion on the correlation of perceived mate competition and its contributions to anti-refugee sentiments and higher crime rates in Germany [@main_paper]. Our reproduction seeks to address two findings made from the original paper and apply a Canadian facing lens.

Their two claims are as follows: (1) Are non-immigrant German men who live in municipalities with excess male populations more likely to perceive refugees as threats? (2) Are non-immigrant German men who perceive mate competition more likely to support violence as the only means to gain the attention of German politicians?

## Methodology

This paper will replicate the survey data that was originally collected for the [-@main_paper] paper by Dancygier, Egami, Jamal, and Rischkes, as previously mentioned. Using the online survey platform "Respondi", they conduct 4 waves of surveys which spanned from September 2016 to December 2017 [@main_paper]. The researchers suggest that the anonymity provided by the online survey platform resulted in respondents answering more truthfully. [@main_paper]. To mitigate potential biases, the researchers employed list experiments in Waves 1 and 2, and in Wave 2, they randomly assigned 50% of the sample to either a control or treatment group. The treatment group was exposed to statements concerning their agreement with using violence against refugees as a means to get the attention of German politicians. However, no evidence was found to suggest that respondents were concealing their support for hate crimes when comparing the means of the control and treatment groups [@main_paper].

## Features

The original survey data assessed participants on 53 variables, being representative of gender, age and state. The range of recorded age data from the survey occurs from 19-89 years old. Age was then categorized by group which is as follows: 18-29, 30-39, 30-49, 50-59, and 60 and older. Both male and female participants took part in the survey, but females were only involved in Waves 2 and 4 of surveys. The survey was distributed across 16 German states. Our reproduction, however, included removing variables that were not utilized in our final reproduction analysis and included only the necessary Waves 2 and 4. As a part of our reproduction, we also simplified the names of variables to make them easier to work with. From the original survey data, each variable correlates with a survey question asked to participants. To discuss the variables used in our reproduction we have grouped them by category way and have listed each variable below. Some survey questions are presented, and have been reworded slightly for consistency and clarity.

[Socio-demographics]{.underline}

-   Age Group
-   Gender
-   State
-   German Citizen
-   Marital Status
-   Relationship status, single
-   Religious Affiliation
-   Education
-   Occupation
-   Income
-   Household Size
-   Subjective Social Status
-   Excess males: The proportion of males to females by states by dividing the number of women by men aged 14 and 44 for each municipality 
-   Politics: left and right-leaning
-   Politics: affiliated parties

[Mate Competition: using a scale (1-4) to indicate agreement or disagreement]{.underline}

-   The influx of male refugees make it difficult for non-immigrant German men to find female partners

[Job Competition: using a scale of agree or disagree]{.underline}

-   The inflow of young male refugees makes it more difficult for young non-immigrant German men to find work/ jobs

[Life Satisfaction: scale of 0-10]{.underline}

-   Rank your satisfaction with life

[Encountering Refugees]{.underline}

-   How many KM is the closest refugee reception center from your home?
-   How many refugees do you believe have settled in your municipality in the last year?
-   In the last month, how many refugees have you encountered in the following locations? (on the street, on public transport or in parks, in stores, in refugee reception centres or hostels, school, work)

[Attitudes Toward Refugees (national and local scale): using a scale of agree or disagree]{.underline}

-   Violence is sometimes the only means that citizens have to get the attention of German politicians 
-   Attitudes towards Muslims
-   Hostility against refugees is justified
-   Politicians should condemn attacks against refugees
-   Racist violence is defensible if it leads to fewer refugees settling in a town
-   Attacks against refugee homes are sometimes necessary to make garner the attention of politicians
-   Refugees are integrating well into Germany
-   German refugees should be entitled to German citizenship
-   The number of refugees should be reduced
-   Refugees are receiving more than non-immigrant Germans
-   Refugees should give up their culture to adopt that of Germany
-   Refugees are good for the economy
-   Refugees increase crime
-   Increased refugees increase the risk of terrorism
-   Additional refugees in your town will increase the influence of Islam (local)
-   Additional refugees in your town will be a challenge for local schools (local)
-   Additional refugees in your town will increase competition for housing (local)
-   Additional refugees in your town will change the way of life in your town (local)

[Operational category]{.underline}

-   Experiment lists
-   Treatment lists
-   Outcome lists
-   Waves: out of 4

# Results

Data from Wave 4 of surveys were used to show correlation between someone answering that they perceive refugees as a threat to finding a romantic partner and that person's gender, age, and their municipality's gender ratio. We reconstructed the portion of the survey data used for this analysis in @fig-excess, changing the presentation to a comparative bar chart where we can directly, visually compare different categories' response patterns along a consistent y-axis.

@main_paper provides groupings for the varying elements that we wanted to distinguish and compare. The three age/gender groups compared are: (1) All (men and women of all ages), (2) Men between ages of 18-44, and (3) Men of "mating age" (30-40), making them of an age that is most commonly seen as the range that people seek to find a partner and "settle down." There were also 3 different groupings for categorizing a municipality's gender ratio which are referred to as "terciles." Gender ratio was calculated by dividing the male population by the female population of a given municipality [@main_paper]. Within the survey data, each response had a value for that respondents' municipality's gender ratio. @tbl-terc shows the exact value of ratio used to divide groupings into 1st, 2nd, and 3rd terciles.

Returning to @fig-excess, we immediately notice that the highest rate of perceiving refugees as threats, over 46%, is found in mating-aged men living in municipalities with relatively high male-to-female ratio (at least 1.12 men per 1 woman). Next is Men ages 18-44 in the same tercile of municipalities at around 37%. This is in stark contrast to the All group which includes men and women of all ages, where the proportion is lowest in the 1st tercile at around 17%, and highest at the 3rd tercile with 23%. There is one exception of Men 30-40 in the 1st tercile, but otherwise, Men are consistently more likely to perceive refugees as threats to mating than the general population. This jumps greatly the higher the male-to-female ratio is in their own town; the rate in Men 30-40 is almost tripled in the 3rd tercile than the 1st, and about 1.8 times more than the 2nd.

In analyzing @fig-excess, we can recognize that the combination of a person being a man, especially between the ages of 30-40, and living in a municipality that has about 9 men per 8 women does seem to predict a higher rate of that person believing that refugees are negatively affecting their chance at finding a romantic partner. To confirm, it is not necessarily true that these respondents are living in an area with disproportionately more refugee men, but men in general. Yet, there being more men at all in their town might lead them to project blame onto refugees when presented with a question regarding the topic.

\renewcommand{\arraystretch}{2}

```{r}
#| label: tbl-terc
#| tbl-cap: "Dividing respondents into three terciles by their municipality's gender ratio"
#| echo: false
#| message: false
#| warning: false

terc_table <- data.frame(
  tercile = c("1st Tercile", "2nd Tercile", "3rd Tercile"),
  ratio = c("Less than 1.04", 
               "More than 1.04, Less than 1.12",
               "More than 1.12")
)

terc_table %>% 
  knitr::kable(booktabs = T, col.names = c("Tercile", "Municipality's Male to Female Ratio")) %>% 
  column_spec(1, bold = T, width = "10em") %>%
  column_spec(2, width = "20em")
```

```{r}
#| label: fig-excess
#| fig-cap: "Proportion of respondents who see refugees as a mating threat by age group and tercile"
#| echo: false
#| message: false
#| warning: false

survey_data <- read_csv(here::here("inputs/data/survey_clean.csv"))

# Subset of people from wave 4 and select needed columns
s_exc <- survey_data[survey_data$wave == 4 ,]
s_exc <- select(s_exc, c(gender, age, mate_compete, excess_males))

# Add indicator if respondent agrees/strongly agrees that refugees are mate threats
s_exc$matecomp <- ifelse(s_exc$mate_compete >= 3, 1, 0)

# Add value for mate competition tercile
s_exc$terc <- ifelse(s_exc$excess_males < 1.04, "1st Tercile", ifelse(s_exc$excess_males < 1.12, "2nd Tercile", "3rd Tercile"))

# Create age groups for all people, men bw 18-44, and men bw 30-40
s_exc$agroup <- "All, Men & Women"

s_exc2 <- s_exc[s_exc$gender == "Male" & s_exc$age <= 44 & s_exc$age >= 18,]
s_exc2$agroup <- "Male 18-44"

s_exc3 <- s_exc[s_exc$gender == "Male" & s_exc$age <= 40 & s_exc$age >= 30,]
s_exc3$agroup <- "Male 30-40"

# Combining data frame back together
s_excm <- rbind(s_exc, s_exc2)
s_exct <- rbind(s_excm, s_exc3)

# Calculating proportion of respondents who agree or strongly agree by tercile
mean_all <- tapply(s_exc$matecomp, s_exc$terc, mean)
mean_2 <- tapply(s_exc2$matecomp, s_exc2$terc, mean)
mean_3 <- tapply(s_exc3$matecomp, s_exc3$terc, mean)

# Setting up data frame for plotting
s1 <- data.frame(c(mean_all))
colnames(s1) <- c("mean")
s2 <- data.frame(c(mean_2))
colnames(s2) <- c("mean")
s3 <- data.frame(c(mean_3))
colnames(s3) <- c("mean")

s_m <- rbind(s1, s2)
s_tot <- rbind(s_m, s3)

rownames(s_tot) <- NULL

s_tot$grp <- rep(c("All, Men & Women","Men 18-44","Men 30-40"),each=3)
s_tot$terc <- rep(c("1st Tercile","2nd Tercile","3rd Tercile"),times=3)

# Plotting
wrapper <- function(x, ...) 
{paste(strwrap(x, ...), collapse = "\n")}

s_tot %>% 
  ggplot(aes(x=terc, y=mean, group=grp, fill=grp)) +
  geom_col(position = "dodge", colour = "black")+
  labs(x="Terciles of Excess Male Rate", fill = "Group") +
  labs(y = wrapper("Proportion perceiving refugees as mate competition", width = 30)) +
  theme_minimal() +
  theme(legend.position="bottom") +
  theme(text=element_text(size=11, family="serif")) +
  ggtitle(wrapper("Nearly half of mating-aged men living in excess male areas perceive refugees as a threat to finding a partner", width =60)) +
  theme(plot.title = element_text(face = "bold"))
```

```{r}
#| label: fig-collection
#| fig-cap: "00000000000000000000000000000000000000000000000000000000000000000000000000"
#| echo: false
#| message: false
#| warning: false

rm(list=ls())
setwd("/cloud/project/raw/data") #set your directory
options("scipen"=100, "digits"=8) #set digits
getwd()

ipak <- function(pkg){  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
if(length(new.pkg)) install.packages(new.pkg, dependencies = TRUE)
sapply(pkg, require, character.only = TRUE)
}

packages <- c("readxl", "haven", "psych", "dplyr", "DescTools", "broom", "cowplot",
              "pwr", "esc", "metaSEM", "metafor", "metaviz", "PerformanceAnalytics", 
              "ggplot2", "ggpubr", "wesanderson", "stringr", "dotwhisker") 
ipak(packages)

dat <- read_excel("/cloud/project/raw/data/02-metaanalysis-data.xlsx", sheet = "Data", 
                  col_names = TRUE, skip = 3)

### dataframe of studies
dat_studies <- dat[c(1:87)] #studies.
dat_studies <- group_by(dat_studies, ID_RS) %>% slice(1)
sum(dat_studies$ESS, na.rm = TRUE) #number of unique respondents

### dataframe of reports
dat_reports <- dat[c(1:87)] #reports/publications.
dat_reports <- group_by(dat_reports, ID_R) %>% slice(1)

### set wished layout settings
mytheme <- theme(plot.title = element_text(face = "bold", size = (22), colour = "black"), 
                 axis.text = element_text(size = (18), colour = "black"),
                 axis.ticks.length = unit(0.5, "cm"),
                 axis.title.y = element_text(size = (22), colour = "black"),
                 axis.title.x = element_text(size = (22), colour = "white"))

# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
###### A. DESCRIPTIVES: THE FIELD OF EMPIRICAL TERRORISM STUDIES ######
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ #

## mean ES's per report (reported in footnote 6)
format(round(psych::describe(aggregate(Correlation ~ ID_R, data = dat, FUN = length)),3), nsmall=3)

StudyYear <- ggplot(dat_studies, aes(x=StudyYear)) + 
  geom_histogram(binwidth=1,
                 color="#000000", fill="#939598") +
  labs(x="to fill some space", y = "", title = "Year of Data Collection") +
  scale_y_continuous(breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45)) +
  scale_x_continuous(breaks = c(1985,1990,1995,2000,2005,2010, 2015,2020)) +
  theme_classic() #histogram year of study 
StudyYear <- StudyYear + geom_vline(xintercept=2001, linetype="dashed", size = 1) #add 9/11 line
StudyYear <- StudyYear + geom_vline(xintercept=2004, linetype="dashed", size = 1) #add line
StudyYear <- StudyYear + geom_vline(xintercept=2015, linetype="dashed", size = 1) #add ISIS line
StudyYear <- StudyYear + geom_label(data = dat_studies, 
                                    aes(x=2001, y=27, label = "9/11"),
                                    size=8) #add 9/11 label
StudyYear <- StudyYear + geom_label(data = dat_studies, 
                                    aes(x=2007, y=35, label = "Madrid & \n Israel-Palestine"),
                                    size=6) #add label
StudyYear <- StudyYear + geom_label(data = dat_studies, 
                                    aes(x=2014, y=44, label = "IS Attacks"),
                                    size=8) #add ISIS label
StudyYear <- StudyYear + mytheme

# year of publication

describe(dat_reports$Year) 
# Figure 2B
PubYear <- ggplot(dat_reports, aes(x=Year)) + 
  geom_histogram(binwidth=1, 
                 color="#000000", fill="#939598") +
  labs(title ="Year of Publication", x = "to fill some space", y = "") +
  scale_y_continuous(breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45)) +
  scale_x_continuous(breaks = c(1985,1990,1995,2000,2005,2010, 2015,2020)) +
  theme_classic() #histogram year of study 
PubYear <- PubYear + geom_vline(xintercept=2001, linetype="dashed", size = 1) #add 9/11 line
PubYear <- PubYear + geom_vline(xintercept=2015, linetype="dashed", size = 1) #add ISIS France line
PubYear <- PubYear + geom_label(data = dat_reports,
                                aes(x=2001, y=27, label = "9/11"),
                                size=8) #add 9/11 label
PubYear <- PubYear + geom_label(data = dat_reports, 
                                aes(x=2014, y=44, label = "IS Attacks"),
                                size=8) #add ISIS label
PubYear <- PubYear + mytheme

####### Terrorism measures, incl. cognitive and affective reactions ######

# IV measurements used 
summary(as.factor(dat$IV_Code))

#wrangling
dat$TerrorMeasure[dat$IV_Code==1] <- "Acts of violence"
dat$TerrorMeasure[dat$IV_Code==2] <- "Acts of violence"
dat$TerrorMeasure[dat$IV_Code==3] <- "Threat"
dat$TerrorMeasure[dat$IV_Code==4] <- "Threat"
dat$TerrorMeasure[dat$IV_Code==5] <- "Other"
dat$TerrorMeasure[dat$IV_Code==6] <- "Reported exposure"
dat$TerrorMeasure[dat$IV_Code==7] <- "Reported exposure"
dat$TerrorMeasure[dat$IV_Code==8] <- "Reported exposure"
dat$TerrorMeasure[dat$IV_Code==9] <- "Threat"
dat$TerrorMeasure[dat$IV_Code==10] <- "Threat"
dat$TerrorMeasure[dat$IV_Code==11] <- "Fear"
dat$TerrorMeasure[dat$IV_Code==12] <- "Anger"
dat$TerrorMeasure[dat$IV_Code==13] <- "Other"
dat$TerrorMeasure[dat$IV_Code==14] <- "Other"
dat$TerrorMeasure[dat$IV_Code==15] <- "Other"
dat$TerrorMeasure[dat$IV_Code==16] <- "Other"

dat$TerrorMeasure <- as.factor(dat$TerrorMeasure)
table(dat$TerrorMeasure)
prop.table(table(dat$TerrorMeasure))
table(dat$ExactAttack) #which attacks are studied?
prop.table(table(dat$ExactAttack)) #which attacks are studied?

#visualization: Figure 2C
tmdat <- data.frame(prop.table(table(dat$TerrorMeasure)))
TerrorMeasures <- ggplot(tmdat, aes(x = reorder(Var1, -Freq), y = Freq)) +
  geom_bar(stat="identity", width=0.7,
           color="#000000", fill="#939598") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  scale_y_continuous(labels = scales::percent,
                     limits = c(0,.6),
                     breaks = c(0,.1,.2,.3,.4,.5,.6)) +
  labs(title = "Terrorism Measures", x="", y = "") +
  theme_classic() 
TerrorMeasures <- TerrorMeasures + mytheme

# type of terrorism
summary(as.factor(dat$Type))

#wrangling
dat$TerrorType[dat$Type==0] <- "No ideology"
dat$TerrorType[dat$Type==1] <- "Islamist"
dat$TerrorType[dat$Type==2] <- "Extreme right"
dat$TerrorType[dat$Type==3] <- "Other"
dat$TerrorType[dat$Type==4] <- "Other"
dat$TerrorType[dat$Type==5] <- "State terror"
dat$TerrorType[dat$Type==6] <- "Other"
dat$TerrorType <- as.factor(dat$TerrorType)
summary(dat$TerrorType)
prop.table(table(dat$TerrorType))

#visualization: Figure 2D
ttdat <- data.frame(prop.table(table(dat$TerrorType)))
TerrorType <- ggplot(ttdat, aes(x = reorder(Var1, -Freq), y = Freq)) +
  geom_bar(stat="identity", width=0.7,
           color="#000000", fill="#939598") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  scale_y_continuous(labels = scales::percent,
                     breaks = c(0,.1,.2,.3,.4,.5,.6)) +
  labs(title = "Type of Terrorism", x = "", y = "") +
  theme_classic() 
TerrorType <- TerrorType + mytheme

jpeg("Figures/Fig2.jpeg", width = 15, height = 16, units = 'in', res = 300)
ggarrange(StudyYear, PubYear, 
          TerrorMeasures, TerrorType,
          labels = c("(A)", "(B)", "(C)", "(D)"),
          font.label = list(size = 22, color = "black"),
          ncol = 2, nrow = 2) #arrange all plots
dev.off() #safe picture in high resolution.
```

```{r}
#| label: fig-collection
#| fig-cap: "000000000000000000000000000000000000000000000000000000000000"
#| echo: false
#| message: false
#| warning: false

# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
######## B. META-ANALYSIS: for each of the hypotheses ######## 
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ #

# Data preparation: Split dataset in 3 based on outcome type
# 1) outgroup dataset
dat_outgroup <- dat[dat$PA_Category == 10 |
                      dat$PA_Category == 99, ]
length(unique(dat_outgroup$ID_R))#number of manuscripts (N_j)
# 2) conservative shift dataset
dat_conservatism <- dat[dat$PA_Category == 5 |
                          dat$PA_Category == 6 |
                          dat$PA_Category == 7 |
                          dat$PA_Category == 8 |
                          dat$PA_Category == 9 |
                          dat$PA_Category == 11, ]
length(unique(dat_conservatism$ID_R))#number of manuscripts (N_j)
# 3) rally-around-the-flag dataset
dat_rally <- dat[dat$PA_Category == 1 |
                   dat$PA_Category == 2 |
                   dat$PA_Category == 3 |
                   dat$PA_Category == 4, ]
length(unique(dat_rally$ID_R))#number of manuscripts (N_j)
# double check (total number of effect sizes; N_k)
count(dat_outgroup) + count(dat_conservatism) + count(dat_rally)

##### 1. Fit empty 3-level model using the meta3 function #####

### To replicate Table 2: call summary() function for each of outcome cluster
      ## coef(model...)[1] = Fishers' Z correlation coefficients (Zr)
### To replicate the correlation coefficients mentioned in the text, 
### call the FisherZinv() function for each outcome cluster.

# Outgroup hostility (Table 2)
set.seed(1234)
model_og_LBCI <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
                       data = dat_outgroup, 
                       I2=c("I2q", "ICC"),
                       intervals.type = "LB",
                       model.name = "3 level outgroup LB")
summary(model_og_LBCI)#results presented in Table 2, as well as
#throughout the Supplementary Information (esp. Table B.3).
FisherZInv(coef(model_og_LBCI)[1])#rho reported in text

# Conservative shift (Table 2)
set.seed(1234)
model_cs_LBCI <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
                       data = dat_conservatism, 
                       I2=c("I2q", "ICC"),
                       intervals.type = "LB",
                       model.name = "3 level conservatism LB")
summary(model_cs_LBCI)#results presented in Table 2, as well as
#throughout the Supplementary Information (esp. Table B.3).
FisherZInv(coef(model_cs_LBCI)[1])#rho reported in text

# Rally-around-the-flag (Table 2)
set.seed(1234)
model_rf_LBCI <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
                       data = dat_rally, 
                       I2=c("I2q", "ICC"),
                       intervals.type = "LB",
                       model.name = "3 level rally LB")
summary(model_rf_LBCI)#results presented in Table 2, as well as
#throughout the Supplementary Information (esp. Table B.3).
FisherZInv(coef(model_rf_LBCI)[1])#rho reported in text

## Substantive interpretation --------------------------------------------------
## i.e., comparison to 2016 ANES Feeling Thermometers
anes2016 <- read_dta(file = "/cloud/project/raw/data/anes_timeseries_2016.dta")
#select variables to summarize
anes2016 <- anes2016 %>%
  select(immterm = V162313, 
         reptherm = V161096) 
#format(round(psych::describe(anes2016),3), nsmall=3): counts NA's
#recode NA's (!)
anes2016$immterm <- ifelse(anes2016$immterm %in% -9:-1, NA, 
                           identity(anes2016$immterm)) 
anes2016$reptherm <- ifelse(anes2016$reptherm %in% -99:-1, NA, 
                            identity(anes2016$reptherm))
#find correct SDs to use in calculations based on Paluck et al. (2021)
format(round(psych::describe(anes2016),3), nsmall=3) 
#the effect of terror on the feeling therm. toward immigrants. 6.9
cohens_d(r = FisherZInv(coef(model_og_LBCI)[1]))*27.285 
#the effect of terror on the feeling therm. toward Rep. party: 7.2
cohens_d(r = FisherZInv(coef(model_cs_LBCI)[1]))*27.330

## Practical implication -------------------------------------------------------
## i.e., what sample size is recommended based on this meta-analysis?
# Outgroup hostility
pwr.r.test(r = FisherZInv(coef(model_og_LBCI)[1]), sig.level = 0.05, power = 0.8) 
# Conservative shift
pwr.r.test(r = FisherZInv(coef(model_cs_LBCI)[1]), sig.level = 0.05, power = 0.8) 
# Rally-around-the-flag
pwr.r.test(r = FisherZInv(coef(model_rf_LBCI)[1]), sig.level = 0.05, power = 0.8)

##### 2. Test variance components #####

### Note: These results are briefly mentioned in footnote 13, but 
### full results are discussed and presented in SI B.2.3.

# Outgroup hostility

#tau^2_3=0 (reported in Table B.2)
set.seed(1234)
model_og_t3 <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
                      data = dat_outgroup, 
                      RE3.constraints = 0, # constraining between-study level
                      model.name = "Tau2_3 eq 0",
                      intervals.type = "LB")
summary(model_og_t3)#this equals a conventional random-effects model
anova(model_og_LBCI, model_og_t3)

#tau^2_2=0 (reported in Table B.2)
set.seed(1234)
model_og_t2 <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
                     data = dat_outgroup,
                     RE2.constraints = 0, # constraining within-study level
                     model.name = "Tau2_2 eq 0",
                     intervals.type = "LB")
summary(model_og_t2)
anova(model_og_LBCI, model_og_t2)

# Conservative shift

#tau^2_3=0 (reported in Table B.2)
set.seed(1234)
model_cs_t3 <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
                     data = dat_conservatism, 
                     RE3.constraints = 0, # constraining between-study level
                     model.name = "Tau2_3 eq 0",
                     intervals.type = "LB")
summary(model_cs_t3)
anova(model_cs_LBCI, model_cs_t3)

#tau^2_2=0 (reported in Table B.2)
set.seed(1234)
model_cs_t2 <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
                     data = dat_conservatism,
                     RE2.constraints = 0, # constraining within-study level
                     model.name = "Tau2_2 eq 0",
                     intervals.type = "LB")
summary(model_cs_t2)
anova(model_cs_LBCI, model_cs_t2)

# Rally-around-the-flag

#tau^2_3=0 (reported in Table B.2)
set.seed(1234)
model_rf_t3 <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
                     data = dat_rally, 
                     RE3.constraints = 0, # constraining between-study level
                     model.name = "Tau2_3 eq 0",
                     intervals.type = "LB")
summary(model_rf_t3)
anova(model_rf_LBCI, model_rf_t3)

#tau^2_2=0 (reported in Table B.2)
set.seed(1234)
model_rf_t2 <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
                     data = dat_rally,
                     RE2.constraints = 0, # constraining within-study level
                     model.name = "Tau2_2 eq 0",
                     intervals.type = "LB")
summary(model_rf_t2)
anova(model_rf_LBCI, model_rf_t2)

```

\clearpage

```{r}
#| label: tbl-stmt
#| tbl-cap: "Statements used for surveying respondents"
#| echo: false
#| message: false
#| warning: false

stmt_table <- data.frame(
  type = c("Only means", "Message", "Justified", "Prevent", "Condemn"),
  question = c("When it comes to the refugee problem, violence is sometimes the only means that citizens have to get the attention of German politicians.", 
               "Attacks against refugee homes are sometimes necessary to make it clear to politicians that we have a refugee problem.",
               "Hostility against refugees is sometimes justified, even when it ends up in violence.",
               "Xenophobic acts of violence are defensible if they result in fewer refugees settling in town.", 
               "Politicians should condemn attacks against refugees more forcefully. (For this statement, the results were reversed such that we are looking at respondents who Disagreed or Strongly Disagreed)")
)

stmt_table %>% 
  knitr::kable(booktabs = T, col.names = c("Type", "Statement")) %>% 
  column_spec(1, bold = T, width = "7em") %>%
  column_spec(2, width = "35em")
```

Shifting to the topic of hate crime and anti-refugee sentiments, another aspect of the survey asked the respondent to share whether they agreed or disagreed with varying statements that conveyed pro-hate crime or anti-refugee opinions. The exact statements the respondents were given can be seen in @tbl-stmt. For discussion, the statements have been shortened to "Only Means", "Message", "Justified", "Prevent", and "Condemn". The data set recorded whether respondents agreed with these statements. The last, Condemn, as seen in @tbl-stmt, is clearly an anti-hate crime statement. Thus, answers for this question were weight inversely, such that the data measures who disagreed with it.

The visualization of what proportion of respondents agreed with given statements in the 2nd wave of surveys can be seen in @fig-statements. For unstated reasons, @main_paper excluded "Prevent" in their analysis despite having the data available to plot and analyze response rate for the statement. As evident, we have included it. We excluded the measurement for the control group of respondents who answered the Only Means statement in a list-format (as discussed in Methodology). This was originally intended to notice whether respondents may hide their true feelings about supporting violence against refugees if asked outright compared to if they were to be presented with it more passively in a list. As @main_paper found, there was no significant difference and this concern was proven to not have actually affected the regular survey data. Thus, we opted to only showcase the regular survey response rates.

@fig-statements, shows that, for the first three statements (Only Means, Message, and Justified), between 17% and 20% of respondents agreed with the prompt. 1 in 5 respondents specifically agreed that "hostility against refugees" that "leads to violence" can be justified in certain cases. The highest rate of agreement, though comes to the inverse of Condemn. Over 25%, more than 1 in 4 respondents, disagreed that there was a need for public figures to condemn hate crimes. This may point to a chunk of respondents not necessarily agreeing or supporting hate crime but not perceiving it as a major issue, and thus not seeing it as something that needs to be condemned. The other stand-out is how relatively low the agreement rate is for Prevent, being barely over 13%, 4% lower than the second lowest, Message. This may be due to the fact that Prevent is the only statement that pointedly uses the term "Xenophobic" to identify the intention of these violent acts, while the other statements use general language that don't assign an intrinsic moral value in their description of the violent acts. A respondent may not see a problem with any of the other statements, read Prevent, and simply disagree that their opinion is xenophobic, and thus disagree with it. It may have yielded more similar results to the other statements if it had been reworded to "Acts of violence against refugees".

Analysis of @fig-excess confirms that there is a generally alarmingly high rate of support for hate-crime and anti-refugee statements, though there may be nuance in certain respondents not seeing these hate crimes as a problem or being racially motivated. These results supported the creation of @tbl-hatemodel discussed below.

```{r}
#| label: fig-statements
#| fig-cap: "Proportion of respondents who agree with varying hate crime support statements"
#| echo: false
#| message: false
#| warning: false

# Set up, filter for wave 2 and select needed columns
survey_data <- read_csv(here::here("inputs/data/survey_clean.csv"))

s_stmt <- survey_data[survey_data$wave == 2,]
s_stmt <- select(s_stmt, c(only_means, message, prevent, condemn, justified))

# Add column with value for people agreeing or strongly agreeing
s_stmt$meansp <- ifelse(s_stmt$only_means >= 3, 1, 0)
s_stmt$msgp <- ifelse(s_stmt$message >= 3, 1, 0)
s_stmt$justp <- ifelse(s_stmt$justified >= 3, 1, 0)
s_stmt$prevp <- ifelse(s_stmt$prevent >= 3, 1, 0)
s_stmt$conp <- ifelse(s_stmt$condemn >= 3, 1, 0)

# Calculate proportion of respondents to agree/strongly agree with given statement
s_stmtmeans <- na.omit(s_stmt$meansp)
meansp <- mean(s_stmtmeans)

msgp <- mean(s_stmt$msgp)
justp <- mean(s_stmt$justp)
prevp <- mean(s_stmt$prevp)
conp <- mean(s_stmt$conp)

# Data frame prepped for plotting
s_stmt_p <- data.frame(c(meansp, msgp, justp, prevp, conp))
s_stmt_p$stmt <- c("Only means", "Message", "Justified", "Prevent", "Condemn")

colnames(s_stmt_p) <- c("pptn", "stmt")

# Plotting
wrapper <- function(x, ...) 
{paste(strwrap(x, ...), collapse = "\n")}

s_stmt_p %>% 
  ggplot(aes(x=stmt, y=pptn)) +
  geom_col(fill="gray", colour="black") +
  scale_x_discrete(limits = c("Only means", "Message", "Justified", "Prevent", "Condemn")) +
  labs(x="Statement Type") +
  labs(y = wrapper("Proportion of respondents", width = 40)) +
  theme_minimal() +
  theme(text=element_text(size=11, family="serif")) +
  ggtitle(wrapper("13% to 25% of respondents agree with statements supporting or not condemning violence against refugees", width =60)) +
  theme(plot.title = element_text(face = "bold"))

# add note for condemn
```

\renewcommand{\arraystretch}{1.5}

Finally, we reconstructed @main_paper's battery of linear models to predict respondents' sentiments toward refugee-directed hate crime. 6 Models were trained with increasing numbers of factors weighted using Ordinary Least Squares @tbl-hatemodel. The first model used solely mate competition (measured by proportion of excess males). Our models grew in complexity such that the second version was inclusive of job competition and life satisfaction. In the next four models, one at a time, sociodemographic factors, attitudes toward refugees (local first, then national), and last, additional factors (including perceptions of refugee settlements and political groups, and their affiliations) were added. Despite the addition of factors, across all models, the predictive weight of mate competition remains high. Job competition, on the other hand, was introduced in model 2 with larger weight than mate competition, but it rapidly fell off with the introduction of more factors. Life satisfaction's weight remains low across all inclusive models. Increasing R Squared indicates that model fit increases with additional factors in our model. These findings are consistent with @main_paper.

\newpage

\blandscape

```{r}
#| label: tbl-hatemodel
#| tbl-cap: "Tabulated weights of linear regression models 1 through 6 using ordinary least squares. In parentheses are the standard errors. Asterisks denote ranges of p-values as described in the table footer."
#| echo: false
#| message: false
#| warning: false

survey_data <- read_csv(here::here("inputs/data/survey_clean.csv"))

survey_w4 <- survey_data[survey_data$wave == 4,]

lm1 <- lm(only_means ~ mate_compete, data=survey_w4)

lm2 <- lm(only_means ~ mate_compete + job_compete + life_satisfaction, data=survey_w4)

lm3 <- lm(only_means ~ mate_compete + job_compete + life_satisfaction + 
            factor(age_group) +     # age group
            factor(gender) +     # gender 
            factor(state) +     # state  
            factor(citizenship) +    # german citizen
            factor(marital) +    # marital status
            factor(religion) +    # religious affiliation
            eduyrs +    # education
            factor(occupation) +    # main activity
            factor(income) +   # income
            factor(household_size) +   # household size
            factor(self_econ),    # subjective social status
          data=survey_w4)

lm4 <- lm(only_means ~ mate_compete + job_compete + life_satisfaction + 
            factor(age_group) +   # age group
            factor(gender) +   # gender 
            factor(state) +   # state  
            factor(citizenship) +  # german citizen
            factor(marital) +  # marital status
            factor(religion) +  # religious affiliation
            eduyrs +  # education
            factor(occupation) +  # main activity
            factor(income) + # income
            factor(household_size) + # household size
            factor(self_econ) + # subjective social status
            factor(ref_integrating) + # Refugee Index (National-level; Q73) 8 in total
            factor(ref_citizenship) + factor(ref_reduce) + factor(ref_moredone) + factor(ref_cultgiveup) + 
            factor(ref_economy) + factor(ref_crime) + factor(ref_terror),
          data=survey_w4)

lm5 <- lm(only_means ~ mate_compete + job_compete + life_satisfaction + 
            factor(age_group) +      # age group
            factor(gender) +      # gender 
            factor(state) +      # state  
            factor(citizenship) +     # german citizen
            factor(marital) +     # marital status
            factor(religion) +     # religious affiliation
            eduyrs + # education
            factor(occupation) +     # main activity
            factor(income) +    # income
            factor(household_size) +    # household size
            factor(self_econ) +    # subjective social status
            factor(ref_integrating) + # Refugee Index (National-level; Q73) 8 in total
            factor(ref_citizenship) + factor(ref_reduce) + factor(ref_moredone) + factor(ref_cultgiveup) + 
            factor(ref_economy) + factor(ref_crime) + factor(ref_terror) + 
            factor(ref_loc_services) +    # Refugee Index (Local, Q75)
            factor(ref_loc_economy) + factor(ref_loc_crime) + factor(ref_loc_culture) + factor(ref_loc_islam) + 
            factor(ref_loc_schools) + factor(ref_loc_housing) + factor(ref_loc_wayoflife), ## end
          data=survey_w4)

# Add More Variables 
# lrscale  Q21  Left-Right Scale
# afd, Q23  Closeness to AfD
# muslim_ind, afd_ind, contact_ind
# distance_ref Q71. Distance to refugee reception centers
# settle_ref Q72. Settlement of refugees living in area

formula.5 <- 
  as.character("only_means ~ mate_compete + job_compete + 
               life_satisfaction +  factor(age_group) + factor(gender) + 
               factor(state) + factor(citizenship) + factor(marital) + 
               factor(religion) + eduyrs + factor(occupation) + 
               factor(income) + factor(household_size) + factor(self_econ) + 
               factor(ref_integrating) + factor(ref_citizenship) + factor(ref_reduce) + 
               factor(ref_moredone) + factor(ref_cultgiveup) + 
               factor(ref_economy) + factor(ref_crime) + factor(ref_terror)  + 
               factor(ref_loc_services) +  factor(ref_loc_economy) + factor(ref_loc_crime) + 
               factor(ref_loc_culture) + factor(ref_loc_islam) + 
               factor(ref_loc_schools) + factor(ref_loc_housing) + factor(ref_loc_wayoflife)")

formula.6 <- paste(formula.5, "factor(distance_ref) + factor(settle_ref)", 
                   "left_right + afd + muslim_att + afd_att + contact_att", 
                   sep="+", collapse="+")

lm6 <- lm(as.formula(formula.6), data=survey_w4)

table1 <- export_summs(lm1, lm2, lm3, lm4, lm5, lm6, scale = TRUE, number_format = "%.3f", coefs = c('mate competition'='mate_compete', 'job competition'='job_compete', 'life satisfaction'='life_satisfaction')) |>
  set_escape_contents(FALSE) |>
  add_rows(c("sociodemographics ", " ", " ", "X", "X", "X", "X"), after = 7)  |>
  add_rows(c("national attitudes toward refugees", " ", " ", " ", "X", "X", "X"), after = 8) |>
  add_rows(c("local attitudes toward refugees", " ", " ", " ", " ", "X", "X"), after = 9) |>
  add_rows(c("additional controls", " ", " ", " ", " ", " ", "X"), after = 10)

table1

```

\elandscape

```{r, message=FALSE, message=FALSE, echo=FALSE, include=FALSE}
#| label: draft code (not used)
table1 <- export_summs(lm1, lm2, lm3, lm4, lm5, lm6, scale = TRUE, digits = 2, coefs = c('Mate competition'='mate_compete', 'Job competition'='job_compete', 'Life satisfaction'='life_satisfaction'))

table1 <- data.frame(table1)

store1 <- table1[8:9,]
store2 <- table1[10,]
store2 <- store2$names

table1 <- table1[-1,]
table1 <- slice(table1, 1:(n() - 3))

table1[nrow(table1) + 1,] <- c("Sociodemographics", " ", " ", "X", "X", "X", "X")
table1[nrow(table1) + 1,] <- c("National attitudes toward refugees", " ", " ", " ", "X", "X", "X")
table1[nrow(table1) + 1,] <- c("Local attitudes toward refugees", " ", " ", " ", " ", "X", "X")
table1[nrow(table1) + 1,] <- c("Additional controls", " ", " ", " ", " ", " ", "X")

table1t <- rbind(table1, store1)
rownames(table1t) <- NULL
colnames(table1t) <- c("name", "m1", "m2", "m3", "m4", "m5", "m6")

table1t1 <- subset(table1t, select = -c(m4, m5, m6))
table1t2 <- subset(table1t, select = -c(m1, m2, m3))

table1t1 %>% 
  kable(booktabs = T, col.names = c("", "Model 1", "Model 2", "Model 3"), align = "lccc") %>% 
  kable_styling(latex_options="scale_down") %>% 
  row_spec(0,bold=TRUE)

table1t2 %>% 
  kable(booktabs = T, col.names = c("", "Model 4", "Model 5", "Model 6"), align = "lccc") %>% 
  kable_styling(latex_options="scale_down") %>% 
  row_spec(0,bold=TRUE) %>% 
  footnote(general = store2)

```

# Discussion

## Findings

In this paper, we have replicated the results found by Dancygier, Egami, Jamal, and Rischke. Their analysis sought to explore the correlation between perceived mate competition in municipalities with excess males and its contributions to anti-refugee sentiments and higher crime rates in Germany. Our paper has replicated two of their major findings.

(1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats.

(2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians.

By replicating their results, we hope to apply a Canadian-facing lens to gain insights into Canadian dating markets, the geographical distribution of males and females and their potential impacts on anti-refugee sentiments.

## Canadian Relevance: Case Study on Alberta's population ratios, dating markets and anti-refugee sentiments

To investigate the relevance of Dancygier, Egami, Jamal, and Rischke's discoveries in a Canadian context, we will now explore Canada's only Province with a higher ratio of males than females.

Alberta is a Province in Canada with a total population of 4,543,111 individuals. It is the only Canadian Province that is more heavily populated by males, with a male population of 2,282,040 compared to 2,261,071 females [@statista]. Thus having a ratio of approximately 1.01, which is comparable to that of the 1st tercile in Figure 1. This means that there are about 11,000 more men than women residing in this Province. Part of the population gap can be explained by age. Alberta has a primarily young population and we typically see that as populations age they exhibit a higher female population [@edmonton_journal]. Its trades centric economy also attracts young male migrants from across Canada [@edmonton_journal].

Concerning the original paper, Alberta's population growth can be largely attributed to international immigration which has typically brought equal numbers of males and females [@edmonton_journal]. However, according to the 2021 census, 101, 650 more males are single (not married or living common law and never married) than women [@govcan]. Due to Alberta's young population, highly concentrated with men of working age, a comparison can be made to the term 'mating-aged' used in the original paper to describe males facing higher tensions of dating competition. We thus believe that similar conditions for dating and marriage markets can be made between Alberta and the German municipalities of that the 1st Tercile from Figure 1.

While population demographics are comparable between that of Alberta and the 1st tercile of German municipalities in the original paper, it is difficult to suggest that potential competition in Albertan dating and marriage markets correlates to anti-refugee sentiments and violence. However, in addressing Albertan immigrant and refugee statistics we will aim to illustrate how these patterns found in Germany can manifest in the context of Alberta. Based on the 2021-2022 Annual Population Report, Alberta welcomed 12,603 immigrants and 21,434 non-permanent residents, which include refugees [@alberta_2023].

While previous accounts have suggested that immigration has brought an equal number of males and females, it is safe to assume that Alberta is a growing population, subject to a population with a higher concentration of males [@edmonton_journal]. According to a 2018 paper, at the time 6 in 10 Canadians disagreed when asked if immigration levels were too high, with 35% believing that Canada accepts too many immigrants [@globe_mail]. However, sentiments appear less than positive in Alberta, with Albertans expressing harsher attitudes towards immigrants and refugees [@globe_mail]. 48% of Albertans at the time agreed that refugee claims are not filed from real refugees, with 62% stating that immigrants do not adopt Canadian values, about 10% higher than the national average of 51% [@globe_mail]. The Globe and Mail suggest that part of Alberta's higher anti-refugee attitudes can be attributed to its economy and fears of competition.Dancygier, Egami, Jamal, and Rischke  find that in areas where men significantly outnumber women, there are higher levels of anti-refugee hate crimes [@main_paper].

Based on these statistics, we believe that Alberta may experience a similar effect of anti-refugee sentiments in part as a result of increased immigrants/ refugees and competition in a young male-dominated population. However, as stated in their original paper, we call for further research to be conducted on this effect to better understand its implications on non-German countries.

## Ethical Implications

In their paper, Dancygier, Egami, Jamal, and Rischke examine the ethical implication of using experimental methodologies to investigate their research topic. By using descriptive data in the form of surveys they are able to investigate the opinions of non-immigrant German males and their perception of mate competition and its translation to anti-refugee violence. By avoiding experimental trials, they were able to explore their topic without provoking anti-refugee sentiment [@main_paper]. While conducting experimental trials on this topic of research is considered unethical, surveys and questionnaires may have a tendency to give respondents the impression that their opinions are commonly shared or even accurate. By being presented with a platform to express their perception of mate competition and if they agree that violence towards refugees is the only way to garner the attention of German politicians, respondents may feel that their opinions are incorrectly justified. This then has the potential to translate to violence towards German refugees.

## Accounting for Bias

Ethical implications and biases arise naturally when collecting quantitative and qualitative data. In their paper, Dancygier, Egami, Jamal, and Rischke use online survey platforms to assess if Germans living in areas with greater populations of men who experience turmoil in the mating market are more likely to perceive competition between themselves and refugees, moreover, does this ideology predict hate crime support [@main_paper]. The authors attempted to address ethical concerns and statistical biases by utilizing control groups and replicating their study with different samples and polling firms. However, one potential bias that is challenging to control for is the presence of sampling bias [@main_paper]. Sampling bias occurs when participants in a study are not representative of the estimand or the ideal population of interest. One method to control for this bias is simple random sampling, where participants are chosen by chance. Meaning that every individual in the population has an equal chance of being selected. However, in their study, they were unable to utilize simple random sampling. Instead attempted to make their survey results representative by conducting 4 waves of surveys meant to be representative of age, gender and geographical region [@main_paper]. Despite their effort, their survey results may not be entirely representative as individuals who have a strong interest in the subject matter are more likely to participate, meaning they do not reflect the views of all non-immigrant German males [@main_paper].

## Limitations

Being a reproduction, much of our analysis was limited to the original survey circumstances captured in [@main_paper]. Despite the survey being long, it can not be considered to be comprehensive. This prevented us from exploring other relationships in the data. For example, in this German context, it would have been interesting to look into sentiments toward the treatment of communities experiencing genocide during the history of World War 2. Our connection of findings to the Albertan context was also limited by this cultural and geographical separation from our data.

Due to the heteronormative nature of this study's data, our analysis was also not able to be fully representative of the German population as [@main_paper]'s authors described. While this is not to be surprised from an ecological context of mating behaviour, perhaps gay men would have been found to experience anti-refugee sentiment as well as an extension of the mate competition argument.

There were also limitations associated with missing and limited data in our set. For example, in our analysis depicted in @fig-excess, fewer than 300 observations were represented in the oldest age group, which these authors doubted was enough for a meaningful evaluation.

## Future Research

As suggested in their original paper, Dancygier, Egami, Jamal, and Rischke call for future research to investigate how their findings apply to less ethnically distinct groups, with less aggressive media attention and under non-heteronormative roles [@main_paper]. They further call for tests in ethnonational countries and in regions where females overpopulate males to see if their findings apply to women [@main_paper]. As Global migration and refuge continue to increase, we anticipate that this field of study will become increasingly significant. It is thus crucial to expand on their findings to assess how they apply in varying nations. This is in hopes to create policy changes and account for preventative measures to avoid increased anti-refugee sentiments and hate crimes caused by sex-driven competition. We further hope for this field of research to be applied under less heteronormative circumstances and work to account for queer-identifying individuals.

\clearpage

# References {.unnumbered}

### 2024-02-13 outputs/paper/paper.qmd
edits

@@
 # install.packages("tidyverse")
-# install.packages("list)
+# install.packages("list")
 # install.packages("knitr")
@@
 #| label: fig-collection
-#| fig-cap: "00000000000000000000000000000000000000000000000000000000000000000000000000"
+#| fig-cap: "Panel A displays the number of unique studies conducted over time, Panel B the number of manuscripts published over time, Panel C the frequency of used terrorism measures (in percentage), and Panel D the frequency of studied types of terrorism (in percentage)"
 #| echo: false
@@
 
-```{r}
-#| label: fig-collection
-#| fig-cap: "000000000000000000000000000000000000000000000000000000000000"
-#| echo: false
-#| message: false
-#| warning: false
+As depicted in @fig-collection(A) and (B), scholarly interest in exploring the link between terrorism and public attitudes notably began following the 9/11 attacks, and received further impetus following the 2015–16 Islamic State (IS) attacks.
+Put differently, the figures imply that this research domain is significantly influenced by specific events.
 
-# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
-######## B. META-ANALYSIS: for each of the hypotheses ######## 
-# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ #
+Moreover, from 1985 to 2020, researchers have employed diverse methodologies to measure exposure to terrorism (refer to @fig-collection(C)).
+Some studies exposed participants to news articles or video clips depicting specific acts of violence (e.g., 9/11), while in other cases, exposure occurred naturally when surveys coincided with terror attacks (527 data points of acts of violence , as 30% ).
+Additionally, studies have assessed or manipulated individuals' perceptions of terrorism threats (threat of violence: 520 data points as 30%), examined affective responses such as fear (146 data points) and anger (111 data points), and investigated self-reported exposure to terrorism through personal experiences, relatives' experiences, or media coverage (self-reported exposure: 184 data points).
 
-# Data preparation: Split dataset in 3 based on outcome type
-# 1) outgroup dataset
-dat_outgroup <- dat[dat$PA_Category == 10 |
-                      dat$PA_Category == 99, ]
-length(unique(dat_outgroup$ID_R))#number of manuscripts (N_j)
-# 2) conservative shift dataset
-dat_conservatism <- dat[dat$PA_Category == 5 |
-                          dat$PA_Category == 6 |
-                          dat$PA_Category == 7 |
-                          dat$PA_Category == 8 |
-                          dat$PA_Category == 9 |
-                          dat$PA_Category == 11, ]
-length(unique(dat_conservatism$ID_R))#number of manuscripts (N_j)
-# 3) rally-around-the-flag dataset
-dat_rally <- dat[dat$PA_Category == 1 |
-                   dat$PA_Category == 2 |
-                   dat$PA_Category == 3 |
-                   dat$PA_Category == 4, ]
-length(unique(dat_rally$ID_R))#number of manuscripts (N_j)
-# double check (total number of effect sizes; N_k)
-count(dat_outgroup) + count(dat_conservatism) + count(dat_rally)
+The most frequently studied acts of violence are—perhaps unsurprisingly—9/11, the Israeli-Palestinian conflict, and the 2015 series of IS attacks in Paris.
+Consequently, regarding the ideology behind the violence (@fig-collection(D)), the vast majority of effect sizes quantify the effects of or relationship with Islamist terrorism (1,064 data points, 61%), following by no ideology terrorism, whereas the share of information on how the public reacts to extreme-right terror is remarkably low (35 data points, 2%).
 
-##### 1. Fit empty 3-level model using the meta3 function #####
-
-### To replicate Table 2: call summary() function for each of outcome cluster
-      ## coef(model...)[1] = Fishers' Z correlation coefficients (Zr)
-### To replicate the correlation coefficients mentioned in the text, 
-### call the FisherZinv() function for each outcome cluster.
-
-# Outgroup hostility (Table 2)
-set.seed(1234)
-model_og_LBCI <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
-                       data = dat_outgroup, 
-                       I2=c("I2q", "ICC"),
-                       intervals.type = "LB",
-                       model.name = "3 level outgroup LB")
-summary(model_og_LBCI)#results presented in Table 2, as well as
-#throughout the Supplementary Information (esp. Table B.3).
-FisherZInv(coef(model_og_LBCI)[1])#rho reported in text
-
-# Conservative shift (Table 2)
-set.seed(1234)
-model_cs_LBCI <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
-                       data = dat_conservatism, 
-                       I2=c("I2q", "ICC"),
-                       intervals.type = "LB",
-                       model.name = "3 level conservatism LB")
-summary(model_cs_LBCI)#results presented in Table 2, as well as
-#throughout the Supplementary Information (esp. Table B.3).
-FisherZInv(coef(model_cs_LBCI)[1])#rho reported in text
-
-# Rally-around-the-flag (Table 2)
-set.seed(1234)
-model_rf_LBCI <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
-                       data = dat_rally, 
-                       I2=c("I2q", "ICC"),
-                       intervals.type = "LB",
-                       model.name = "3 level rally LB")
-summary(model_rf_LBCI)#results presented in Table 2, as well as
-#throughout the Supplementary Information (esp. Table B.3).
-FisherZInv(coef(model_rf_LBCI)[1])#rho reported in text
-
-## Substantive interpretation --------------------------------------------------
-## i.e., comparison to 2016 ANES Feeling Thermometers
-anes2016 <- read_dta(file = "/cloud/project/raw/data/anes_timeseries_2016.dta")
-#select variables to summarize
-anes2016 <- anes2016 %>%
-  select(immterm = V162313, 
-         reptherm = V161096) 
-#format(round(psych::describe(anes2016),3), nsmall=3): counts NA's
-#recode NA's (!)
-anes2016$immterm <- ifelse(anes2016$immterm %in% -9:-1, NA, 
-                           identity(anes2016$immterm)) 
-anes2016$reptherm <- ifelse(anes2016$reptherm %in% -99:-1, NA, 
-                            identity(anes2016$reptherm))
-#find correct SDs to use in calculations based on Paluck et al. (2021)
-format(round(psych::describe(anes2016),3), nsmall=3) 
-#the effect of terror on the feeling therm. toward immigrants. 6.9
-cohens_d(r = FisherZInv(coef(model_og_LBCI)[1]))*27.285 
-#the effect of terror on the feeling therm. toward Rep. party: 7.2
-cohens_d(r = FisherZInv(coef(model_cs_LBCI)[1]))*27.330
-
-## Practical implication -------------------------------------------------------
-## i.e., what sample size is recommended based on this meta-analysis?
-# Outgroup hostility
-pwr.r.test(r = FisherZInv(coef(model_og_LBCI)[1]), sig.level = 0.05, power = 0.8) 
-# Conservative shift
-pwr.r.test(r = FisherZInv(coef(model_cs_LBCI)[1]), sig.level = 0.05, power = 0.8) 
-# Rally-around-the-flag
-pwr.r.test(r = FisherZInv(coef(model_rf_LBCI)[1]), sig.level = 0.05, power = 0.8)
-
-##### 2. Test variance components #####
-
-### Note: These results are briefly mentioned in footnote 13, but 
-### full results are discussed and presented in SI B.2.3.
-
-# Outgroup hostility
-
-#tau^2_3=0 (reported in Table B.2)
-set.seed(1234)
-model_og_t3 <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
-                      data = dat_outgroup, 
-                      RE3.constraints = 0, # constraining between-study level
-                      model.name = "Tau2_3 eq 0",
-                      intervals.type = "LB")
-summary(model_og_t3)#this equals a conventional random-effects model
-anova(model_og_LBCI, model_og_t3)
-
-#tau^2_2=0 (reported in Table B.2)
-set.seed(1234)
-model_og_t2 <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
-                     data = dat_outgroup,
-                     RE2.constraints = 0, # constraining within-study level
-                     model.name = "Tau2_2 eq 0",
-                     intervals.type = "LB")
-summary(model_og_t2)
-anova(model_og_LBCI, model_og_t2)
-
-# Conservative shift
-
-#tau^2_3=0 (reported in Table B.2)
-set.seed(1234)
-model_cs_t3 <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
-                     data = dat_conservatism, 
-                     RE3.constraints = 0, # constraining between-study level
-                     model.name = "Tau2_3 eq 0",
-                     intervals.type = "LB")
-summary(model_cs_t3)
-anova(model_cs_LBCI, model_cs_t3)
-
-#tau^2_2=0 (reported in Table B.2)
-set.seed(1234)
-model_cs_t2 <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
-                     data = dat_conservatism,
-                     RE2.constraints = 0, # constraining within-study level
-                     model.name = "Tau2_2 eq 0",
-                     intervals.type = "LB")
-summary(model_cs_t2)
-anova(model_cs_LBCI, model_cs_t2)
-
-# Rally-around-the-flag
-
-#tau^2_3=0 (reported in Table B.2)
-set.seed(1234)
-model_rf_t3 <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
-                     data = dat_rally, 
-                     RE3.constraints = 0, # constraining between-study level
-                     model.name = "Tau2_3 eq 0",
-                     intervals.type = "LB")
-summary(model_rf_t3)
-anova(model_rf_LBCI, model_rf_t3)
-
-#tau^2_2=0 (reported in Table B.2)
-set.seed(1234)
-model_rf_t2 <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
-                     data = dat_rally,
-                     RE2.constraints = 0, # constraining within-study level
-                     model.name = "Tau2_2 eq 0",
-                     intervals.type = "LB")
-summary(model_rf_t2)
-anova(model_rf_LBCI, model_rf_t2)
-
-```
+Table 1 demonstrates that...
 

### 2024-02-13 outputs/paper/paper.qmd
edits

@@
 
-Data from Wave 4 of surveys were used to show correlation between someone answering that they perceive refugees as a threat to finding a romantic partner and that person's gender, age, and their municipality's gender ratio.
-We reconstructed the portion of the survey data used for this analysis in @fig-excess, changing the presentation to a comparative bar chart where we can directly, visually compare different categories' response patterns along a consistent y-axis.
-
-@main_paper provides groupings for the varying elements that we wanted to distinguish and compare.
-The three age/gender groups compared are: (1) All (men and women of all ages), (2) Men between ages of 18-44, and (3) Men of "mating age" (30-40), making them of an age that is most commonly seen as the range that people seek to find a partner and "settle down." There were also 3 different groupings for categorizing a municipality's gender ratio which are referred to as "terciles." Gender ratio was calculated by dividing the male population by the female population of a given municipality [@main_paper].
-Within the survey data, each response had a value for that respondents' municipality's gender ratio.
-@tbl-terc shows the exact value of ratio used to divide groupings into 1st, 2nd, and 3rd terciles.
-
-Returning to @fig-excess, we immediately notice that the highest rate of perceiving refugees as threats, over 46%, is found in mating-aged men living in municipalities with relatively high male-to-female ratio (at least 1.12 men per 1 woman).
-Next is Men ages 18-44 in the same tercile of municipalities at around 37%.
-This is in stark contrast to the All group which includes men and women of all ages, where the proportion is lowest in the 1st tercile at around 17%, and highest at the 3rd tercile with 23%.
-There is one exception of Men 30-40 in the 1st tercile, but otherwise, Men are consistently more likely to perceive refugees as threats to mating than the general population.
-This jumps greatly the higher the male-to-female ratio is in their own town; the rate in Men 30-40 is almost tripled in the 3rd tercile than the 1st, and about 1.8 times more than the 2nd.
-
-In analyzing @fig-excess, we can recognize that the combination of a person being a man, especially between the ages of 30-40, and living in a municipality that has about 9 men per 8 women does seem to predict a higher rate of that person believing that refugees are negatively affecting their chance at finding a romantic partner.
-To confirm, it is not necessarily true that these respondents are living in an area with disproportionately more refugee men, but men in general.
-Yet, there being more men at all in their town might lead them to project blame onto refugees when presented with a question regarding the topic.
-
-\renewcommand{\arraystretch}{2}
-
-```{r}
-#| label: tbl-terc
-#| tbl-cap: "Dividing respondents into three terciles by their municipality's gender ratio"
-#| echo: false
-#| message: false
-#| warning: false
-
-terc_table <- data.frame(
-  tercile = c("1st Tercile", "2nd Tercile", "3rd Tercile"),
-  ratio = c("Less than 1.04", 
-               "More than 1.04, Less than 1.12",
-               "More than 1.12")
-)
-
-terc_table %>% 
-  knitr::kable(booktabs = T, col.names = c("Tercile", "Municipality's Male to Female Ratio")) %>% 
-  column_spec(1, bold = T, width = "10em") %>%
-  column_spec(2, width = "20em")
-```
-
-```{r}
-#| label: fig-excess
-#| fig-cap: "Proportion of respondents who see refugees as a mating threat by age group and tercile"
-#| echo: false
-#| message: false
-#| warning: false
-
-survey_data <- read_csv(here::here("inputs/data/survey_clean.csv"))
-
-# Subset of people from wave 4 and select needed columns
-s_exc <- survey_data[survey_data$wave == 4 ,]
-s_exc <- select(s_exc, c(gender, age, mate_compete, excess_males))
-
-# Add indicator if respondent agrees/strongly agrees that refugees are mate threats
-s_exc$matecomp <- ifelse(s_exc$mate_compete >= 3, 1, 0)
-
-# Add value for mate competition tercile
-s_exc$terc <- ifelse(s_exc$excess_males < 1.04, "1st Tercile", ifelse(s_exc$excess_males < 1.12, "2nd Tercile", "3rd Tercile"))
-
-# Create age groups for all people, men bw 18-44, and men bw 30-40
-s_exc$agroup <- "All, Men & Women"
-
-s_exc2 <- s_exc[s_exc$gender == "Male" & s_exc$age <= 44 & s_exc$age >= 18,]
-s_exc2$agroup <- "Male 18-44"
-
-s_exc3 <- s_exc[s_exc$gender == "Male" & s_exc$age <= 40 & s_exc$age >= 30,]
-s_exc3$agroup <- "Male 30-40"
-
-# Combining data frame back together
-s_excm <- rbind(s_exc, s_exc2)
-s_exct <- rbind(s_excm, s_exc3)
-
-# Calculating proportion of respondents who agree or strongly agree by tercile
-mean_all <- tapply(s_exc$matecomp, s_exc$terc, mean)
-mean_2 <- tapply(s_exc2$matecomp, s_exc2$terc, mean)
-mean_3 <- tapply(s_exc3$matecomp, s_exc3$terc, mean)
-
-# Setting up data frame for plotting
-s1 <- data.frame(c(mean_all))
-colnames(s1) <- c("mean")
-s2 <- data.frame(c(mean_2))
-colnames(s2) <- c("mean")
-s3 <- data.frame(c(mean_3))
-colnames(s3) <- c("mean")
-
-s_m <- rbind(s1, s2)
-s_tot <- rbind(s_m, s3)
-
-rownames(s_tot) <- NULL
-
-s_tot$grp <- rep(c("All, Men & Women","Men 18-44","Men 30-40"),each=3)
-s_tot$terc <- rep(c("1st Tercile","2nd Tercile","3rd Tercile"),times=3)
-
-# Plotting
-wrapper <- function(x, ...) 
-{paste(strwrap(x, ...), collapse = "\n")}
-
-s_tot %>% 
-  ggplot(aes(x=terc, y=mean, group=grp, fill=grp)) +
-  geom_col(position = "dodge", colour = "black")+
-  labs(x="Terciles of Excess Male Rate", fill = "Group") +
-  labs(y = wrapper("Proportion perceiving refugees as mate competition", width = 30)) +
-  theme_minimal() +
-  theme(legend.position="bottom") +
-  theme(text=element_text(size=11, family="serif")) +
-  ggtitle(wrapper("Nearly half of mating-aged men living in excess male areas perceive refugees as a threat to finding a partner", width =60)) +
-  theme(plot.title = element_text(face = "bold"))
-```
-
 ```{r}
@@
 Moreover, from 1985 to 2020, researchers have employed diverse methodologies to measure exposure to terrorism (refer to @fig-collection(C)).
-Some studies exposed participants to news articles or video clips depicting specific acts of violence (e.g., 9/11), while in other cases, exposure occurred naturally when surveys coincided with terror attacks (527 data points of acts of violence , as 30% ).
+Some studies exposed participants to news articles or video clips depicting specific acts of violence (e.g., 9/11), while in other cases, exposure occurred naturally when surveys coincided with terror attacks (527 data points of acts of violence , as 30%).
 Additionally, studies have assessed or manipulated individuals' perceptions of terrorism threats (threat of violence: 520 data points as 30%), examined affective responses such as fear (146 data points) and anger (111 data points), and investigated self-reported exposure to terrorism through personal experiences, relatives' experiences, or media coverage (self-reported exposure: 184 data points).
@@
 \clearpage
-
-```{r}
-#| label: tbl-stmt
-#| tbl-cap: "Statements used for surveying respondents"
-#| echo: false
-#| message: false
-#| warning: false
-
-stmt_table <- data.frame(
-  type = c("Only means", "Message", "Justified", "Prevent", "Condemn"),
-  question = c("When it comes to the refugee problem, violence is sometimes the only means that citizens have to get the attention of German politicians.", 
-               "Attacks against refugee homes are sometimes necessary to make it clear to politicians that we have a refugee problem.",
-               "Hostility against refugees is sometimes justified, even when it ends up in violence.",
-               "Xenophobic acts of violence are defensible if they result in fewer refugees settling in town.", 
-               "Politicians should condemn attacks against refugees more forcefully.
-(For this statement, the results were reversed such that we are looking at respondents who Disagreed or Strongly Disagreed)")
-)
-
-stmt_table %>% 
-  knitr::kable(booktabs = T, col.names = c("Type", "Statement")) %>% 
-  column_spec(1, bold = T, width = "7em") %>%
-  column_spec(2, width = "35em")
-```
-
-Shifting to the topic of hate crime and anti-refugee sentiments, another aspect of the survey asked the respondent to share whether they agreed or disagreed with varying statements that conveyed pro-hate crime or anti-refugee opinions.
-The exact statements the respondents were given can be seen in @tbl-stmt.
-For discussion, the statements have been shortened to "Only Means", "Message", "Justified", "Prevent", and "Condemn".
-The data set recorded whether respondents agreed with these statements.
-The last, Condemn, as seen in @tbl-stmt, is clearly an anti-hate crime statement.
-Thus, answers for this question were weight inversely, such that the data measures who disagreed with it.
-
-The visualization of what proportion of respondents agreed with given statements in the 2nd wave of surveys can be seen in @fig-statements.
-For unstated reasons, @main_paper excluded "Prevent" in their analysis despite having the data available to plot and analyze response rate for the statement.
-As evident, we have included it.
-We excluded the measurement for the control group of respondents who answered the Only Means statement in a list-format (as discussed in Methodology).
-This was originally intended to notice whether respondents may hide their true feelings about supporting violence against refugees if asked outright compared to if they were to be presented with it more passively in a list.
-As @main_paper found, there was no significant difference and this concern was proven to not have actually affected the regular survey data.
-Thus, we opted to only showcase the regular survey response rates.
-
-@fig-statements, shows that, for the first three statements (Only Means, Message, and Justified), between 17% and 20% of respondents agreed with the prompt.
-1 in 5 respondents specifically agreed that "hostility against refugees" that "leads to violence" can be justified in certain cases.
-The highest rate of agreement, though comes to the inverse of Condemn.
-Over 25%, more than 1 in 4 respondents, disagreed that there was a need for public figures to condemn hate crimes.
-This may point to a chunk of respondents not necessarily agreeing or supporting hate crime but not perceiving it as a major issue, and thus not seeing it as something that needs to be condemned.
-The other stand-out is how relatively low the agreement rate is for Prevent, being barely over 13%, 4% lower than the second lowest, Message.
-This may be due to the fact that Prevent is the only statement that pointedly uses the term "Xenophobic" to identify the intention of these violent acts, while the other statements use general language that don't assign an intrinsic moral value in their description of the violent acts.
-A respondent may not see a problem with any of the other statements, read Prevent, and simply disagree that their opinion is xenophobic, and thus disagree with it.
-It may have yielded more similar results to the other statements if it had been reworded to "Acts of violence against refugees".
-
-Analysis of @fig-excess confirms that there is a generally alarmingly high rate of support for hate-crime and anti-refugee statements, though there may be nuance in certain respondents not seeing these hate crimes as a problem or being racially motivated.
-These results supported the creation of @tbl-hatemodel discussed below.
-
-```{r}
-#| label: fig-statements
-#| fig-cap: "Proportion of respondents who agree with varying hate crime support statements"
-#| echo: false
-#| message: false
-#| warning: false
-
-# Set up, filter for wave 2 and select needed columns
-survey_data <- read_csv(here::here("inputs/data/survey_clean.csv"))
-
-s_stmt <- survey_data[survey_data$wave == 2,]
-s_stmt <- select(s_stmt, c(only_means, message, prevent, condemn, justified))
-
-# Add column with value for people agreeing or strongly agreeing
-s_stmt$meansp <- ifelse(s_stmt$only_means >= 3, 1, 0)
-s_stmt$msgp <- ifelse(s_stmt$message >= 3, 1, 0)
-s_stmt$justp <- ifelse(s_stmt$justified >= 3, 1, 0)
-s_stmt$prevp <- ifelse(s_stmt$prevent >= 3, 1, 0)
-s_stmt$conp <- ifelse(s_stmt$condemn >= 3, 1, 0)
-
-# Calculate proportion of respondents to agree/strongly agree with given statement
-s_stmtmeans <- na.omit(s_stmt$meansp)
-meansp <- mean(s_stmtmeans)
-
-msgp <- mean(s_stmt$msgp)
-justp <- mean(s_stmt$justp)
-prevp <- mean(s_stmt$prevp)
-conp <- mean(s_stmt$conp)
-
-# Data frame prepped for plotting
-s_stmt_p <- data.frame(c(meansp, msgp, justp, prevp, conp))
-s_stmt_p$stmt <- c("Only means", "Message", "Justified", "Prevent", "Condemn")
-
-colnames(s_stmt_p) <- c("pptn", "stmt")
-
-# Plotting
-wrapper <- function(x, ...) 
-{paste(strwrap(x, ...), collapse = "\n")}
-
-s_stmt_p %>% 
-  ggplot(aes(x=stmt, y=pptn)) +
-  geom_col(fill="gray", colour="black") +
-  scale_x_discrete(limits = c("Only means", "Message", "Justified", "Prevent", "Condemn")) +
-  labs(x="Statement Type") +
-  labs(y = wrapper("Proportion of respondents", width = 40)) +
-  theme_minimal() +
-  theme(text=element_text(size=11, family="serif")) +
-  ggtitle(wrapper("13% to 25% of respondents agree with statements supporting or not condemning violence against refugees", width =60)) +
-  theme(plot.title = element_text(face = "bold"))
-
-# add note for condemn
-```
-
-\renewcommand{\arraystretch}{1.5}
-
-Finally, we reconstructed @main_paper's battery of linear models to predict respondents' sentiments toward refugee-directed hate crime.
-6 Models were trained with increasing numbers of factors weighted using Ordinary Least Squares @tbl-hatemodel.
-The first model used solely mate competition (measured by proportion of excess males).
-Our models grew in complexity such that the second version was inclusive of job competition and life satisfaction.
-In the next four models, one at a time, sociodemographic factors, attitudes toward refugees (local first, then national), and last, additional factors (including perceptions of refugee settlements and political groups, and their affiliations) were added.
-Despite the addition of factors, across all models, the predictive weight of mate competition remains high.
-Job competition, on the other hand, was introduced in model 2 with larger weight than mate competition, but it rapidly fell off with the introduction of more factors.
-Life satisfaction's weight remains low across all inclusive models.
-Increasing R Squared indicates that model fit increases with additional factors in our model.
-These findings are consistent with @main_paper.
-
-\newpage
-
-\blandscape
-
-```{r}
-#| label: tbl-hatemodel
-#| tbl-cap: "Tabulated weights of linear regression models 1 through 6 using ordinary least squares.
-In parentheses are the standard errors.
-Asterisks denote ranges of p-values as described in the table footer."
-#| echo: false
-#| message: false
-#| warning: false
-
-survey_data <- read_csv(here::here("inputs/data/survey_clean.csv"))
-
-survey_w4 <- survey_data[survey_data$wave == 4,]
-
-lm1 <- lm(only_means ~ mate_compete, data=survey_w4)
-
-lm2 <- lm(only_means ~ mate_compete + job_compete + life_satisfaction, data=survey_w4)
-
-lm3 <- lm(only_means ~ mate_compete + job_compete + life_satisfaction + 
-            factor(age_group) +     # age group
-            factor(gender) +     # gender 
-            factor(state) +     # state  
-            factor(citizenship) +    # german citizen
-            factor(marital) +    # marital status
-            factor(religion) +    # religious affiliation
-            eduyrs +    # education
-            factor(occupation) +    # main activity
-            factor(income) +   # income
-            factor(household_size) +   # household size
-            factor(self_econ),    # subjective social status
-          data=survey_w4)
-
-lm4 <- lm(only_means ~ mate_compete + job_compete + life_satisfaction + 
-            factor(age_group) +   # age group
-            factor(gender) +   # gender 
-            factor(state) +   # state  
-            factor(citizenship) +  # german citizen
-            factor(marital) +  # marital status
-            factor(religion) +  # religious affiliation
-            eduyrs +  # education
-            factor(occupation) +  # main activity
-            factor(income) + # income
-            factor(household_size) + # household size
-            factor(self_econ) + # subjective social status
-            factor(ref_integrating) + # Refugee Index (National-level; Q73) 8 in total
-            factor(ref_citizenship) + factor(ref_reduce) + factor(ref_moredone) + factor(ref_cultgiveup) + 
-            factor(ref_economy) + factor(ref_crime) + factor(ref_terror),
-          data=survey_w4)
-
-lm5 <- lm(only_means ~ mate_compete + job_compete + life_satisfaction + 
-            factor(age_group) +      # age group
-            factor(gender) +      # gender 
-            factor(state) +      # state  
-            factor(citizenship) +     # german citizen
-            factor(marital) +     # marital status
-            factor(religion) +     # religious affiliation
-            eduyrs + # education
-            factor(occupation) +     # main activity
-            factor(income) +    # income
-            factor(household_size) +    # household size
-            factor(self_econ) +    # subjective social status
-            factor(ref_integrating) + # Refugee Index (National-level; Q73) 8 in total
-            factor(ref_citizenship) + factor(ref_reduce) + factor(ref_moredone) + factor(ref_cultgiveup) + 
-            factor(ref_economy) + factor(ref_crime) + factor(ref_terror) + 
-            factor(ref_loc_services) +    # Refugee Index (Local, Q75)
-            factor(ref_loc_economy) + factor(ref_loc_crime) + factor(ref_loc_culture) + factor(ref_loc_islam) + 
-            factor(ref_loc_schools) + factor(ref_loc_housing) + factor(ref_loc_wayoflife), ## end
-          data=survey_w4)
-
-# Add More Variables 
-# lrscale  Q21  Left-Right Scale
-# afd, Q23  Closeness to AfD
-# muslim_ind, afd_ind, contact_ind
-# distance_ref Q71. Distance to refugee reception centers
-# settle_ref Q72. Settlement of refugees living in area
-
-formula.5 <- 
-  as.character("only_means ~ mate_compete + job_compete + 
-               life_satisfaction +  factor(age_group) + factor(gender) + 
-               factor(state) + factor(citizenship) + factor(marital) + 
-               factor(religion) + eduyrs + factor(occupation) + 
-               factor(income) + factor(household_size) + factor(self_econ) + 
-               factor(ref_integrating) + factor(ref_citizenship) + factor(ref_reduce) + 
-               factor(ref_moredone) + factor(ref_cultgiveup) + 
-               factor(ref_economy) + factor(ref_crime) + factor(ref_terror)  + 
-               factor(ref_loc_services) +  factor(ref_loc_economy) + factor(ref_loc_crime) + 
-               factor(ref_loc_culture) + factor(ref_loc_islam) + 
-               factor(ref_loc_schools) + factor(ref_loc_housing) + factor(ref_loc_wayoflife)")
-
-formula.6 <- paste(formula.5, "factor(distance_ref) + factor(settle_ref)", 
-                   "left_right + afd + muslim_att + afd_att + contact_att", 
-                   sep="+", collapse="+")
-
-lm6 <- lm(as.formula(formula.6), data=survey_w4)
-
-table1 <- export_summs(lm1, lm2, lm3, lm4, lm5, lm6, scale = TRUE, number_format = "%.3f", coefs = c('mate competition'='mate_compete', 'job competition'='job_compete', 'life satisfaction'='life_satisfaction')) |>
-  set_escape_contents(FALSE) |>
-  add_rows(c("sociodemographics ", " ", " ", "X", "X", "X", "X"), after = 7)  |>
-  add_rows(c("national attitudes toward refugees", " ", " ", " ", "X", "X", "X"), after = 8) |>
-  add_rows(c("local attitudes toward refugees", " ", " ", " ", " ", "X", "X"), after = 9) |>
-  add_rows(c("additional controls", " ", " ", " ", " ", " ", "X"), after = 10)
-
-table1
-
-```
-
-\elandscape
-
-```{r, message=FALSE, message=FALSE, echo=FALSE, include=FALSE}
-#| label: draft code (not used)
-table1 <- export_summs(lm1, lm2, lm3, lm4, lm5, lm6, scale = TRUE, digits = 2, coefs = c('Mate competition'='mate_compete', 'Job competition'='job_compete', 'Life satisfaction'='life_satisfaction'))
-
-table1 <- data.frame(table1)
-
-store1 <- table1[8:9,]
-store2 <- table1[10,]
-store2 <- store2$names
-
-table1 <- table1[-1,]
-table1 <- slice(table1, 1:(n() - 3))
-
-table1[nrow(table1) + 1,] <- c("Sociodemographics", " ", " ", "X", "X", "X", "X")
-table1[nrow(table1) + 1,] <- c("National attitudes toward refugees", " ", " ", " ", "X", "X", "X")
-table1[nrow(table1) + 1,] <- c("Local attitudes toward refugees", " ", " ", " ", " ", "X", "X")
-table1[nrow(table1) + 1,] <- c("Additional controls", " ", " ", " ", " ", " ", "X")
-
-table1t <- rbind(table1, store1)
-rownames(table1t) <- NULL
-colnames(table1t) <- c("name", "m1", "m2", "m3", "m4", "m5", "m6")
-
-table1t1 <- subset(table1t, select = -c(m4, m5, m6))
-table1t2 <- subset(table1t, select = -c(m1, m2, m3))
-
-table1t1 %>% 
-  kable(booktabs = T, col.names = c("", "Model 1", "Model 2", "Model 3"), align = "lccc") %>% 
-  kable_styling(latex_options="scale_down") %>% 
-  row_spec(0,bold=TRUE)
-
-table1t2 %>% 
-  kable(booktabs = T, col.names = c("", "Model 4", "Model 5", "Model 6"), align = "lccc") %>% 
-  kable_styling(latex_options="scale_down") %>% 
-  row_spec(0,bold=TRUE) %>% 
-  footnote(general = store2)
-
-```
 

### 2024-02-13 raw/data/123.qmd
raw data

--- 2024-02-13 outputs/paper/paper.qmd
@@
----
-title: "Harmful Anti-Foreign Sentiments based on Concern for Competition Should be Recognized and Addressed"
-author: "Jayden Jung, Finn Korol, Sofia Sellitto"
-thanks: "Code and data are available at: https://github.com/jj-andj/mate-comp-hate ; Replication on Social Science Reproduction platform available at: https://doi.org/10.48152/ssrp-qg85-cb34"
-date: "February 17, 2023"
-date-format: long
-format: 
-  pdf: 
-    include-in-header: 
-      text: |
-        \usepackage{lscape}
-        \newcommand{\blandscape}{\begin{landscape}}
-        \newcommand{\elandscape}{\end{landscape}}
-    documentclass: article
-    geometry: margin = 1in
-    abstract: "Immigration and asylum-seeking are common topics of discussion in our globalized world, about which many Westerners hold opinions due to certain personal justifications.
-This paper replicates data analysis of the perceptions of non-immigrant German males towards refugees in municipalities where males overpopulate females.
-We apply secondary research regarding Canadian rates of immigration and gender imbalances in Alberta and raise concerns regarding the possibly generalizable nature of the findings in Germany.
-As this issue specifically affects minority groups experiencing prejudice, we place great emphasis on the weight of this discussion and call for future investigations of this field to inform policies and initiatives to address racism and hate crimes."
-    number-sections: true
-output: 
-  bookdown::pdf_document2
-toc: false
-fig_caption: yes
-nocite: '@*'
-bibliography: references.bib
----
-
-```{r setup}
-#| echo: false
-#| message: false
-#| warning: false
-# install.packages('readr')
-# install.packages('here')
-# install.packages("readstata13")  #  readstata13_0.9.2
-# install.packages("MASS") # MASS_7.3-51.6  
-# install.packages("sandwich")  # sandwich_2.5-1 
-# install.packages("lmtest") # lmtest_0.9-37 
-# install.packages("pBrackets") # pBrackets_1.0  
-# install.packages("dplyr") 
-# install.packages("tidyverse")
-# install.packages("list")
-# install.packages("knitr")
-# install.packages("kableExtra")
-
-library(readr) # read_csv
-library(here) # here
-library(readstata13) #  readstata13_0.9.2
-library(MASS) # MASS_7.3-51.6  
-library(sandwich)  # sandwich_2.5-1 
-library(lmtest) # lmtest_0.9-37  
-library(dplyr)
-library(tidyverse)
-library(jtools)
-library(huxtable)
-library(list)
-library(knitr)
-library(kableExtra)
-```
-
-# Introduction
-
-In Canada, hate crimes based on race and ethnicity increased by 80% in 2020, with the highest number of incidents targeting black individuals, followed by east and southeast Asians, indigenous individuals, and the lowest number of victims being South Asian individuals [@moreau_wang_2022].
-Seeing that Canada is one of the most diverse countries in the world, welcoming 405,999 permanent immigrants in 2021 [@government_of_canada_2022] and 130,125 refugees in 2020 [@macrotrends], these statistics concerning the increase of hate crimes pose a real and visceral threat to a large proportion of Canadian residents.
-
-There are many factors that contribute to the increase in hate crimes in Canada.
-However, with the rise of far-right discourse in the United States, anti-immigrant and anti-refugee rhetoric is becoming more prevalent in Canada.
-These negative attitudes and actions towards immigrants, refugees, and marginalized individuals can be the result of various structural and personal factors, including increased competition in the job and housing markets, resource scarcity, misguided beliefs about crime rates, illness, welfare dependency, and fears of losing national identity.
-Despite this, one factor that has received little attention until recently is the impact of mate competition in dating and marriage markets on anti-refugee sentiments.
-A [-@main_paper] paper by Dancygier, Egami, Jamal, and Rischke published in the American Journal of Political Science delves into this potentially important and often-overlooked fusion of social science with ecology.
-
-In studying the opinions of German males living in municipalities with excess male populations, they find that a portion of non-immigrant German men hold the belief that refugees pose a threat to their ability to pursue German women [@main_paper].
-The study population is primarily non-immigrant German males in highly male populated municipalities.
-The estimand which we intend to replicate is the effect of mate competition on anti-refugee sentiments.
-Their finding suggests that hate crimes increase where non-immigrant German men are disadvantaged in their local dating markets [@main_paper].
-Using ecological evidence and originally curated survey data, the paper concludes that competition in dating and marriage markets where men outnumber women increases anti-refugee sentiments and violence [@main_paper].
-
-Our paper will follow a reproduction of Dancygier, Egami, Jamal, and Rischke's findings and apply a Canadian-facing lens to discuss its implications on local Canadian populations and increased anti-refugee/ immigrant sentiments and violence.
-Our paper seeks to replicate their two following research claims, (1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats and (2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians.
-Our reproduction was conducted using the statistical programming language R [@citeR].
-To further enable our analysis we employed the use of the following packages: readr [@readr], here [@here], readstata13 [@readstata13], MASS [@MASS], sandwich [@sandwich], lmtest [@lmtest], dplyr [@dplyr], tidyverse [@tidyverse], jtools [@jtools], huxtable [@huxtable], list [@list], knitr [@knitr] and kableExtra [@kableExtra].
-
-We begin our paper with a discussion of the data source, the methodologies employed in the original paper and a review of the variables used for our reproduction.
-We will then conduct a reproduction of select results to verify their findings and improve upon their accessibility.
-Our paper will conclude with a discussion of our findings where we conduct a case study to apply our findings to Alberta, Canada's only Province with a greater population of males, a discussion of ethical biases, limitations and a push for future research.
-
-# Data
-
-## Source
-
-The paper used for replication is from the American Journal of Political Science which follows a discussion on the correlation of perceived mate competition and its contributions to anti-refugee sentiments and higher crime rates in Germany [@main_paper].
-Our reproduction seeks to address two findings made from the original paper and apply a Canadian facing lens.
-
-Their two claims are as follows: (1) Are non-immigrant German men who live in municipalities with excess male populations more likely to perceive refugees as threats?
-(2) Are non-immigrant German men who perceive mate competition more likely to support violence as the only means to gain the attention of German politicians?
-
-## Methodology
-
-This paper will replicate the survey data that was originally collected for the [-@main_paper] paper by Dancygier, Egami, Jamal, and Rischkes, as previously mentioned.
-Using the online survey platform "Respondi", they conduct 4 waves of surveys which spanned from September 2016 to December 2017 [@main_paper].
-The researchers suggest that the anonymity provided by the online survey platform resulted in respondents answering more truthfully.
-[@main_paper].
-To mitigate potential biases, the researchers employed list experiments in Waves 1 and 2, and in Wave 2, they randomly assigned 50% of the sample to either a control or treatment group.
-The treatment group was exposed to statements concerning their agreement with using violence against refugees as a means to get the attention of German politicians.
-However, no evidence was found to suggest that respondents were concealing their support for hate crimes when comparing the means of the control and treatment groups [@main_paper].
-
-## Features
-
-The original survey data assessed participants on 53 variables, being representative of gender, age and state.
-The range of recorded age data from the survey occurs from 19-89 years old.
-Age was then categorized by group which is as follows: 18-29, 30-39, 30-49, 50-59, and 60 and older.
-Both male and female participants took part in the survey, but females were only involved in Waves 2 and 4 of surveys.
-The survey was distributed across 16 German states.
-Our reproduction, however, included removing variables that were not utilized in our final reproduction analysis and included only the necessary Waves 2 and 4.
-As a part of our reproduction, we also simplified the names of variables to make them easier to work with.
-From the original survey data, each variable correlates with a survey question asked to participants.
-To discuss the variables used in our reproduction we have grouped them by category way and have listed each variable below.
-Some survey questions are presented, and have been reworded slightly for consistency and clarity.
-
-[Socio-demographics]{.underline}
-
--   Age Group
--   Gender
--   State
--   German Citizen
--   Marital Status
--   Relationship status, single
--   Religious Affiliation
--   Education
--   Occupation
--   Income
--   Household Size
--   Subjective Social Status
--   Excess males: The proportion of males to females by states by dividing the number of women by men aged 14 and 44 for each municipality 
--   Politics: left and right-leaning
--   Politics: affiliated parties
-
-[Mate Competition: using a scale (1-4) to indicate agreement or disagreement]{.underline}
-
--   The influx of male refugees make it difficult for non-immigrant German men to find female partners
-
-[Job Competition: using a scale of agree or disagree]{.underline}
-
--   The inflow of young male refugees makes it more difficult for young non-immigrant German men to find work/ jobs
-
-[Life Satisfaction: scale of 0-10]{.underline}
-
--   Rank your satisfaction with life
-
-[Encountering Refugees]{.underline}
-
--   How many KM is the closest refugee reception center from your home?
--   How many refugees do you believe have settled in your municipality in the last year?
--   In the last month, how many refugees have you encountered in the following locations?
-(on the street, on public transport or in parks, in stores, in refugee reception centres or hostels, school, work)
-
-[Attitudes Toward Refugees (national and local scale): using a scale of agree or disagree]{.underline}
-
--   Violence is sometimes the only means that citizens have to get the attention of German politicians 
--   Attitudes towards Muslims
--   Hostility against refugees is justified
--   Politicians should condemn attacks against refugees
--   Racist violence is defensible if it leads to fewer refugees settling in a town
--   Attacks against refugee homes are sometimes necessary to make garner the attention of politicians
--   Refugees are integrating well into Germany
--   German refugees should be entitled to German citizenship
--   The number of refugees should be reduced
--   Refugees are receiving more than non-immigrant Germans
--   Refugees should give up their culture to adopt that of Germany
--   Refugees are good for the economy
--   Refugees increase crime
--   Increased refugees increase the risk of terrorism
--   Additional refugees in your town will increase the influence of Islam (local)
--   Additional refugees in your town will be a challenge for local schools (local)
--   Additional refugees in your town will increase competition for housing (local)
--   Additional refugees in your town will change the way of life in your town (local)
-
-[Operational category]{.underline}
-
--   Experiment lists
--   Treatment lists
--   Outcome lists
--   Waves: out of 4
-
-# Results
-
 ```{r}
-#| label: fig-collection
-#| fig-cap: "Panel A displays the number of unique studies conducted over time, Panel B the number of manuscripts published over time, Panel C the frequency of used terrorism measures (in percentage), and Panel D the frequency of studied types of terrorism (in percentage)"
+#| label: fig-collection1
+#| fig-cap: "00000000000000000000000000000000000000000000000000000000000000000000000000"
 #| echo: false
@@
 
-As depicted in @fig-collection(A) and (B), scholarly interest in exploring the link between terrorism and public attitudes notably began following the 9/11 attacks, and received further impetus following the 2015–16 Islamic State (IS) attacks.
-Put differently, the figures imply that this research domain is significantly influenced by specific events.
+```{r}
+#| label: fig-collection
+#| fig-cap: "00000000000000000000000000000000000000000000000000000000"
+#| echo: false
+#| message: false
+#| warning: false
 
-Moreover, from 1985 to 2020, researchers have employed diverse methodologies to measure exposure to terrorism (refer to @fig-collection(C)).
-Some studies exposed participants to news articles or video clips depicting specific acts of violence (e.g., 9/11), while in other cases, exposure occurred naturally when surveys coincided with terror attacks (527 data points of acts of violence , as 30%).
-Additionally, studies have assessed or manipulated individuals' perceptions of terrorism threats (threat of violence: 520 data points as 30%), examined affective responses such as fear (146 data points) and anger (111 data points), and investigated self-reported exposure to terrorism through personal experiences, relatives' experiences, or media coverage (self-reported exposure: 184 data points).
+# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
+######## B. META-ANALYSIS: for each of the hypotheses ######## 
+# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ #
 
-The most frequently studied acts of violence are—perhaps unsurprisingly—9/11, the Israeli-Palestinian conflict, and the 2015 series of IS attacks in Paris.
-Consequently, regarding the ideology behind the violence (@fig-collection(D)), the vast majority of effect sizes quantify the effects of or relationship with Islamist terrorism (1,064 data points, 61%), following by no ideology terrorism, whereas the share of information on how the public reacts to extreme-right terror is remarkably low (35 data points, 2%).
+# Data preparation: Split dataset in 3 based on outcome type
+# 1) outgroup dataset
 
-Table 1 demonstrates that...
+dat <- read_excel("/cloud/project/raw/data/02-metaanalysis-data.xlsx", sheet = "Data", 
+                  col_names = TRUE, skip = 3)
 
-\clearpage
+dat_outgroup <- dat[dat$PA_Category == 10 |
+                      dat$PA_Category == 99, ]
+length(unique(dat_outgroup$ID_R))#number of manuscripts (N_j)
+# 2) conservative shift dataset
+dat_conservatism <- dat[dat$PA_Category == 5 |
+                          dat$PA_Category == 6 |
+                          dat$PA_Category == 7 |
+                          dat$PA_Category == 8 |
+                          dat$PA_Category == 9 |
+                          dat$PA_Category == 11, ]
+length(unique(dat_conservatism$ID_R))#number of manuscripts (N_j)
+# 3) rally-around-the-flag dataset
+dat_rally <- dat[dat$PA_Category == 1 |
+                   dat$PA_Category == 2 |
+                   dat$PA_Category == 3 |
+                   dat$PA_Category == 4, ]
+length(unique(dat_rally$ID_R))#number of manuscripts (N_j)
+# double check (total number of effect sizes; N_k)
+count(dat_outgroup) + count(dat_conservatism) + count(dat_rally)
 
-# Discussion
+##### 1. Fit empty 3-level model using the meta3L function #####
 
-## Findings
+### To replicate Table 2: call summary() function for each of outcome cluster
+      ## coef(model...)[1] = Fishers' Z correlation coefficients (Zr)
+### To replicate the correlation coefficients mentioned in the text, 
+### call the FisherZinv() function for each outcome cluster.
 
-In this paper, we have replicated the results found by Dancygier, Egami, Jamal, and Rischke.
-Their analysis sought to explore the correlation between perceived mate competition in municipalities with excess males and its contributions to anti-refugee sentiments and higher crime rates in Germany.
-Our paper has replicated two of their major findings.
+# Outgroup hostility (Table 2)
+set.seed(1234)
+model_og_LBCI <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
+                       data = dat_outgroup, 
+                       I2=c("I2q", "ICC"),
+                       intervals.type = "LB",
+                       model.name = "3 level outgroup LB")
+summary(model_og_LBCI)#results presented in Table 2, as well as
+#throughout the Supplementary Information (esp. Table B.3).
+FisherZInv(coef(model_og_LBCI)[1])#rho reported in text
 
-(1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats.
+# Conservative shift (Table 2)
+set.seed(1234)
+model_cs_LBCI <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
+                       data = dat_conservatism, 
+                       I2=c("I2q", "ICC"),
+                       intervals.type = "LB",
+                       model.name = "3 level conservatism LB")
+summary(model_cs_LBCI)#results presented in Table 2, as well as
+#throughout the Supplementary Information (esp. Table B.3).
+FisherZInv(coef(model_cs_LBCI)[1])#rho reported in text
 
-(2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians.
+# Rally-around-the-flag (Table 2)
+set.seed(1234)
+model_rf_LBCI <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
+                       data = dat_rally, 
+                       I2=c("I2q", "ICC"),
+                       intervals.type = "LB",
+                       model.name = "3 level rally LB")
+summary(model_rf_LBCI)#results presented in Table 2, as well as
+#throughout the Supplementary Information (esp. Table B.3).
+FisherZInv(coef(model_rf_LBCI)[1])#rho reported in text
 
-By replicating their results, we hope to apply a Canadian-facing lens to gain insights into Canadian dating markets, the geographical distribution of males and females and their potential impacts on anti-refugee sentiments.
+## Substantive interpretation --------------------------------------------------
+## i.e., comparison to 2016 ANES Feeling Thermometers
+anes2016 <- read_dta(file = "/cloud/project/raw/data/anes_timeseries_2016.dta")
+#select variables to summarize
+anes2016 <- anes2016 %>%
+  select(immterm = V162313, 
+         reptherm = V161096) 
+#format(round(psych::describe(anes2016),3), nsmall=3): counts NA's
+#recode NA's (!)
+anes2016$immterm <- ifelse(anes2016$immterm %in% -9:-1, NA, 
+                           identity(anes2016$immterm)) 
+anes2016$reptherm <- ifelse(anes2016$reptherm %in% -99:-1, NA, 
+                            identity(anes2016$reptherm))
+#find correct SDs to use in calculations based on Paluck et al. (2021)
+format(round(psych::describe(anes2016),3), nsmall=3) 
+#the effect of terror on the feeling therm. toward immigrants. 6.9
+cohens_d(r = FisherZInv(coef(model_og_LBCI)[1]))*27.285 
+#the effect of terror on the feeling therm. toward Rep. party: 7.2
+cohens_d(r = FisherZInv(coef(model_cs_LBCI)[1]))*27.330
 
-## Canadian Relevance: Case Study on Alberta's population ratios, dating markets and anti-refugee sentiments
+## Practical implication -------------------------------------------------------
+## i.e., what sample size is recommended based on this meta-analysis?
+# Outgroup hostility
+pwr.r.test(r = FisherZInv(coef(model_og_LBCI)[1]), sig.level = 0.05, power = 0.8) 
+# Conservative shift
+pwr.r.test(r = FisherZInv(coef(model_cs_LBCI)[1]), sig.level = 0.05, power = 0.8) 
+# Rally-around-the-flag
+pwr.r.test(r = FisherZInv(coef(model_rf_LBCI)[1]), sig.level = 0.05, power = 0.8)
 
-To investigate the relevance of Dancygier, Egami, Jamal, and Rischke's discoveries in a Canadian context, we will now explore Canada's only Province with a higher ratio of males than females.
+```
 
-Alberta is a Province in Canada with a total population of 4,543,111 individuals.
-It is the only Canadian Province that is more heavily populated by males, with a male population of 2,282,040 compared to 2,261,071 females [@statista].
-Thus having a ratio of approximately 1.01, which is comparable to that of the 1st tercile in Figure 1.
-This means that there are about 11,000 more men than women residing in this Province.
-Part of the population gap can be explained by age.
-Alberta has a primarily young population and we typically see that as populations age they exhibit a higher female population [@edmonton_journal].
-Its trades centric economy also attracts young male migrants from across Canada [@edmonton_journal].
+```{r}
 
-Concerning the original paper, Alberta's population growth can be largely attributed to international immigration which has typically brought equal numbers of males and females [@edmonton_journal].
-However, according to the 2021 census, 101, 650 more males are single (not married or living common law and never married) than women [@govcan].
-Due to Alberta's young population, highly concentrated with men of working age, a comparison can be made to the term 'mating-aged' used in the original paper to describe males facing higher tensions of dating competition.
-We thus believe that similar conditions for dating and marriage markets can be made between Alberta and the German municipalities of that the 1st Tercile from Figure 1.
+```{r}
+#| label: fig-collection1
+#| fig-cap: "000000000000000000000000000000000000000000000000000000000000"
+#| echo: false
+#| message: false
+#| warning: false
 
-While population demographics are comparable between that of Alberta and the 1st tercile of German municipalities in the original paper, it is difficult to suggest that potential competition in Albertan dating and marriage markets correlates to anti-refugee sentiments and violence.
-However, in addressing Albertan immigrant and refugee statistics we will aim to illustrate how these patterns found in Germany can manifest in the context of Alberta.
-Based on the 2021-2022 Annual Population Report, Alberta welcomed 12,603 immigrants and 21,434 non-permanent residents, which include refugees [@alberta_2023].
+# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
+######## B. META-ANALYSIS: for each of the hypotheses ######## 
+# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ #
 
-While previous accounts have suggested that immigration has brought an equal number of males and females, it is safe to assume that Alberta is a growing population, subject to a population with a higher concentration of males [@edmonton_journal].
-According to a 2018 paper, at the time 6 in 10 Canadians disagreed when asked if immigration levels were too high, with 35% believing that Canada accepts too many immigrants [@globe_mail].
-However, sentiments appear less than positive in Alberta, with Albertans expressing harsher attitudes towards immigrants and refugees [@globe_mail].
-48% of Albertans at the time agreed that refugee claims are not filed from real refugees, with 62% stating that immigrants do not adopt Canadian values, about 10% higher than the national average of 51% [@globe_mail].
-The Globe and Mail suggest that part of Alberta's higher anti-refugee attitudes can be attributed to its economy and fears of competition.Dancygier, Egami, Jamal, and Rischke  find that in areas where men significantly outnumber women, there are higher levels of anti-refugee hate crimes [@main_paper].
+# Data preparation: Split dataset in 3 based on outcome type
+# 1) outgroup dataset
+dat_outgroup <- dat[dat$PA_Category == 10 |
+                      dat$PA_Category == 99, ]
+length(unique(dat_outgroup$ID_R))#number of manuscripts (N_j)
+# 2) conservative shift dataset
+dat_conservatism <- dat[dat$PA_Category == 5 |
+                          dat$PA_Category == 6 |
+                          dat$PA_Category == 7 |
+                          dat$PA_Category == 8 |
+                          dat$PA_Category == 9 |
+                          dat$PA_Category == 11, ]
+length(unique(dat_conservatism$ID_R))#number of manuscripts (N_j)
+# 3) rally-around-the-flag dataset
+dat_rally <- dat[dat$PA_Category == 1 |
+                   dat$PA_Category == 2 |
+                   dat$PA_Category == 3 |
+                   dat$PA_Category == 4, ]
+length(unique(dat_rally$ID_R))#number of manuscripts (N_j)
+# double check (total number of effect sizes; N_k)
+count(dat_outgroup) + count(dat_conservatism) + count(dat_rally)
 
-Based on these statistics, we believe that Alberta may experience a similar effect of anti-refugee sentiments in part as a result of increased immigrants/ refugees and competition in a young male-dominated population.
-However, as stated in their original paper, we call for further research to be conducted on this effect to better understand its implications on non-German countries.
+##### 1. Fit empty 3-level model using the meta3 function #####
 
-## Ethical Implications
+### To replicate Table 2: call summary() function for each of outcome cluster
+      ## coef(model...)[1] = Fishers' Z correlation coefficients (Zr)
+### To replicate the correlation coefficients mentioned in the text, 
+### call the FisherZinv() function for each outcome cluster.
 
-In their paper, Dancygier, Egami, Jamal, and Rischke examine the ethical implication of using experimental methodologies to investigate their research topic.
-By using descriptive data in the form of surveys they are able to investigate the opinions of non-immigrant German males and their perception of mate competition and its translation to anti-refugee violence.
-By avoiding experimental trials, they were able to explore their topic without provoking anti-refugee sentiment [@main_paper].
-While conducting experimental trials on this topic of research is considered unethical, surveys and questionnaires may have a tendency to give respondents the impression that their opinions are commonly shared or even accurate.
-By being presented with a platform to express their perception of mate competition and if they agree that violence towards refugees is the only way to garner the attention of German politicians, respondents may feel that their opinions are incorrectly justified.
-This then has the potential to translate to violence towards German refugees.
+# Outgroup hostility (Table 2)
+set.seed(1234)
+model_og_LBCI <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
+                       data = dat_outgroup, 
+                       I2=c("I2q", "ICC"),
+                       intervals.type = "LB",
+                       model.name = "3 level outgroup LB")
+summary(model_og_LBCI)#results presented in Table 2, as well as
+#throughout the Supplementary Information (esp. Table B.3).
+FisherZInv(coef(model_og_LBCI)[1])#rho reported in text
 
-## Accounting for Bias
+# Conservative shift (Table 2)
+set.seed(1234)
+model_cs_LBCI <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
+                       data = dat_conservatism, 
+                       I2=c("I2q", "ICC"),
+                       intervals.type = "LB",
+                       model.name = "3 level conservatism LB")
+summary(model_cs_LBCI)#results presented in Table 2, as well as
+#throughout the Supplementary Information (esp. Table B.3).
+FisherZInv(coef(model_cs_LBCI)[1])#rho reported in text
 
-Ethical implications and biases arise naturally when collecting quantitative and qualitative data.
-In their paper, Dancygier, Egami, Jamal, and Rischke use online survey platforms to assess if Germans living in areas with greater populations of men who experience turmoil in the mating market are more likely to perceive competition between themselves and refugees, moreover, does this ideology predict hate crime support [@main_paper].
-The authors attempted to address ethical concerns and statistical biases by utilizing control groups and replicating their study with different samples and polling firms.
-However, one potential bias that is challenging to control for is the presence of sampling bias [@main_paper].
-Sampling bias occurs when participants in a study are not representative of the estimand or the ideal population of interest.
-One method to control for this bias is simple random sampling, where participants are chosen by chance.
-Meaning that every individual in the population has an equal chance of being selected.
-However, in their study, they were unable to utilize simple random sampling.
-Instead attempted to make their survey results representative by conducting 4 waves of surveys meant to be representative of age, gender and geographical region [@main_paper].
-Despite their effort, their survey results may not be entirely representative as individuals who have a strong interest in the subject matter are more likely to participate, meaning they do not reflect the views of all non-immigrant German males [@main_paper].
+# Rally-around-the-flag (Table 2)
+set.seed(1234)
+model_rf_LBCI <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
+                       data = dat_rally, 
+                       I2=c("I2q", "ICC"),
+                       intervals.type = "LB",
+                       model.name = "3 level rally LB")
+summary(model_rf_LBCI)#results presented in Table 2, as well as
+#throughout the Supplementary Information (esp. Table B.3).
+FisherZInv(coef(model_rf_LBCI)[1])#rho reported in text
 
-## Limitations
+## Substantive interpretation --------------------------------------------------
+## i.e., comparison to 2016 ANES Feeling Thermometers
+anes2016 <- read_dta(file = "/cloud/project/raw/data/anes_timeseries_2016.dta")
+#select variables to summarize
+anes2016 <- anes2016 %>%
+  select(immterm = V162313, 
+         reptherm = V161096) 
+#format(round(psych::describe(anes2016),3), nsmall=3): counts NA's
+#recode NA's (!)
+anes2016$immterm <- ifelse(anes2016$immterm %in% -9:-1, NA, 
+                           identity(anes2016$immterm)) 
+anes2016$reptherm <- ifelse(anes2016$reptherm %in% -99:-1, NA, 
+                            identity(anes2016$reptherm))
+#find correct SDs to use in calculations based on Paluck et al. (2021)
+format(round(psych::describe(anes2016),3), nsmall=3) 
+#the effect of terror on the feeling therm. toward immigrants. 6.9
+cohens_d(r = FisherZInv(coef(model_og_LBCI)[1]))*27.285 
+#the effect of terror on the feeling therm. toward Rep. party: 7.2
+cohens_d(r = FisherZInv(coef(model_cs_LBCI)[1]))*27.330
 
-Being a reproduction, much of our analysis was limited to the original survey circumstances captured in [@main_paper].
-Despite the survey being long, it can not be considered to be comprehensive.
-This prevented us from exploring other relationships in the data.
-For example, in this German context, it would have been interesting to look into sentiments toward the treatment of communities experiencing genocide during the history of World War 2.
-Our connection of findings to the Albertan context was also limited by this cultural and geographical separation from our data.
+## Practical implication -------------------------------------------------------
+## i.e., what sample size is recommended based on this meta-analysis?
+# Outgroup hostility
+pwr.r.test(r = FisherZInv(coef(model_og_LBCI)[1]), sig.level = 0.05, power = 0.8) 
+# Conservative shift
+pwr.r.test(r = FisherZInv(coef(model_cs_LBCI)[1]), sig.level = 0.05, power = 0.8) 
+# Rally-around-the-flag
+pwr.r.test(r = FisherZInv(coef(model_rf_LBCI)[1]), sig.level = 0.05, power = 0.8)
 
-Due to the heteronormative nature of this study's data, our analysis was also not able to be fully representative of the German population as [@main_paper]'s authors described.
-While this is not to be surprised from an ecological context of mating behaviour, perhaps gay men would have been found to experience anti-refugee sentiment as well as an extension of the mate competition argument.
-
-There were also limitations associated with missing and limited data in our set.
-For example, in our analysis depicted in @fig-excess, fewer than 300 observations were represented in the oldest age group, which these authors doubted was enough for a meaningful evaluation.
-
-## Future Research
-
-As suggested in their original paper, Dancygier, Egami, Jamal, and Rischke call for future research to investigate how their findings apply to less ethnically distinct groups, with less aggressive media attention and under non-heteronormative roles [@main_paper].
-They further call for tests in ethnonational countries and in regions where females overpopulate males to see if their findings apply to women [@main_paper].
-As Global migration and refuge continue to increase, we anticipate that this field of study will become increasingly significant.
-It is thus crucial to expand on their findings to assess how they apply in varying nations.
-This is in hopes to create policy changes and account for preventative measures to avoid increased anti-refugee sentiments and hate crimes caused by sex-driven competition.
-We further hope for this field of research to be applied under less heteronormative circumstances and work to account for queer-identifying individuals.
-
-\clearpage
-
-# References {.unnumbered}
+```
+```

### 2024-02-13 raw/02-meta-analysis.R

@@ -1,0 +1,2567 @@
+# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
+# PROJECT:    How Terrorism Does (and Does Not) Affect Citizens' 
+#             Political Attitudes: A Meta-Analysis. 
+# AUTHOR:     Amelie Godefroidt
+# CONTACT:    amelie.godefroidt@ntnu.no
+# 
+# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
+# This R file contains the code necessary to replicate all main results,
+# including the descriptive statistics, meta-analysis, and meta-regressions.
+# 
+# Last successful replication: 01.11.2021
+# 
+# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
+
+# first things first: set your settings.
+
+rm(list=ls())
+#setwd("raw/data") #set your directory
+options("scipen"=100, "digits"=8) #set digits
+getwd()
+
+
+###### Install and load packages ###### 
+
+# ipak function: install and load multiple R packages.
+# check to see if packages are installed. Install them if they are not, then load them into the R session.
+
+ipak <- function(pkg){  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
+if(length(new.pkg)) install.packages(new.pkg, dependencies = TRUE)
+sapply(pkg, require, character.only = TRUE)
+}
+
+packages <- c("readxl", "haven", "psych", "dplyr", "DescTools", "broom", "cowplot",
+              "pwr", "esc", "metaSEM", "metafor", "metaviz", "PerformanceAnalytics", 
+              "ggplot2", "ggpubr", "wesanderson", "stringr", "dotwhisker") 
+ipak(packages)
+
+
+###### Import and split data ###### 
+
+dat <- read_excel("/cloud/project/raw/data/02-metaanalysis-data.xlsx", sheet = "Data", 
+                  col_names = TRUE, skip = 3)
+
+### dataframe of studies
+dat_studies <- dat[c(1:87)] #studies.
+dat_studies <- group_by(dat_studies, ID_RS) %>% slice(1)
[…]

### 2024-02-13 outputs/paper/paper.qmd
update data part

@@
 
-The paper used for replication is from the American Journal of Political Science which follows a discussion on the correlation of perceived mate competition and its contributions to anti-refugee sentiments and higher crime rates in Germany [@main_paper].
-Our reproduction seeks to address two findings made from the original paper and apply a Canadian facing lens.
+In this paper we aim to replicate part of the results from the "How Terrorism Does (and Does Not) Affect Citizens’ Political Attitudes: A Meta-Analysis." In the original paper, the author Godefroidt explored the correlation between terrorism and outgroup hostility and conservatism.
+Furthermore, the author also included more complicated models and even an shinny app for interactive viewing.
+Due to various restraints, we are going the test the major finding of the original paper.
 
-Their two claims are as follows: (1) Are non-immigrant German men who live in municipalities with excess male populations more likely to perceive refugees as threats?
-(2) Are non-immigrant German men who perceive mate competition more likely to support violence as the only means to gain the attention of German politicians?
+In summary, the major claims(also what we are gong to replicate ) of the original paper are:
+1.To what extend do terrorism arose public sentiment towards outgroup hostility, and a conservative shift. 
+2.To what extend do the last claim hold, if being placed across different contexts.How such differences in observed effect sizes explained by additional moderators?
 
@@
 
-This paper will replicate the survey data that was originally collected for the [-@main_paper] paper by Dancygier, Egami, Jamal, and Rischkes, as previously mentioned.
-Using the online survey platform "Respondi", they conduct 4 waves of surveys which spanned from September 2016 to December 2017 [@main_paper].
-The researchers suggest that the anonymity provided by the online survey platform resulted in respondents answering more truthfully.
-[@main_paper].
-To mitigate potential biases, the researchers employed list experiments in Waves 1 and 2, and in Wave 2, they randomly assigned 50% of the sample to either a control or treatment group.
-The treatment group was exposed to statements concerning their agreement with using violence against refugees as a means to get the attention of German politicians.
-However, no evidence was found to suggest that respondents were concealing their support for hate crimes when comparing the means of the control and treatment groups [@main_paper].
+The original paper obtained its data from database that contains 12333 records.
+The data was collected throug three steps, electronic search, screening related paper, and public survey.
+After the filtering, 10,391 records were included for further reviewing.
+In the [figure 1], the author used a flow chart to illustrate the collecting and cleaning process.
+The collected data from six sources ranging from 'web of science,' to 'personal contact.' After preliminary filtering, additional 9444 records were removed due to the nature of these information are news articles and policy briefing.
+The inclusion of these information may ditch the reliability of the analysis.
+Eventually 241 pieces were retained.
+They were then used for data processing, a total of 1733 total associations were generated.
 
@@
 
-The original survey data assessed participants on 53 variables, being representative of gender, age and state.
-The range of recorded age data from the survey occurs from 19-89 years old.
-Age was then categorized by group which is as follows: 18-29, 30-39, 30-49, 50-59, and 60 and older.
-Both male and female participants took part in the survey, but females were only involved in Waves 2 and 4 of surveys.
-The survey was distributed across 16 German states.
-Our reproduction, however, included removing variables that were not utilized in our final reproduction analysis and included only the necessary Waves 2 and 4.
-As a part of our reproduction, we also simplified the names of variables to make them easier to work with.
+Those associations or processed data are stored in the file metaanalysis-data.xlsx.
+It contains 76 column and 1733 observations.
+A randomized selection of manuscripts (±15% of the total sample) was used to pilot the code book and make any necessary revisions.
+The columns can be divided into fifth major data categories.
+The first part of the variables are identity information of the data such as the author name, year of the study, the sample size and the general population.
+The second part is the political tendency and people's ethnicity with variables ranging from the percentage of people identifying as a liberal and mean to the white-muslims percentage.
+The third portion records the detail of each terrorist attack, including the type, date, casualties.
+The forth part records a series of political attitudes.
+For example, nationalism and institutional trust, socio-economic conservatism, support for policies that pertains an outgroup.
+The last part lists the analysis technical data that will be used in meta-analysis code such as Fisher's Z correlation, Regression and so on.
 From the original survey data, each variable correlates with a survey question asked to participants.
-To discuss the variables used in our reproduction we have grouped them by category way and have listed each variable below.
-Some survey questions are presented, and have been reworded slightly for consistency and clarity.
+In our reproduction, we excluded data that being used for figure3 and figure4 the moderator test.
+We also made some minor changes and removed insignificant data for clearer replication and viewing.
 
-[Socio-demographics]{.underline}
+In order to better present our replication of the results, The following are measurments of public political opinions provided by the author.
+They are classfied into 4 categories given in the orignal paper.
+We selected some important measures
 
--   Age Group
--   Gender
--   State
--   German Citizen
--   Marital Status
--   Relationship status, single
--   Religious Affiliation
--   Education
--   Occupation
--   Income
--   Household Size
--   Subjective Social Status
--   Excess males: The proportion of males to females by states by dividing the number of women by men aged 14 and 44 for each municipality 
--   Politics: left and right-leaning
--   Politics: affiliated parties
+[Objective exposure]{.underline}
 
-[Mate Competition: using a scale (1-4) to indicate agreement or disagreement]{.underline}
+-   Pre postattack measures
+-   Days between an act of violence and survey day
+-   Newspaper vignette about an act of violence
+-   News clip about an act of violence
 
--   The influx of male refugees make it difficult for non-immigrant German men to find female partners
+[Self-reported exposre]{.underline}
 
-[Job Competition: using a scale of agree or disagree]{.underline}
+-   Direct exposure to terrorism
+-   Indirect exposure via friends and family
+-   Indirect exposure via media reports
 
--   The inflow of young male refugees makes it more difficult for young non-immigrant German men to find work/ jobs
+[Cognitions]{.underline}
 
-[Life Satisfaction: scale of 0-10]{.underline}
+-   Self-reported concern/worry for an attack on the nation
+-   Self-reported concern/worry to become a victim of terrorism
+-   Self-reported concern/worry for an attack on the nation
+-   Manipulated vignette or writing task about the threat of terrorism (rather than about a specific act of violence)
+-   Manipulated percentage of the threat of terrorism
 
--   Rank your satisfaction with life
+[Emotion]{.underline}
 
-[Encountering Refugees]{.underline}
+-   Anger/outrage
+-   Fear/anxiety
+-   Sadness
+-   General negative emotion
 
--   How many KM is the closest refugee reception center from your home?
--   How many refugees do you believe have settled in your municipality in the last year?
--   In the last month, how many refugees have you encountered in the following locations?
-(on the street, on public transport or in parks, in stores, in refugee reception centres or hostels, school, work)
+# Statistical Analysis
 
-[Attitudes Toward Refugees (national and local scale): using a scale of agree or disagree]{.underline}
-
--   Violence is sometimes the only means that citizens have to get the attention of German politicians 
--   Attitudes towards Muslims
--   Hostility against refugees is justified
--   Politicians should condemn attacks against refugees
--   Racist violence is defensible if it leads to fewer refugees settling in a town
--   Attacks against refugee homes are sometimes necessary to make garner the attention of politicians
--   Refugees are integrating well into Germany
--   German refugees should be entitled to German citizenship
--   The number of refugees should be reduced
--   Refugees are receiving more than non-immigrant Germans
--   Refugees should give up their culture to adopt that of Germany
--   Refugees are good for the economy
--   Refugees increase crime
--   Increased refugees increase the risk of terrorism
--   Additional refugees in your town will increase the influence of Islam (local)
--   Additional refugees in your town will be a challenge for local schools (local)
--   Additional refugees in your town will increase competition for housing (local)
--   Additional refugees in your town will change the way of life in your town (local)
-
-[Operational category]{.underline}
-
--   Experiment lists
--   Treatment lists
--   Outcome lists
--   Waves: out of 4
-
+In this paper we will replicate figure 2 and table2 of the orginal paper.
+Fortunately, the author has already compressed all the analysis into one coding file.
+We selected the corresponding part for each illustration.
+In terms of the analysis method, Pearson's correlation coefficient is used.
+According to the orignal paper, the manuscripts of the data they collected used various statistical method.
+For comparison purposes, each association is converted into a Pearson's correlation coefficient with the sampling variance.
+The author stressed that to "meaningfully compare and pool effect sizes, all correlations must also reflect the relation between terrorism and sociopolitical attitudes in the same direction."
 # Results
-
-```{r}
-#| label: fig-collection
-#| fig-cap: "Panel A displays the number of unique studies conducted over time, Panel B the number of manuscripts published over time, Panel C the frequency of used terrorism measures (in percentage), and Panel D the frequency of studied types of terrorism (in percentage)"
-#| echo: false
-#| message: false
-#| warning: false
-
-rm(list=ls())
-setwd("/cloud/project/raw/data") #set your directory
-options("scipen"=100, "digits"=8) #set digits
-getwd()
-
-ipak <- function(pkg){  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
-if(length(new.pkg)) install.packages(new.pkg, dependencies = TRUE)
-sapply(pkg, require, character.only = TRUE)
-}
-
-packages <- c("readxl", "haven", "psych", "dplyr", "DescTools", "broom", "cowplot",
-              "pwr", "esc", "metaSEM", "metafor", "metaviz", "PerformanceAnalytics", 
-              "ggplot2", "ggpubr", "wesanderson", "stringr", "dotwhisker") 
-ipak(packages)
-
-dat <- read_excel("/cloud/project/raw/data/02-metaanalysis-data.xlsx", sheet = "Data", 
-                  col_names = TRUE, skip = 3)
-
-### dataframe of studies
-dat_studies <- dat[c(1:87)] #studies.
-dat_studies <- group_by(dat_studies, ID_RS) %>% slice(1)
-sum(dat_studies$ESS, na.rm = TRUE) #number of unique respondents
-
-### dataframe of reports
-dat_reports <- dat[c(1:87)] #reports/publications.
-dat_reports <- group_by(dat_reports, ID_R) %>% slice(1)
-
-### set wished layout settings
-mytheme <- theme(plot.title = element_text(face = "bold", size = (22), colour = "black"), 
-                 axis.text = element_text(size = (18), colour = "black"),
-                 axis.ticks.length = unit(0.5, "cm"),
-                 axis.title.y = element_text(size = (22), colour = "black"),
-                 axis.title.x = element_text(size = (22), colour = "white"))
-
-# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
-###### A. DESCRIPTIVES: THE FIELD OF EMPIRICAL TERRORISM STUDIES ######
-# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ #
-
-## mean ES's per report (reported in footnote 6)
-format(round(psych::describe(aggregate(Correlation ~ ID_R, data = dat, FUN = length)),3), nsmall=3)
-
-StudyYear <- ggplot(dat_studies, aes(x=StudyYear)) + 
-  geom_histogram(binwidth=1,
-                 color="#000000", fill="#939598") +
-  labs(x="to fill some space", y = "", title = "Year of Data Collection") +
-  scale_y_continuous(breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45)) +
-  scale_x_continuous(breaks = c(1985,1990,1995,2000,2005,2010, 2015,2020)) +
-  theme_classic() #histogram year of study 
-StudyYear <- StudyYear + geom_vline(xintercept=2001, linetype="dashed", size = 1) #add 9/11 line
-StudyYear <- StudyYear + geom_vline(xintercept=2004, linetype="dashed", size = 1) #add line
-StudyYear <- StudyYear + geom_vline(xintercept=2015, linetype="dashed", size = 1) #add ISIS line
-StudyYear <- StudyYear + geom_label(data = dat_studies, 
-                                    aes(x=2001, y=27, label = "9/11"),
-                                    size=8) #add 9/11 label
-StudyYear <- StudyYear + geom_label(data = dat_studies, 
-                                    aes(x=2007, y=35, label = "Madrid & \n Israel-Palestine"),
-                                    size=6) #add label
-StudyYear <- StudyYear + geom_label(data = dat_studies, 
-                                    aes(x=2014, y=44, label = "IS Attacks"),
-                                    size=8) #add ISIS label
-StudyYear <- StudyYear + mytheme
-
-# year of publication
-
-describe(dat_reports$Year) 
-# Figure 2B
-PubYear <- ggplot(dat_reports, aes(x=Year)) + 
-  geom_histogram(binwidth=1, 
-                 color="#000000", fill="#939598") +
-  labs(title ="Year of Publication", x = "to fill some space", y = "") +
-  scale_y_continuous(breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45)) +
-  scale_x_continuous(breaks = c(1985,1990,1995,2000,2005,2010, 2015,2020)) +
-  theme_classic() #histogram year of study 
-PubYear <- PubYear + geom_vline(xintercept=2001, linetype="dashed", size = 1) #add 9/11 line
-PubYear <- PubYear + geom_vline(xintercept=2015, linetype="dashed", size = 1) #add ISIS France line
-PubYear <- PubYear + geom_label(data = dat_reports,
-                                aes(x=2001, y=27, label = "9/11"),
-                                size=8) #add 9/11 label
-PubYear <- PubYear + geom_label(data = dat_reports, 
-                                aes(x=2014, y=44, label = "IS Attacks"),
-                                size=8) #add ISIS label
-PubYear <- PubYear + mytheme
-
-####### Terrorism measures, incl. cognitive and affective reactions ######
-
-# IV measurements used 
-summary(as.factor(dat$IV_Code))
-
-#wrangling
-dat$TerrorMeasure[dat$IV_Code==1] <- "Acts of violence"
-dat$TerrorMeasure[dat$IV_Code==2] <- "Acts of violence"
-dat$TerrorMeasure[dat$IV_Code==3] <- "Threat"
-dat$TerrorMeasure[dat$IV_Code==4] <- "Threat"
-dat$TerrorMeasure[dat$IV_Code==5] <- "Other"
-dat$TerrorMeasure[dat$IV_Code==6] <- "Reported exposure"
-dat$TerrorMeasure[dat$IV_Code==7] <- "Reported exposure"
-dat$TerrorMeasure[dat$IV_Code==8] <- "Reported exposure"
-dat$TerrorMeasure[dat$IV_Code==9] <- "Threat"
-dat$TerrorMeasure[dat$IV_Code==10] <- "Threat"
-dat$TerrorMeasure[dat$IV_Code==11] <- "Fear"
-dat$TerrorMeasure[dat$IV_Code==12] <- "Anger"
-dat$TerrorMeasure[dat$IV_Code==13] <- "Other"
-dat$TerrorMeasure[dat$IV_Code==14] <- "Other"
-dat$TerrorMeasure[dat$IV_Code==15] <- "Other"
-dat$TerrorMeasure[dat$IV_Code==16] <- "Other"
-
-dat$TerrorMeasure <- as.factor(dat$TerrorMeasure)
-table(dat$TerrorMeasure)
-prop.table(table(dat$TerrorMeasure))
-table(dat$ExactAttack) #which attacks are studied?
-prop.table(table(dat$ExactAttack)) #which attacks are studied?
-
-#visualization: Figure 2C
-tmdat <- data.frame(prop.table(table(dat$TerrorMeasure)))
-TerrorMeasures <- ggplot(tmdat, aes(x = reorder(Var1, -Freq), y = Freq)) +
-  geom_bar(stat="identity", width=0.7,
-           color="#000000", fill="#939598") +
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
-  scale_y_continuous(labels = scales::percent,
-                     limits = c(0,.6),
-                     breaks = c(0,.1,.2,.3,.4,.5,.6)) +
-  labs(title = "Terrorism Measures", x="", y = "") +
-  theme_classic() 
-TerrorMeasures <- TerrorMeasures + mytheme
-
-# type of terrorism
-summary(as.factor(dat$Type))
-
-#wrangling
-dat$TerrorType[dat$Type==0] <- "No ideology"
-dat$TerrorType[dat$Type==1] <- "Islamist"
-dat$TerrorType[dat$Type==2] <- "Extreme right"
-dat$TerrorType[dat$Type==3] <- "Other"
-dat$TerrorType[dat$Type==4] <- "Other"
-dat$TerrorType[dat$Type==5] <- "State terror"
-dat$TerrorType[dat$Type==6] <- "Other"
-dat$TerrorType <- as.factor(dat$TerrorType)
-summary(dat$TerrorType)
-prop.table(table(dat$TerrorType))
-
-#visualization: Figure 2D
-ttdat <- data.frame(prop.table(table(dat$TerrorType)))
-TerrorType <- ggplot(ttdat, aes(x = reorder(Var1, -Freq), y = Freq)) +
-  geom_bar(stat="identity", width=0.7,
-           color="#000000", fill="#939598") +
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
-  scale_y_continuous(labels = scales::percent,
-                     breaks = c(0,.1,.2,.3,.4,.5,.6)) +
-  labs(title = "Type of Terrorism", x = "", y = "") +
-  theme_classic() 
-TerrorType <- TerrorType + mytheme
-
-jpeg("Figures/Fig2.jpeg", width = 15, height = 16, units = 'in', res = 300)
-ggarrange(StudyYear, PubYear, 
-          TerrorMeasures, TerrorType,
-          labels = c("(A)", "(B)", "(C)", "(D)"),
-          font.label = list(size = 22, color = "black"),
-          ncol = 2, nrow = 2) #arrange all plots
-dev.off() #safe picture in high resolution.
-```
 

### 2024-02-13 scripts/00-simulation.R
delete

@@ -1,123 +1,0 @@
-#### Preamble ####
-# Purpose: Simulating data on survery results 
-# Authors: Finn Korol, Jayden Jung, Sofia Sellitto
-# Contact: finn.korol@mail.utoronto.ca, jayden.jung@mail.utoronto.ca, sofia.sellitto@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: none
-
-library(here)
-library(readr)
-
-set.seed(3)
-
-#participant values used in analysis in relation to survey scores
-age <- sample(x = 1:90, size = 100, replace = TRUE)
-# data used for our figures will only be from waves 2 and 4 of surveying
-wave <- sample(c(2,4), size = 100, replace = TRUE)
-age_group <- sample(c('18-29','30-39','40-49','50-59','60 and older'), size = 100, replace = TRUE)
-gender <- sample(c('Male','Female'), size = 100, replace = TRUE)
-state <- sample(c('State A','State B', 'State C', 'State D'), size = 100, replace = TRUE)
-citizenship <- sample(x = 0:1, size = 100, replace = TRUE)
-marital <- sample(c('widowed', 'married', 'commonlaw', 'single', 'divorced/separated'), size = 100, replace = TRUE)
-religion <- sample(c('catholic christian', 'protestant christian', 'jewish', 'muslim', 'nondenominational', 'atheist', 'agnostic', 'Eastern Religion'), size = 100, replace = TRUE)
-occupation <- sample(c('student', 'unemployed', 'retired', 'civil servant', 'self-employed', 'sick/on leave', 'employee'), size = 100, replace = TRUE)
-income <- sample(c('under 500', '500-1500', '1500-2500', '2500-3500', '3500-4500', '4500-5500', 'over 5500'), size = 100, replace = TRUE)
-household_size <- sample(x = 0:10, size = 100, replace = TRUE)
-
-#important survey scores
-only_means <- sample(x = 1:4, size = 100, replace = TRUE)
-condemn <- sample(x = 1:4, size = 100, replace = TRUE)
-justified <- sample(x = 1:4, size = 100, replace = TRUE)
-message <- sample(x = 1:4, size = 100, replace = TRUE)
-prevent <- sample(x = 1:4, size = 100, replace = TRUE)
-
[…]

### 2024-02-13 scripts/01-test.R

@@ -1,23 +1,0 @@
-#### Preamble ####
-# Purpose: Testing simulated survey data
-# Author: Finn Korol, Jayden Jung, Sofia Sellitto
-# Data: survey_sim.csv
-# Contact: finn.korol@mail.utoronto.ca, jayden.jung@mail.utoronto.ca, sofia.sellitto@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: Have run 00-simulation.R and have survey_sim.csv saved
-
-# read in simulation file
-survey_sim <- read_csv(here::here("inputs/data/survey_sim.csv"), 
-                       show_col_types = FALSE)
-
-#checking bound minimum
-min(survey_sim$age, na.rm=TRUE) > 0
-
-#checking bound maximum
-max(survey_sim$age, na.rm=TRUE) < 110
-
-#checking that number of unique row values is appropriate
-length(unique(survey_sim$wave)) < 4
-
-#checking for allowed col types
-any((survey_sim$only_means | survey_sim$condemn | survey_sim$justified | survey_sim$message | survey_sim$prevent)%%1==0)

### 2024-02-13 inputs/code/02-meta-analysis.R
update

@@ -1,2552 +1,0 @@
-# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
-# PROJECT:    How Terrorism Does (and Does Not) Affect Citizens' 
-#             Political Attitudes: A Meta-Analysis. 
-# AUTHOR:     Amelie Godefroidt
-# CONTACT:    amelie.godefroidt@ntnu.no
-# 
-# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
-# This R file contains the code necessary to replicate all main results,
-# including the descriptive statistics, meta-analysis, and meta-regressions.
-# 
-# Last successful replication: 01.11.2021
-# 
-# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
-
-# first things first: set your settings.
-
-rm(list=ls())
-setwd("inputs/code/") #set your directory
-options("scipen"=100, "digits"=8) #set digits
-getwd()
-
-
-###### Install and load packages ###### 
-
-# ipak function: install and load multiple R packages.
-# check to see if packages are installed. Install them if they are not, then load them into the R session.
-
-ipak <- function(pkg){  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
-if(length(new.pkg)) install.packages(new.pkg, dependencies = TRUE)
-sapply(pkg, require, character.only = TRUE)
-}
-
-packages <- c("readxl", "haven", "psych", "dplyr", "DescTools", "broom", "cowplot",
-              "pwr", "esc", "metaSEM", "metafor", "metaviz", "PerformanceAnalytics", 
-              "ggplot2", "ggpubr", "wesanderson", "stringr", "dotwhisker") 
-ipak(packages)
-
-
-###### Import and split data ###### 
-
-dat <- read_excel("inputs/data/02-metaanalysis-data.xlsx", sheet = "Data", 
-                  col_names = TRUE, skip = 3)
-
-### dataframe of studies
-dat_studies <- dat[c(1:87)] #studies.
-dat_studies <- group_by(dat_studies, ID_RS) %>% slice(1)
[…]

### 2024-02-13 inputs/code/04-shiny-data.R

@@ -1,141 +1,0 @@
-# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
-# PROJECT:    How Terrorism Does (and Does Not) Affect Citizens' 
-#             Political Attitudes: A Meta-Analysis. 
-# AUTHOR:     Amelie Godefroidt
-# CONTACT:    amelie.godefroidt@ntnu.no
-# 
-# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
-# This R file contains the code necessary to clean the data for the Shiny App
-
-# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
-
-#rm(list=ls())
-#set your own directory
-#setwd("../Godefroidt_2021_ReplicationFiles/") 
-
-
-#get necessary packages
-ipak <- function(pkg){  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
-if(length(new.pkg)) install.packages(new.pkg, dependencies=TRUE)
-sapply(pkg, require, character.only=TRUE) }
-packages <- c("dplyr", "readxl") 
-ipak(packages)
-
-
-###### A. GET THE DATA ######
-#Full Data-Set of Meta-Analysis
-mydata <- read_excel("data/02-metaanalysis-data.xlsx", sheet = "Data", col_names = TRUE, skip = 3)
-myotherdata <- read_excel("data/01-sampling-information.xlsx", sheet = "Final sample (N=241)", col_names = TRUE)
-
-#Sub-Set Used for Shiny App
-shinydata <- mydata %>%
-  select(Fisher, Variance_F, SE_F, ID_R, ID_ES_Unique,
-    country = Country, 
-    design = TypeStudy,
-    terrortype = Type,
-    outcome = PA_Category)
-
-
-###### B. RECODE THE DATA: Make Cleaner Selection Variables ######
-#### 1. Re-categorize country of study #### 
-summary(as.factor(shinydata$country))
-shinydata$country[shinydata$country=="US"] <- "United States"
-shinydata$country[shinydata$country=="Israel" |
[…]

### 2024-02-13 outputs/paper/paper.qmd
update

@@
 ---
-title: "Harmful Anti-Foreign Sentiments based on Concern for Competition Should be Recognized and Addressed"
-author: "Jayden Jung, Finn Korol, Sofia Sellitto"
-thanks: "Code and data are available at: https://github.com/jj-andj/mate-comp-hate ; Replication on Social Science Reproduction platform available at: https://doi.org/10.48152/ssrp-qg85-cb34"
-date: "February 17, 2023"
+title: "Start with the literature: assessthe empirical evidence for the relationship between ter-rorism and political attitudes"
+author: "Bernice(Yixuan) Bao, Zheng(Zeb) Yang, Jingcheng Yang"
+thanks: "Code and data are available at: https://github.com/BerniceBao/Terrorism-Political-Attitude ; Replication on Social Science Reproduction platform available at: https://doi.org/10.48152/ssrp-qg85-cb34"
+date: "February 13, 2024"
 date-format: long
@@
 The author stressed that to "meaningfully compare and pool effect sizes, all correlations must also reflect the relation between terrorism and sociopolitical attitudes in the same direction."
+
 # Results

### 2024-02-13 outputs/paper/paper.qmd
Improve the writing

@@
     geometry: margin = 1in
-    abstract: "Immigration and asylum-seeking are common topics of discussion in our globalized world, about which many Westerners hold opinions due to certain personal justifications.
-This paper replicates data analysis of the perceptions of non-immigrant German males towards refugees in municipalities where males overpopulate females.
-We apply secondary research regarding Canadian rates of immigration and gender imbalances in Alberta and raise concerns regarding the possibly generalizable nature of the findings in Germany.
-As this issue specifically affects minority groups experiencing prejudice, we place great emphasis on the weight of this discussion and call for future investigations of this field to inform policies and initiatives to address racism and hate crimes."
+    abstract: "Over time, many scholars have attempted to investigate the impact of terrorism on citizens' political beliefs.
+This paper replicates data analysis of this body of literature, examining around 325 studies conducted between 1985 and 2020, which results affirm that terrorism is correlated—albeit to a small but meaningful extent—with increased hostility towards outgroups, tendencies towards political conservatism, and the occurrence of rally-'round-the-flag effects.
+Overall, this meta-analysis consolidates existing evidence, discerns consistent findings across different situations, and identifies significant areas of knowledge deficiency.
+However, since the effects of terrorism vary widely, with studies focusing on Islamist violence, carried out in the United States or Israel, we raise concerns regarding the possibly generalizable nature of the findings.
+It is essential to place great emphasis on the weight of this discussion and call for future investigations of the reaction of political attitudes on terrorism."
     number-sections: true
@@
 
-In Canada, hate crimes based on race and ethnicity increased by 80% in 2020, with the highest number of incidents targeting black individuals, followed by east and southeast Asians, indigenous individuals, and the lowest number of victims being South Asian individuals [@moreau_wang_2022].
-Seeing that Canada is one of the most diverse countries in the world, welcoming 405,999 permanent immigrants in 2021 [@government_of_canada_2022] and 130,125 refugees in 2020 [@macrotrends], these statistics concerning the increase of hate crimes pose a real and visceral threat to a large proportion of Canadian residents.
+Terrorists, distinct from ordinary criminals, are perceived to advocate for a political cause, often resorting to violent tactics to garner public attention and influence public opinion.
+Hence, within political science, there's a prevalent belief that the effectiveness of terrorism hinges on assumptions regarding its impact on public sentiment.
+Essentially, public opinion is deemed crucial in understanding the dynamics of terrorism.
+Yet, the extent and manner in which terrorism affects "ordinary citizens" remain ambiguous.
+Are citizens more inclined towards supporting authoritarian leaders in times of terror?
+Are they willing to sacrifice civil liberties and democratic values for enhanced security post-attack?
+Additionally, what or who exactly constitutes "terrorism"?
 
-There are many factors that contribute to the increase in hate crimes in Canada.
-However, with the rise of far-right discourse in the United States, anti-immigrant and anti-refugee rhetoric is becoming more prevalent in Canada.
-These negative attitudes and actions towards immigrants, refugees, and marginalized individuals can be the result of various structural and personal factors, including increased competition in the job and housing markets, resource scarcity, misguided beliefs about crime rates, illness, welfare dependency, and fears of losing national identity.
-Despite this, one factor that has received little attention until recently is the impact of mate competition in dating and marriage markets on anti-refugee sentiments.
-A [-@main_paper] paper by Dancygier, Egami, Jamal, and Rischke published in the American Journal of Political Science delves into this potentially important and often-overlooked fusion of social science with ecology.
-
-In studying the opinions of German males living in municipalities with excess male populations, they find that a portion of non-immigrant German men hold the belief that refugees pose a threat to their ability to pursue German women [@main_paper].
-The study population is primarily non-immigrant German males in highly male populated municipalities.
-The estimand which we intend to replicate is the effect of mate competition on anti-refugee sentiments.
-Their finding suggests that hate crimes increase where non-immigrant German men are disadvantaged in their local dating markets [@main_paper].
-Using ecological evidence and originally curated survey data, the paper concludes that competition in dating and marriage markets where men outnumber women increases anti-refugee sentiments and violence [@main_paper].
+Since the tragic events of September 11, 2001 (9/11), a substantial body of literature has emerged addressing these inquiries, yielding varied conclusions.
+While some scholars express concern that public reactions to terrorism jeopardize democracy, others argue that such responses are limited or transient, and sometimes even absent.
+However, these studies often explore diverse outcomes, nations, and terrorist threats using a range of methodologies.
+Consequently, there's a lack of systematic scrutiny regarding how the public's response to terrorism has been studied, resulting in limited understanding of this field's key characteristics and how they influence conclusions.
 

### 2024-02-14 outputs/paper/paper.qmd
edits

@@
 
+```{r}
+#| label: fig-collection
+#| fig-cap: "Panel A displays the number of unique studies conducted over time, Panel B the number of manuscripts published over time, Panel C the frequency of used terrorism measures (in percentage), and Panel D the frequency of studied types of terrorism (in percentage)"
+#| echo: false
+#| message: false
+#| warning: false
+
+library(readxl)
+library(haven)
+library(psych)
+library(dplyr)
+library(DescTools)
+library(broom)
+library(cowplot)
+library(pwr)
+library(esc)
+library(metaSEM)
+library(metafor)
+library(metaviz)
+library(PerformanceAnalytics)
+library(ggplot2)
+library(ggpubr)
+library(wesanderson)
+library(stringr)
+library(dotwhisker)
+
+dat <- read_excel("/cloud/project/raw/data/02-metaanalysis-data.xlsx", sheet = "Data", 
+                  col_names = TRUE, skip = 3)
+
+### dataframe of studies
+dat_studies <- dat[c(1:87)] #studies.
+dat_studies <- group_by(dat_studies, ID_RS) %>% slice(1)
+#sum(dat_studies$ESS, na.rm = TRUE) #number of unique respondents
+
+### dataframe of reports
+dat_reports <- dat[c(1:87)] #reports/publications.
+dat_reports <- group_by(dat_reports, ID_R) %>% slice(1)
+
+### set wished layout settings
+mytheme <- theme(plot.title = element_text(face = "bold", size = (13), colour = "black"), 
+                 axis.text = element_text(size = (6), colour = "black"),
+                 axis.ticks.length = unit(0.5, "cm"),
+                 axis.title.y = element_text(size = (6), colour = "black"),
+                 axis.title.x = element_text(size = (6), colour = "white"))
+
+# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
+###### A. DESCRIPTIVES: THE FIELD OF EMPIRICAL TERRORISM STUDIES ######
+# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ #
+
+## mean ES's per report (reported in footnote 6)
+#format(round(psych::describe(aggregate(Correlation ~ ID_R, data = dat, FUN = length)),3), #nsmall=3)
+
+StudyYear <- ggplot(dat_studies, aes(x=StudyYear)) + 
+  geom_histogram(binwidth=1,
+                 color="#000000", fill="#939598") +
+  labs(x="to fill some space", y = "", title = "Year of Data Collection") +
+  scale_y_continuous(breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45)) +
+  scale_x_continuous(breaks = c(1985,1990,1995,2000,2005,2010, 2015,2020)) +
+  theme_classic() #histogram year of study 
+StudyYear <- StudyYear + geom_vline(xintercept=2001, linetype="dashed", size = 1) #add 9/11 line
+StudyYear <- StudyYear + geom_vline(xintercept=2004, linetype="dashed", size = 1) #add line
+StudyYear <- StudyYear + geom_vline(xintercept=2015, linetype="dashed", size = 1) #add ISIS line
+StudyYear <- StudyYear + geom_label(data = dat_studies, 
+                                    aes(x=2001, y=27, label = "9/11"),
+                                    size=4) #add 9/11 label
+StudyYear <- StudyYear + geom_label(data = dat_studies, 
+                                    aes(x=2007, y=35, label = "Madrid & \n Israel-Palestine"),
+                                    size=2) #add label
+StudyYear <- StudyYear + geom_label(data = dat_studies, 
+                                    aes(x=2014, y=44, label = "IS Attacks"),
+                                    size=2) #add ISIS label
+StudyYear <- StudyYear + mytheme
+
+# year of publication
+
+#describe(dat_reports$Year) 
+# Figure 2B
+PubYear <- ggplot(dat_reports, aes(x=Year)) + 
+  geom_histogram(binwidth=1, 
+                 color="#000000", fill="#939598") +
+  labs(title ="Year of Publication", x = "to fill some space", y = "") +
+  scale_y_continuous(breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45)) +
+  scale_x_continuous(breaks = c(1985,1990,1995,2000,2005,2010, 2015,2020)) +
+  theme_classic() #histogram year of study 
+PubYear <- PubYear + geom_vline(xintercept=2001, linetype="dashed", size = 1) #add 9/11 line
+PubYear <- PubYear + geom_vline(xintercept=2015, linetype="dashed", size = 1) #add ISIS France line
+PubYear <- PubYear + geom_label(data = dat_reports,
+                                aes(x=2001, y=27, label = "9/11"),
+                                size=2) #add 9/11 label
+PubYear <- PubYear + geom_label(data = dat_reports, 
+                                aes(x=2014, y=44, label = "IS Attacks"),
+                                size=2) #add ISIS label
+PubYear <- PubYear + mytheme
+
+####### Terrorism measures, incl. cognitive and affective reactions ######
+
+# IV measurements used
+
+#wrangling
+dat$TerrorMeasure[dat$IV_Code==1] <- "Acts of violence"
+dat$TerrorMeasure[dat$IV_Code==2] <- "Acts of violence"
+dat$TerrorMeasure[dat$IV_Code==3] <- "Threat"
+dat$TerrorMeasure[dat$IV_Code==4] <- "Threat"
+dat$TerrorMeasure[dat$IV_Code==5] <- "Other"
+dat$TerrorMeasure[dat$IV_Code==6] <- "Reported exposure"
+dat$TerrorMeasure[dat$IV_Code==7] <- "Reported exposure"
+dat$TerrorMeasure[dat$IV_Code==8] <- "Reported exposure"
+dat$TerrorMeasure[dat$IV_Code==9] <- "Threat"
+dat$TerrorMeasure[dat$IV_Code==10] <- "Threat"
+dat$TerrorMeasure[dat$IV_Code==11] <- "Fear"
+dat$TerrorMeasure[dat$IV_Code==12] <- "Anger"
+dat$TerrorMeasure[dat$IV_Code==13] <- "Other"
+dat$TerrorMeasure[dat$IV_Code==14] <- "Other"
+dat$TerrorMeasure[dat$IV_Code==15] <- "Other"
+dat$TerrorMeasure[dat$IV_Code==16] <- "Other"
+
+#dat$TerrorMeasure <- as.factor(dat$TerrorMeasure)
+
+#visualization: Figure 2C
+tmdat <- data.frame(prop.table(table(dat$TerrorMeasure)))
+TerrorMeasures <- ggplot(tmdat, aes(x = reorder(Var1, -Freq), y = Freq)) +
+  geom_bar(stat="identity", width=0.7,
+           color="#000000", fill="#939598") +
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
+  scale_y_continuous(labels = scales::percent,
+                     limits = c(0,.6),
+                     breaks = c(0,.1,.2,.3,.4,.5,.6)) +
+  labs(title = "Terrorism Measures", x="", y = "") +
+  theme_classic() 
+TerrorMeasures <- TerrorMeasures + mytheme
+
+# type of terrorism
+
+#wrangling
+dat$TerrorType[dat$Type==0] <- "No ideology"
+dat$TerrorType[dat$Type==1] <- "Islamist"
+dat$TerrorType[dat$Type==2] <- "Extreme right"
+dat$TerrorType[dat$Type==3] <- "Other"
+dat$TerrorType[dat$Type==4] <- "Other"
+dat$TerrorType[dat$Type==5] <- "State terror"
+dat$TerrorType[dat$Type==6] <- "Other"
+#dat$TerrorType <- as.factor(dat$TerrorType)
+
+#visualization: Figure 2D
+ttdat <- data.frame(prop.table(table(dat$TerrorType)))
+TerrorType <- ggplot(ttdat, aes(x = reorder(Var1, -Freq), y = Freq)) +
+  geom_bar(stat="identity", width=0.7,
+           color="#000000", fill="#939598") +
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
+  scale_y_continuous(labels = scales::percent,
+                     breaks = c(0,.1,.2,.3,.4,.5,.6)) +
+  labs(title = "Type of Terrorism", x = "", y = "") +
+  theme_classic() 
+TerrorType <- TerrorType + mytheme
+
+ggarrange(StudyYear, PubYear, 
+          TerrorMeasures, TerrorType,
+          labels = c("(A)", "(B)", "(C)", "(D)"),
+          font.label = list(size = 10, color = "black"),
+          widths = 10,
+          heights = 10,
+          ncol = 2, nrow = 2) #arrange all plots
+
+```
+
 As depicted in @fig-collection(A) and (B), scholarly interest in exploring the link between terrorism and public attitudes notably began following the 9/11 attacks, and received further impetus following the 2015–16 Islamic State (IS) attacks.
@@
 Table 1 demonstrates that...
+
+```{r}
+#| label: table
+#| tbl-cap: "0000000000000000000"
+#| echo: false
+#| message: false
+#| warning: false
+
+library(knitr)
+library(kableExtra)
+library(dplyr)
+
+knitr::kable(
+  tibble(OutcomeType = c("Outgroup hostility","Conservative shift","Rally effects"),
+         k = c(645,728,360),
+         j = c(126,144,72),
+         Zr = c(0.126,0.132,0.090),
+         LBCI = c("[0.094;0.159]","[0.108;0.156]","[0.055;0.127]")
+  )
+)
+```
 

### 2024-02-15 outputs/paper/paper.qmd
edits

@@
 
-dat <- read_excel("/cloud/project/raw/data/02-metaanalysis-data.xlsx", sheet = "Data", 
+dat <- read_excel("/cloud/project/inputs/data/02-metaanalysis-data.xlsx", sheet = "Data", 
                   col_names = TRUE, skip = 3)
@@
           widths = 10,
-          heights = 10,
+          heights = 15,
           ncol = 2, nrow = 2) #arrange all plots
@@
          LBCI = c("[0.094;0.159]","[0.108;0.156]","[0.055;0.127]")
-  )
+  ),
+  caption = "Relationship between Terrorism and Political Attitudes"
 )

### 2024-02-15 outputs/paper/paper.qmd
renew the idea of conclusion

--- 2024-02-14 outputs/paper/paper.qmd
@@
 
-Our paper will follow a reproduction of Dancygier, Egami, Jamal, and Rischke's findings and apply a Canadian-facing lens to discuss its implications on local Canadian populations and increased anti-refugee/ immigrant sentiments and violence.
+A [-@main_paper] paper by Amélie Godefroidt from Norwegian University of Science and Technology published in the American Journal of Political Science delves into the moderator analyses, in order to understand how contextual factors influence the relationship between terrorism and political attitudes.
+The study discusses an extended model for analyzing the relationship between terrorism and political attitudes, incorporating characteristics of manuscripts and effect sizes as moderators.
+
+The study examines data from various sources, and details the characteristics of studies in the field, including the types of terrorism studied, geographical focus, and methodological approaches.
+It notes gaps in longitudinal studies, the dominance of convenience samples, and the focus on majority group perspectives.
+The study finds that terrorism is associated with increased outgroup hostility, political conservatism, and rally-'round-the-flag responses, though the effects are relatively small.
+Although the discussion section reflects on the findings, the limitations of the existing literature still exist, such as the predominant focus on Islamist terrorism and the limited geographical scope.
+It calls for a more nuanced understanding of public responses to terrorism, considering the potential long-term consequences.
+
+Our paper will follow a reproduction of Amélie Godefroidt's implications on the relationship between terrorism and political attitudes.
 Our paper seeks to replicate their two following research claims, (1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats and (2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians.
@@
 
-In their paper, Dancygier, Egami, Jamal, and Rischke examine the ethical implication of using experimental methodologies to investigate their research topic.
-By using descriptive data in the form of surveys they are able to investigate the opinions of non-immigrant German males and their perception of mate competition and its translation to anti-refugee violence.
-By avoiding experimental trials, they were able to explore their topic without provoking anti-refugee sentiment [@main_paper].
-While conducting experimental trials on this topic of research is considered unethical, surveys and questionnaires may have a tendency to give respondents the impression that their opinions are commonly shared or even accurate.
-By being presented with a platform to express their perception of mate competition and if they agree that violence towards refugees is the only way to garner the attention of German politicians, respondents may feel that their opinions are incorrectly justified.
-This then has the potential to translate to violence towards German refugees.
+In their paper, studying terrorism and political attitudes [@main_paper] raises significant ethical considerations due to the potential impact on individuals and communities.
+For instance, examining public responses to terrorism may inadvertently contribute to the stigmatization of certain groups, particularly when findings are not adequately contextualized or interpreted.
+Moreover, researchers must ensure the well-being and rights of participants by obtaining informed consent and protecting their confidentiality.
+For example, studies employing self-report measures to assess exposure to terrorism should carefully consider the potential psychological distress participants may experiensce when recalling traumatic events [@main_paper].
+Additionally, researchers must navigate the sensitive nature of studying terrorism across diverse cultural contexts, being mindful of cultural differences in understanding and interpreting acts of violence.
 
@@
 
-Ethical implications and biases arise naturally when collecting quantitative and qualitative data.
-In their paper, Dancygier, Egami, Jamal, and Rischke use online survey platforms to assess if Germans living in areas with greater populations of men who experience turmoil in the mating market are more likely to perceive competition between themselves and refugees, moreover, does this ideology predict hate crime support [@main_paper].
-The authors attempted to address ethical concerns and statistical biases by utilizing control groups and replicating their study with different samples and polling firms.
-However, one potential bias that is challenging to control for is the presence of sampling bias [@main_paper].
-Sampling bias occurs when participants in a study are not representative of the estimand or the ideal population of interest.
-One method to control for this bias is simple random sampling, where participants are chosen by chance.
-Meaning that every individual in the population has an equal chance of being selected.
-However, in their study, they were unable to utilize simple random sampling.
-Instead attempted to make their survey results representative by conducting 4 waves of surveys meant to be representative of age, gender and geographical region [@main_paper].
-Despite their effort, their survey results may not be entirely representative as individuals who have a strong interest in the subject matter are more likely to participate, meaning they do not reflect the views of all non-immigrant German males [@main_paper].
+Bias can manifest in various stages of the research process, impacting the validity and reliability of findings.
+To mitigate bias, researchers should employ rigorous methodologies and transparent reporting practices.
+For example, when selecting participants, researchers should strive for representative samples to minimize selection bias.
+Moreover, controlling for confounding variables, such as political ideology or prior exposure to terrorism, helps ensure that observed associations are not spurious.
+Additionally, researchers should be transparent about potential sources of bias in their data analysis methods, such as the exclusion of certain demographic groups or the use of subjective coding criteria.
+By acknowledging and addressing potential biases, researchers can enhance the credibility and robustness of their findings.
 
@@
 
-Being a reproduction, much of our analysis was limited to the original survey circumstances captured in [@main_paper].
-Despite the survey being long, it can not be considered to be comprehensive.
-This prevented us from exploring other relationships in the data.
-For example, in this German context, it would have been interesting to look into sentiments toward the treatment of communities experiencing genocide during the history of World War 2.
-Our connection of findings to the Albertan context was also limited by this cultural and geographical separation from our data.
-
-Due to the heteronormative nature of this study's data, our analysis was also not able to be fully representative of the German population as [@main_paper]'s authors described.
-While this is not to be surprised from an ecological context of mating behaviour, perhaps gay men would have been found to experience anti-refugee sentiment as well as an extension of the mate competition argument.
-
-There were also limitations associated with missing and limited data in our set.
-For example, in our analysis depicted in @fig-excess, fewer than 300 observations were represented in the oldest age group, which these authors doubted was enough for a meaningful evaluation.
+Despite its contributions, the article acknowledges several limitations that warrant consideration.
+For instance, the predominance of studies focused on Islamist terrorism in Western contexts limits the generalizability of findings to other types of terrorism and cultural contexts.
+This bias may stem from the availability of data or the framing of terrorism within public discourse.
+Moreover, the reliance on cross-sectional designs and self-report measures introduces potential biases, such as recall bias or social desirability bias.
+Additionally, the limited representation of studies from regions most affected by terrorism, such as Afghanistan or Syria, hinders the comprehensive understanding of public responses to terrorism.
+These limitations underscore the need for future research to address these gaps and provide a more nuanced understanding of the phenomena under study.
 
@@
 
-As suggested in their original paper, Dancygier, Egami, Jamal, and Rischke call for future research to investigate how their findings apply to less ethnically distinct groups, with less aggressive media attention and under non-heteronormative roles [@main_paper].
-They further call for tests in ethnonational countries and in regions where females overpopulate males to see if their findings apply to women [@main_paper].
-As Global migration and refuge continue to increase, we anticipate that this field of study will become increasingly significant.
-It is thus crucial to expand on their findings to assess how they apply in varying nations.
-This is in hopes to create policy changes and account for preventative measures to avoid increased anti-refugee sentiments and hate crimes caused by sex-driven competition.
-We further hope for this field of research to be applied under less heteronormative circumstances and work to account for queer-identifying individuals.
+Moving forward, future research should prioritize addressing the identified limitations and advancing knowledge in the field.
+For example, comparative studies across different types of terrorism and ideological motivations can elucidate the differential impact on political attitudes and behaviors.
+Longitudinal studies are also essential for capturing the dynamic nature of public responses to terrorism over time.
+Moreover, qualitative research methods, such as interviews or focus groups, can provide insights into the underlying mechanisms and individual experiences of terrorism.
+Additionally, exploring the role of contextual factors, such as media framing or political discourse, can enrich our understanding of the complex interplay between terrorism and political attitudes.
+By pursuing these avenues of research, scholars can contribute to a more comprehensive understanding of the phenomena while upholding ethical standards and methodological rigor.
 

### 2024-02-15 outputs/paper/paper.qmd
improve the writing of discussion

@@
 It contains 76 column and 1733 observations.
-A randomized selection of manuscripts (±15% of the total sample) was used to pilot the code book and make any necessary revisions.
-The columns can be divided into fifth major data categories.
+A randomized selection of manuscripts (±15% of the total sample) was used to pilot the code book and make any necessary revisions.（Godefroidt, 2022) The columns can be divided into fifth major data categories.
 The first part of the variables are identity information of the data such as the author name, year of the study, the sample size and the general population.
@@
 For example, nationalism and institutional trust, socio-economic conservatism, support for policies that pertains an outgroup.
-The last part lists the analysis technical data that will be used in meta-analysis code such as Fisher's Z correlation, Regression and so on.
+The last part lists the technical data that will be used in meta-analysis code such as Fisher's Z correlation, regression and so on.
 From the original survey data, each variable correlates with a survey question asked to participants.
@@
 
-In order to better present our replication of the results, The following are measurments of public political opinions provided by the author.
-They are classfied into 4 categories given in the orignal paper.
+In order to better present our replication of the results, The following are measurements of public political opinions provided by the author.
+They are classfied into 4 categories given in the original paper.
 We selected some important measures
@@
 
-In this paper we will replicate figure 2 and table2 of the orginal paper.
+In this paper we will replicate figure 2 and table2 of the original paper.
 Fortunately, the author has already compressed all the analysis into one coding file.
@@
 In terms of the analysis method, Pearson's correlation coefficient is used.
-According to the orignal paper, the manuscripts of the data they collected used various statistical method.
+According to the original paper, the manuscripts of the data they collected used various statistical method.
 For comparison purposes, each association is converted into a Pearson's correlation coefficient with the sampling variance.
-The author stressed that to "meaningfully compare and pool effect sizes, all correlations must also reflect the relation between terrorism and sociopolitical attitudes in the same direction."
+The author stressed that to "meaningfully compare and pool effect sizes, all correlations must also reflect the relation between terrorism and sociopolitical attitudes in the same direction."[@main_paper]
 
@@
 
-In this paper, we have replicated the results found by Dancygier, Egami, Jamal, and Rischke.
-Their analysis sought to explore the correlation between perceived mate competition in municipalities with excess males and its contributions to anti-refugee sentiments and higher crime rates in Germany.
-Our paper has replicated two of their major findings.
+In this reproduction we successfully replicated and proved the research result of the core findings of the original paper; the interplay between terrorism and general conservatism.
+Humans possess a natural tendency to favor members of their own group while displaying suspicion or hostility towards outsiders (Tajfel & Turner, 2019[@tajfel2019integrative]).
+This ingroup-outgroup bias serves as fertile ground for the cultivation of stereotypes, prejudice, and intergroup conflict.
+In the context of terrorism, extremist ideologies often exploit these psychological tendencies to demonize the targeted groups, portraying them as existential threats to the ingroup's identity and well-being.
+Even though political position is a person’s own opinion, but this paper used statical method and quantified the perception.
+After the public has witnessed a terrorism, they will shift to be more unwelcome of the region that terrorism stands for, which in this paper is mainly about Islamism.
+This will exacerbating pre-existing prejudices and fueling intergroup tensions.
+Following terrorist incidents, there is often a surge in xenophobic rhetoric, hate crimes, and discriminatory policies targeting marginalized communities (Huddy et al., 2005).
+This cycle of violence and retaliation perpetuates a vicious cycle of outgroup hostility, further alienating communities and creating fertile recruiting grounds for extremist ideologies.
 
-(1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats.
-
-(2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians.
-
-By replicating their results, we hope to apply a Canadian-facing lens to gain insights into Canadian dating markets, the geographical distribution of males and females and their potential impacts on anti-refugee sentiments.
-
-## Canadian Relevance: Case Study on Alberta's population ratios, dating markets and anti-refugee sentiments
-
-To investigate the relevance of Dancygier, Egami, Jamal, and Rischke's discoveries in a Canadian context, we will now explore Canada's only Province with a higher ratio of males than females.
-
-Alberta is a Province in Canada with a total population of 4,543,111 individuals.
-It is the only Canadian Province that is more heavily populated by males, with a male population of 2,282,040 compared to 2,261,071 females [@statista].
-Thus having a ratio of approximately 1.01, which is comparable to that of the 1st tercile in Figure 1.
-This means that there are about 11,000 more men than women residing in this Province.
-Part of the population gap can be explained by age.
-Alberta has a primarily young population and we typically see that as populations age they exhibit a higher female population [@edmonton_journal].
-Its trades centric economy also attracts young male migrants from across Canada [@edmonton_journal].
-
-Concerning the original paper, Alberta's population growth can be largely attributed to international immigration which has typically brought equal numbers of males and females [@edmonton_journal].
-However, according to the 2021 census, 101, 650 more males are single (not married or living common law and never married) than women [@govcan].
-Due to Alberta's young population, highly concentrated with men of working age, a comparison can be made to the term 'mating-aged' used in the original paper to describe males facing higher tensions of dating competition.
-We thus believe that similar conditions for dating and marriage markets can be made between Alberta and the German municipalities of that the 1st Tercile from Figure 1.
-
-While population demographics are comparable between that of Alberta and the 1st tercile of German municipalities in the original paper, it is difficult to suggest that potential competition in Albertan dating and marriage markets correlates to anti-refugee sentiments and violence.
-However, in addressing Albertan immigrant and refugee statistics we will aim to illustrate how these patterns found in Germany can manifest in the context of Alberta.
-Based on the 2021-2022 Annual Population Report, Alberta welcomed 12,603 immigrants and 21,434 non-permanent residents, which include refugees [@alberta_2023].
-
-While previous accounts have suggested that immigration has brought an equal number of males and females, it is safe to assume that Alberta is a growing population, subject to a population with a higher concentration of males [@edmonton_journal].
-According to a 2018 paper, at the time 6 in 10 Canadians disagreed when asked if immigration levels were too high, with 35% believing that Canada accepts too many immigrants [@globe_mail].
-However, sentiments appear less than positive in Alberta, with Albertans expressing harsher attitudes towards immigrants and refugees [@globe_mail].
-48% of Albertans at the time agreed that refugee claims are not filed from real refugees, with 62% stating that immigrants do not adopt Canadian values, about 10% higher than the national average of 51% [@globe_mail].
-The Globe and Mail suggest that part of Alberta's higher anti-refugee attitudes can be attributed to its economy and fears of competition.Dancygier, Egami, Jamal, and Rischke  find that in areas where men significantly outnumber women, there are higher levels of anti-refugee hate crimes [@main_paper].
-
-Based on these statistics, we believe that Alberta may experience a similar effect of anti-refugee sentiments in part as a result of increased immigrants/ refugees and competition in a young male-dominated population.
-However, as stated in their original paper, we call for further research to be conducted on this effect to better understand its implications on non-German countries.
+Ideological Underpinnings Ideology plays a crucial role in shaping terrorist groups and their actions.
+From nationalist movements to religious extremism, various ideologies have been exploited to justify acts of terrorism.
+For example, groups like Al-Qaeda and ISIS espouse a distorted interpretation of Islam to justify their violent campaigns, while others, such as the Irish Republican Army (IRA), are driven by nationalist aspirations (Juergensmeyer, 2003[@juergensmeyer2003terror]).
+Understanding the ideological motivations behind terrorism is essential for devising effective counterterrorism strategies that address root causes rather than merely addressing symptoms.
+In short, addressing outgroup hostility requires a holistic approach that addresses the root causes of prejudice while promoting social cohesion and resilience against extremist narratives.
+By fostering empathy, understanding, and solidarity among diverse communities, we can build a more inclusive and resilient society resilient to the influence of terrorism and extremism.
 

### 2024-02-15 outputs/paper/paper.qmd
add a bibtex

@@
 The study discusses an extended model for analyzing the relationship between terrorism and political attitudes, incorporating characteristics of manuscripts and effect sizes as moderators.
-
 The study examines data from various sources, and details the characteristics of studies in the field, including the types of terrorism studied, geographical focus, and methodological approaches.
@@
 Our paper will follow a reproduction of Amélie Godefroidt's implications on the relationship between terrorism and political attitudes.
-Our paper seeks to replicate their two following research claims, (1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats and (2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians.
+Our paper seeks to replicate their two following research claims, (1) terrorism, whether through self-reported exposure, manipulated news exposure, anxious or angry appraisals of terrorism, or terrorist risk perceptions, is related to higher levels of outgroup hostility, political conservatism, and, to a lesser extent, rally-'round-the-flag responses, and (2) public responses to terrorism, such as outgroup hostility, political conservatism, and rally-'round-the-flag effects, are particularly noticeable in the United States and when attacks are carried out by outgroup members.
 Our reproduction was conducted using the statistical programming language R [@citeR].
@@
 
-We begin our paper with a discussion of the data source, the methodologies employed in the original paper and a review of the variables used for our reproduction.
-We will then conduct a reproduction of select results to verify their findings and improve upon their accessibility.
-Our paper will conclude with a discussion of our findings where we conduct a case study to apply our findings to Alberta, Canada's only Province with a greater population of males, a discussion of ethical biases, limitations and a push for future research.
+In this paper, we commences with an overview of the data source, examining the methodologies utilized in the original study, and conducting a review of the variables employed for our replication efforts.
+Following this, we will proceed with reproducing specific results to validate their conclusions and enhance their comprehensibility.
+Finally, our paper will culminate with an analysis of our findings, an exploration of ethical considerations and biases, a discussion of the limitations encountered during the replication process, and an advocacy for further research in the field.
 

### 2024-02-15 outputs/paper/paper.qmd
add a reference

@@
 This will exacerbating pre-existing prejudices and fueling intergroup tensions.
-Following terrorist incidents, there is often a surge in xenophobic rhetoric, hate crimes, and discriminatory policies targeting marginalized communities (Huddy et al., 2005).
+Following terrorist incidents, there is often a surge in xenophobic rhetoric, hate crimes, and discriminatory policies targeting marginalized communities (Huddy et al., 2005[@huddy2005threat]).
 This cycle of violence and retaliation perpetuates a vicious cycle of outgroup hostility, further alienating communities and creating fertile recruiting grounds for extremist ideologies.

### 2024-02-15 outputs/paper/paper.qmd
change doi

@@
 author: "Bernice(Yixuan) Bao, Zheng(Zeb) Yang, Jingcheng Yang"
-thanks: "Code and data are available at: https://github.com/BerniceBao/Terrorism-Political-Attitude ; Replication on Social Science Reproduction platform available at: https://doi.org/10.48152/ssrp-qg85-cb34"
+thanks: "Code and data are available at: https://github.com/BerniceBao/Terrorism-Political-Attitude ; Replication on Social Science Reproduction platform available at: https://doi.org/10.48152/ssrp-2vrs-r095"
 date: "February 13, 2024"

### 2024-02-15 outputs/paper/paper.qmd
edits

--- 2024-02-15 outputs/paper/paper.qmd
@@
 The study discusses an extended model for analyzing the relationship between terrorism and political attitudes, incorporating characteristics of manuscripts and effect sizes as moderators.
+
 The study examines data from various sources, and details the characteristics of studies in the field, including the types of terrorism studied, geographical focus, and methodological approaches.
@@
 Our paper will follow a reproduction of Amélie Godefroidt's implications on the relationship between terrorism and political attitudes.
-Our paper seeks to replicate their two following research claims, (1) terrorism, whether through self-reported exposure, manipulated news exposure, anxious or angry appraisals of terrorism, or terrorist risk perceptions, is related to higher levels of outgroup hostility, political conservatism, and, to a lesser extent, rally-'round-the-flag responses, and (2) public responses to terrorism, such as outgroup hostility, political conservatism, and rally-'round-the-flag effects, are particularly noticeable in the United States and when attacks are carried out by outgroup members.
+Our paper seeks to replicate their two following research claims, (1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats and (2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians.
 Our reproduction was conducted using the statistical programming language R [@citeR].
@@
 
-In this paper, we commences with an overview of the data source, examining the methodologies utilized in the original study, and conducting a review of the variables employed for our replication efforts.
-Following this, we will proceed with reproducing specific results to validate their conclusions and enhance their comprehensibility.
-Finally, our paper will culminate with an analysis of our findings, an exploration of ethical considerations and biases, a discussion of the limitations encountered during the replication process, and an advocacy for further research in the field.
+We begin our paper with a discussion of the data source, the methodologies employed in the original paper and a review of the variables used for our reproduction.
+We will then conduct a reproduction of select results to verify their findings and improve upon their accessibility.
+Our paper will conclude with a discussion of our findings where we conduct a case study to apply our findings to Alberta, Canada's only Province with a greater population of males, a discussion of ethical biases, limitations and a push for future research.
 
@@
 It contains 76 column and 1733 observations.
-A randomized selection of manuscripts (±15% of the total sample) was used to pilot the code book and make any necessary revisions.（Godefroidt, 2022) The columns can be divided into fifth major data categories.
+A randomized selection of manuscripts (±15% of the total sample) was used to pilot the code book and make any necessary revisions.
+The columns can be divided into fifth major data categories.
 The first part of the variables are identity information of the data such as the author name, year of the study, the sample size and the general population.
@@
 For example, nationalism and institutional trust, socio-economic conservatism, support for policies that pertains an outgroup.
-The last part lists the technical data that will be used in meta-analysis code such as Fisher's Z correlation, regression and so on.
+The last part lists the analysis technical data that will be used in meta-analysis code such as Fisher's Z correlation, Regression and so on.
 From the original survey data, each variable correlates with a survey question asked to participants.
@@
 
-In order to better present our replication of the results, The following are measurements of public political opinions provided by the author.
-They are classfied into 4 categories given in the original paper.
+In order to better present our replication of the results, The following are measurments of public political opinions provided by the author.
+They are classfied into 4 categories given in the orignal paper.
 We selected some important measures
@@
 
-In this paper we will replicate figure 2 and table2 of the original paper.
+In this paper we will replicate figure 2 and table2 of the orginal paper.
 Fortunately, the author has already compressed all the analysis into one coding file.
@@
 In terms of the analysis method, Pearson's correlation coefficient is used.
-According to the original paper, the manuscripts of the data they collected used various statistical method.
+According to the orignal paper, the manuscripts of the data they collected used various statistical method.
 For comparison purposes, each association is converted into a Pearson's correlation coefficient with the sampling variance.
-The author stressed that to "meaningfully compare and pool effect sizes, all correlations must also reflect the relation between terrorism and sociopolitical attitudes in the same direction."[@main_paper]
+The author stressed that to "meaningfully compare and pool effect sizes, all correlations must also reflect the relation between terrorism and sociopolitical attitudes in the same direction."
 
@@
 As depicted in @fig-collection(A) and (B), scholarly interest in exploring the link between terrorism and public attitudes notably began following the 9/11 attacks, and received further impetus following the 2015–16 Islamic State (IS) attacks.
-Put differently, the figures imply that this research domain is significantly influenced by specific events.
+After terrorist attacks, the number of studies reaches its peak level and the number of manuscripts published has increased sharply in the following years.Put differently, the figures imply that this research domain is significantly influenced by specific events.
 
@@
 
-Table 1 demonstrates that...
+All Fisher's Z transformed correlation coefficients were used as inputs to a random-effects, three-level meta-analysis.
+A three-level meta-analysis assumes that observed effect sizes differ because of (1) sampling variance, (2) variance between manuscripts, and (3) variance between the correlations from within the same manuscript[@main_paper].
+Therefore, the author estimated the following model:
+$$
+y_{ij} = \beta_0 + u_{(2)j} + u_{(3)j} + e_{ij}
+$$
+where any observed effect size in manuscript j ($y_{ij}$) is assumed to be equal to an overall population effect size ($\beta_0$), plus a random deviation of the mean population effect size in manuscript j from this overall population effect size ($u_{(3)j}$), plus a random deviation of the i-th population effect size in manuscript j from the mean effect in this particular manuscript ($u_{(2)ij}$), plus a random error deviation of the observed effect size from the population effect due to sampling fluctuation ($e_{ij}$)[@main_paper].
+In plain language, a three-level approach allows me to consolidate an overall effect size using all 1,733 effect sizes (while properly accounting for clustering in the data), to study heterogeneity in effect sizes both between and within manuscripts, and to explore moderator variables that explain part of this variation between and within manuscripts[@main_paper].
+
+The extent of terrorism's association with outgroup hostility, political conservatism, or rally-'round-the-flag responses can be observed in the estimated overall correlations ($Z_r$) displayed in @table.
+Table 2 displays the estimated overall correlations ($Z_r$).
+The correlations in this table are Fisher's Z-transformed, while those reported in the text below are back-transformed to their normal correlation scale (denoted as $\widehat{\rho}$) for ease of interpretation[@main_paper].
 
@@
 #| label: table
-#| tbl-cap: "0000000000000000000"
+#| tbl-cap: "Note.
+k = number of effect sizes.
+j = number of manuscripts.
+Zr = Overall Fisher's Z correlation coefficients.
+LBCI = Likelihood-Based Confidence Interval.
+The Zr estimates are considered significant when the LBCIs do not include zero."
 #| echo: false
@@
   caption = "Relationship between Terrorism and Political Attitudes"
-)
+)#These numbers are the results from the file "Table2_calculation.qmd"
 ```
+
+@table shows that terrorism is significantly associated with outgroup hostility ($\widehat{\rho}$ = 0.126), political conservatism($\widehat{\rho}$ = 0.131), and, to a lesser extent, rally-‘round-the-flag effects ($\widehat{\rho}$ = 0.090).
+@main_paper indicates that it is important to note that all associations are relatively small, both following conventional standards and compared to other meta-analyses in the social sciences.
 
@@
 
-In this reproduction we successfully replicated and proved the research result of the core findings of the original paper; the interplay between terrorism and general conservatism.
-Humans possess a natural tendency to favor members of their own group while displaying suspicion or hostility towards outsiders (Tajfel & Turner, 2019[@tajfel2019integrative]).
-This ingroup-outgroup bias serves as fertile ground for the cultivation of stereotypes, prejudice, and intergroup conflict.
-In the context of terrorism, extremist ideologies often exploit these psychological tendencies to demonize the targeted groups, portraying them as existential threats to the ingroup's identity and well-being.
-Even though political position is a person’s own opinion, but this paper used statical method and quantified the perception.
-After the public has witnessed a terrorism, they will shift to be more unwelcome of the region that terrorism stands for, which in this paper is mainly about Islamism.
-This will exacerbating pre-existing prejudices and fueling intergroup tensions.
-Following terrorist incidents, there is often a surge in xenophobic rhetoric, hate crimes, and discriminatory policies targeting marginalized communities (Huddy et al., 2005).
-This cycle of violence and retaliation perpetuates a vicious cycle of outgroup hostility, further alienating communities and creating fertile recruiting grounds for extremist ideologies.
+In this paper, we have replicated the results found by Dancygier, Egami, Jamal, and Rischke.
+Their analysis sought to explore the correlation between perceived mate competition in municipalities with excess males and its contributions to anti-refugee sentiments and higher crime rates in Germany.
+Our paper has replicated two of their major findings.
 
-Ideological Underpinnings Ideology plays a crucial role in shaping terrorist groups and their actions.
-From nationalist movements to religious extremism, various ideologies have been exploited to justify acts of terrorism.
-For example, groups like Al-Qaeda and ISIS espouse a distorted interpretation of Islam to justify their violent campaigns, while others, such as the Irish Republican Army (IRA), are driven by nationalist aspirations (Juergensmeyer, 2003[@juergensmeyer2003terror]).
-Understanding the ideological motivations behind terrorism is essential for devising effective counterterrorism strategies that address root causes rather than merely addressing symptoms.
-In short, addressing outgroup hostility requires a holistic approach that addresses the root causes of prejudice while promoting social cohesion and resilience against extremist narratives.
-By fostering empathy, understanding, and solidarity among diverse communities, we can build a more inclusive and resilient society resilient to the influence of terrorism and extremism.
+(1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats.
+
+(2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians.
+
+By replicating their results, we hope to apply a Canadian-facing lens to gain insights into Canadian dating markets, the geographical distribution of males and females and their potential impacts on anti-refugee sentiments.
+
+## Canadian Relevance: Case Study on Alberta's population ratios, dating markets and anti-refugee sentiments
+
+To investigate the relevance of Dancygier, Egami, Jamal, and Rischke's discoveries in a Canadian context, we will now explore Canada's only Province with a higher ratio of males than females.
+
+Alberta is a Province in Canada with a total population of 4,543,111 individuals.
+It is the only Canadian Province that is more heavily populated by males, with a male population of 2,282,040 compared to 2,261,071 females [@statista].
+Thus having a ratio of approximately 1.01, which is comparable to that of the 1st tercile in Figure 1.
+This means that there are about 11,000 more men than women residing in this Province.
+Part of the population gap can be explained by age.
+Alberta has a primarily young population and we typically see that as populations age they exhibit a higher female population [@edmonton_journal].
+Its trades centric economy also attracts young male migrants from across Canada [@edmonton_journal].
+
+Concerning the original paper, Alberta's population growth can be largely attributed to international immigration which has typically brought equal numbers of males and females [@edmonton_journal].
+However, according to the 2021 census, 101, 650 more males are single (not married or living common law and never married) than women [@govcan].
+Due to Alberta's young population, highly concentrated with men of working age, a comparison can be made to the term 'mating-aged' used in the original paper to describe males facing higher tensions of dating competition.
+We thus believe that similar conditions for dating and marriage markets can be made between Alberta and the German municipalities of that the 1st Tercile from Figure 1.
+
+While population demographics are comparable between that of Alberta and the 1st tercile of German municipalities in the original paper, it is difficult to suggest that potential competition in Albertan dating and marriage markets correlates to anti-refugee sentiments and violence.
+However, in addressing Albertan immigrant and refugee statistics we will aim to illustrate how these patterns found in Germany can manifest in the context of Alberta.
+Based on the 2021-2022 Annual Population Report, Alberta welcomed 12,603 immigrants and 21,434 non-permanent residents, which include refugees [@alberta_2023].
+
+While previous accounts have suggested that immigration has brought an equal number of males and females, it is safe to assume that Alberta is a growing population, subject to a population with a higher concentration of males [@edmonton_journal].
+According to a 2018 paper, at the time 6 in 10 Canadians disagreed when asked if immigration levels were too high, with 35% believing that Canada accepts too many immigrants [@globe_mail].
+However, sentiments appear less than positive in Alberta, with Albertans expressing harsher attitudes towards immigrants and refugees [@globe_mail].
+48% of Albertans at the time agreed that refugee claims are not filed from real refugees, with 62% stating that immigrants do not adopt Canadian values, about 10% higher than the national average of 51% [@globe_mail].
+The Globe and Mail suggest that part of Alberta's higher anti-refugee attitudes can be attributed to its economy and fears of competition.Dancygier, Egami, Jamal, and Rischke  find that in areas where men significantly outnumber women, there are higher levels of anti-refugee hate crimes [@main_paper].
+
+Based on these statistics, we believe that Alberta may experience a similar effect of anti-refugee sentiments in part as a result of increased immigrants/ refugees and competition in a young male-dominated population.
+However, as stated in their original paper, we call for further research to be conducted on this effect to better understand its implications on non-German countries.
 

### 2024-02-15 outputs/paper/paper.qmd
edits

@@
 
-In this paper we will replicate figure 2 and table2 of the original paper.
+In this paper we will replicate figure 2 and table 2 of the original paper.
 Fortunately, the author has already compressed all the analysis into one coding file.
@@
 
-The extent of terrorism's association with outgroup hostility, political conservatism, or rally-'round-the-flag responses can be observed in the estimated overall correlations ($Z_r$) displayed in @table.
-Table 2 displays the estimated overall correlations ($Z_r$).
+The extent of terrorism's association with outgroup hostility, political conservatism, or rally-'round-the-flag responses can be observed in the estimated overall correlations ($Z_r$) displayed in @table-t.
+@table-t displays the estimated overall correlations ($Z_r$).
 The correlations in this table are Fisher's Z-transformed, while those reported in the text below are back-transformed to their normal correlation scale (denoted as $\widehat{\rho}$) for ease of interpretation[@main_paper].
@@
 ```{r}
-#| label: table
+#| label: table-t
 #| tbl-cap: "Note.
@@
 
-@table shows that terrorism is significantly associated with outgroup hostility ($\widehat{\rho}$ = 0.126), political conservatism($\widehat{\rho}$ = 0.131), and, to a lesser extent, rally-‘round-the-flag effects ($\widehat{\rho}$ = 0.090).
+@table-t shows that terrorism is significantly associated with outgroup hostility ($\widehat{\rho}$ = 0.126), political conservatism($\widehat{\rho}$ = 0.131), and, to a lesser extent, rally-‘round-the-flag effects ($\widehat{\rho}$ = 0.090).
 @main_paper indicates that it is important to note that all associations are relatively small, both following conventional standards and compared to other meta-analyses in the social sciences.

### 2024-02-15 outputs/paper/paper.qmd
edits

@@
 
-The extent of terrorism's association with outgroup hostility, political conservatism, or rally-'round-the-flag responses can be observed in the estimated overall correlations ($Z_r$) displayed in @table-t.
-@table-t displays the estimated overall correlations ($Z_r$).
+The extent of terrorism's association with outgroup hostility, political conservatism, or rally-'round-the-flag responses can be observed in the estimated overall correlations ($Z_r$) displayed in @tbl-t.
+@tbl-t displays the estimated overall correlations ($Z_r$).
 The correlations in this table are Fisher's Z-transformed, while those reported in the text below are back-transformed to their normal correlation scale (denoted as $\widehat{\rho}$) for ease of interpretation[@main_paper].
@@
 ```{r}
-#| label: table-t
+#| label: tbl-t
 #| tbl-cap: "Note.
@@
 
-@table-t shows that terrorism is significantly associated with outgroup hostility ($\widehat{\rho}$ = 0.126), political conservatism($\widehat{\rho}$ = 0.131), and, to a lesser extent, rally-‘round-the-flag effects ($\widehat{\rho}$ = 0.090).
+@tbl-t shows that terrorism is significantly associated with outgroup hostility ($\widehat{\rho}$ = 0.126), political conservatism($\widehat{\rho}$ = 0.131), and, to a lesser extent, rally-‘round-the-flag effects ($\widehat{\rho}$ = 0.090).
 @main_paper indicates that it is important to note that all associations are relatively small, both following conventional standards and compared to other meta-analyses in the social sciences.

### 2024-02-15 raw/02-meta-analysis.R
delete

@@ -1,2567 +1,0 @@
-# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
-# PROJECT:    How Terrorism Does (and Does Not) Affect Citizens' 
-#             Political Attitudes: A Meta-Analysis. 
-# AUTHOR:     Amelie Godefroidt
-# CONTACT:    amelie.godefroidt@ntnu.no
-# 
-# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
-# This R file contains the code necessary to replicate all main results,
-# including the descriptive statistics, meta-analysis, and meta-regressions.
-# 
-# Last successful replication: 01.11.2021
-# 
-# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
-
-# first things first: set your settings.
-
-rm(list=ls())
-#setwd("raw/data") #set your directory
-options("scipen"=100, "digits"=8) #set digits
-getwd()
-
-
-###### Install and load packages ###### 
-
-# ipak function: install and load multiple R packages.
-# check to see if packages are installed. Install them if they are not, then load them into the R session.
-
-ipak <- function(pkg){  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
-if(length(new.pkg)) install.packages(new.pkg, dependencies = TRUE)
-sapply(pkg, require, character.only = TRUE)
-}
-
-packages <- c("readxl", "haven", "psych", "dplyr", "DescTools", "broom", "cowplot",
-              "pwr", "esc", "metaSEM", "metafor", "metaviz", "PerformanceAnalytics", 
-              "ggplot2", "ggpubr", "wesanderson", "stringr", "dotwhisker") 
-ipak(packages)
-
-
-###### Import and split data ###### 
-
-dat <- read_excel("/cloud/project/raw/data/02-metaanalysis-data.xlsx", sheet = "Data", 
-                  col_names = TRUE, skip = 3)
-
-### dataframe of studies
-dat_studies <- dat[c(1:87)] #studies.
-dat_studies <- group_by(dat_studies, ID_RS) %>% slice(1)
[…]

### 2024-02-15 outputs/Table2_calculations/Table2_calculation.qmd
code for table 2

--- 2024-02-13 raw/data/123.qmd
@@
 ```{r}
-#| label: fig-collection1
-#| fig-cap: "00000000000000000000000000000000000000000000000000000000000000000000000000"
-#| echo: false
-#| message: false
-#| warning: false
-
-rm(list=ls())
-setwd("/cloud/project/raw/data") #set your directory
-options("scipen"=100, "digits"=8) #set digits
-getwd()
-
-ipak <- function(pkg){  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
-if(length(new.pkg)) install.packages(new.pkg, dependencies = TRUE)
-sapply(pkg, require, character.only = TRUE)
-}
-
-packages <- c("readxl", "haven", "psych", "dplyr", "DescTools", "broom", "cowplot",
-              "pwr", "esc", "metaSEM", "metafor", "metaviz", "PerformanceAnalytics", 
-              "ggplot2", "ggpubr", "wesanderson", "stringr", "dotwhisker") 
-ipak(packages)
-
-dat <- read_excel("/cloud/project/raw/data/02-metaanalysis-data.xlsx", sheet = "Data", 
-                  col_names = TRUE, skip = 3)
-
-### dataframe of studies
-dat_studies <- dat[c(1:87)] #studies.
-dat_studies <- group_by(dat_studies, ID_RS) %>% slice(1)
-sum(dat_studies$ESS, na.rm = TRUE) #number of unique respondents
-
-### dataframe of reports
-dat_reports <- dat[c(1:87)] #reports/publications.
-dat_reports <- group_by(dat_reports, ID_R) %>% slice(1)
-
-### set wished layout settings
-mytheme <- theme(plot.title = element_text(face = "bold", size = (22), colour = "black"), 
-                 axis.text = element_text(size = (18), colour = "black"),
-                 axis.ticks.length = unit(0.5, "cm"),
-                 axis.title.y = element_text(size = (22), colour = "black"),
-                 axis.title.x = element_text(size = (22), colour = "white"))
-
-# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
-###### A. DESCRIPTIVES: THE FIELD OF EMPIRICAL TERRORISM STUDIES ######
-# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ #
-
-## mean ES's per report (reported in footnote 6)
-format(round(psych::describe(aggregate(Correlation ~ ID_R, data = dat, FUN = length)),3), nsmall=3)
-
-StudyYear <- ggplot(dat_studies, aes(x=StudyYear)) + 
-  geom_histogram(binwidth=1,
-                 color="#000000", fill="#939598") +
-  labs(x="to fill some space", y = "", title = "Year of Data Collection") +
-  scale_y_continuous(breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45)) +
-  scale_x_continuous(breaks = c(1985,1990,1995,2000,2005,2010, 2015,2020)) +
-  theme_classic() #histogram year of study 
-StudyYear <- StudyYear + geom_vline(xintercept=2001, linetype="dashed", size = 1) #add 9/11 line
-StudyYear <- StudyYear + geom_vline(xintercept=2004, linetype="dashed", size = 1) #add line
-StudyYear <- StudyYear + geom_vline(xintercept=2015, linetype="dashed", size = 1) #add ISIS line
-StudyYear <- StudyYear + geom_label(data = dat_studies, 
-                                    aes(x=2001, y=27, label = "9/11"),
-                                    size=8) #add 9/11 label
-StudyYear <- StudyYear + geom_label(data = dat_studies, 
-                                    aes(x=2007, y=35, label = "Madrid & \n Israel-Palestine"),
-                                    size=6) #add label
-StudyYear <- StudyYear + geom_label(data = dat_studies, 
-                                    aes(x=2014, y=44, label = "IS Attacks"),
-                                    size=8) #add ISIS label
-StudyYear <- StudyYear + mytheme
-
-# year of publication
-
-describe(dat_reports$Year) 
-# Figure 2B
-PubYear <- ggplot(dat_reports, aes(x=Year)) + 
-  geom_histogram(binwidth=1, 
-                 color="#000000", fill="#939598") +
-  labs(title ="Year of Publication", x = "to fill some space", y = "") +
-  scale_y_continuous(breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45)) +
-  scale_x_continuous(breaks = c(1985,1990,1995,2000,2005,2010, 2015,2020)) +
-  theme_classic() #histogram year of study 
-PubYear <- PubYear + geom_vline(xintercept=2001, linetype="dashed", size = 1) #add 9/11 line
-PubYear <- PubYear + geom_vline(xintercept=2015, linetype="dashed", size = 1) #add ISIS France line
-PubYear <- PubYear + geom_label(data = dat_reports,
-                                aes(x=2001, y=27, label = "9/11"),
-                                size=8) #add 9/11 label
-PubYear <- PubYear + geom_label(data = dat_reports, 
-                                aes(x=2014, y=44, label = "IS Attacks"),
-                                size=8) #add ISIS label
-PubYear <- PubYear + mytheme
-
-####### Terrorism measures, incl. cognitive and affective reactions ######
-
-# IV measurements used 
-summary(as.factor(dat$IV_Code))
-
-#wrangling
-dat$TerrorMeasure[dat$IV_Code==1] <- "Acts of violence"
-dat$TerrorMeasure[dat$IV_Code==2] <- "Acts of violence"
-dat$TerrorMeasure[dat$IV_Code==3] <- "Threat"
-dat$TerrorMeasure[dat$IV_Code==4] <- "Threat"
-dat$TerrorMeasure[dat$IV_Code==5] <- "Other"
-dat$TerrorMeasure[dat$IV_Code==6] <- "Reported exposure"
-dat$TerrorMeasure[dat$IV_Code==7] <- "Reported exposure"
-dat$TerrorMeasure[dat$IV_Code==8] <- "Reported exposure"
-dat$TerrorMeasure[dat$IV_Code==9] <- "Threat"
-dat$TerrorMeasure[dat$IV_Code==10] <- "Threat"
-dat$TerrorMeasure[dat$IV_Code==11] <- "Fear"
-dat$TerrorMeasure[dat$IV_Code==12] <- "Anger"
-dat$TerrorMeasure[dat$IV_Code==13] <- "Other"
-dat$TerrorMeasure[dat$IV_Code==14] <- "Other"
-dat$TerrorMeasure[dat$IV_Code==15] <- "Other"
-dat$TerrorMeasure[dat$IV_Code==16] <- "Other"
-
-dat$TerrorMeasure <- as.factor(dat$TerrorMeasure)
-table(dat$TerrorMeasure)
-prop.table(table(dat$TerrorMeasure))
-table(dat$ExactAttack) #which attacks are studied?
-prop.table(table(dat$ExactAttack)) #which attacks are studied?
-
-#visualization: Figure 2C
-tmdat <- data.frame(prop.table(table(dat$TerrorMeasure)))
-TerrorMeasures <- ggplot(tmdat, aes(x = reorder(Var1, -Freq), y = Freq)) +
-  geom_bar(stat="identity", width=0.7,
-           color="#000000", fill="#939598") +
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
-  scale_y_continuous(labels = scales::percent,
-                     limits = c(0,.6),
-                     breaks = c(0,.1,.2,.3,.4,.5,.6)) +
-  labs(title = "Terrorism Measures", x="", y = "") +
-  theme_classic() 
-TerrorMeasures <- TerrorMeasures + mytheme
-
-# type of terrorism
-summary(as.factor(dat$Type))
-
-#wrangling
-dat$TerrorType[dat$Type==0] <- "No ideology"
-dat$TerrorType[dat$Type==1] <- "Islamist"
-dat$TerrorType[dat$Type==2] <- "Extreme right"
-dat$TerrorType[dat$Type==3] <- "Other"
-dat$TerrorType[dat$Type==4] <- "Other"
-dat$TerrorType[dat$Type==5] <- "State terror"
-dat$TerrorType[dat$Type==6] <- "Other"
-dat$TerrorType <- as.factor(dat$TerrorType)
-summary(dat$TerrorType)
-prop.table(table(dat$TerrorType))
-
-#visualization: Figure 2D
-ttdat <- data.frame(prop.table(table(dat$TerrorType)))
-TerrorType <- ggplot(ttdat, aes(x = reorder(Var1, -Freq), y = Freq)) +
-  geom_bar(stat="identity", width=0.7,
-           color="#000000", fill="#939598") +
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
-  scale_y_continuous(labels = scales::percent,
-                     breaks = c(0,.1,.2,.3,.4,.5,.6)) +
-  labs(title = "Type of Terrorism", x = "", y = "") +
-  theme_classic() 
-TerrorType <- TerrorType + mytheme
-
-jpeg("Figures/Fig2.jpeg", width = 15, height = 16, units = 'in', res = 300)
-ggarrange(StudyYear, PubYear, 
-          TerrorMeasures, TerrorType,
-          labels = c("(A)", "(B)", "(C)", "(D)"),
-          font.label = list(size = 22, color = "black"),
-          ncol = 2, nrow = 2) #arrange all plots
-dev.off() #safe picture in high resolution.
-```
-
-```{r}
-#| label: fig-collection
-#| fig-cap: "00000000000000000000000000000000000000000000000000000000"
-#| echo: false
-#| message: false
-#| warning: false
-
-# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
-######## B. META-ANALYSIS: for each of the hypotheses ######## 
-# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ #
-
-# Data preparation: Split dataset in 3 based on outcome type
-# 1) outgroup dataset
-
-dat <- read_excel("/cloud/project/raw/data/02-metaanalysis-data.xlsx", sheet = "Data", 
-                  col_names = TRUE, skip = 3)
-
-dat_outgroup <- dat[dat$PA_Category == 10 |
-                      dat$PA_Category == 99, ]
-length(unique(dat_outgroup$ID_R))#number of manuscripts (N_j)
-# 2) conservative shift dataset
-dat_conservatism <- dat[dat$PA_Category == 5 |
-                          dat$PA_Category == 6 |
-                          dat$PA_Category == 7 |
-                          dat$PA_Category == 8 |
-                          dat$PA_Category == 9 |
-                          dat$PA_Category == 11, ]
-length(unique(dat_conservatism$ID_R))#number of manuscripts (N_j)
-# 3) rally-around-the-flag dataset
-dat_rally <- dat[dat$PA_Category == 1 |
-                   dat$PA_Category == 2 |
-                   dat$PA_Category == 3 |
-                   dat$PA_Category == 4, ]
-length(unique(dat_rally$ID_R))#number of manuscripts (N_j)
-# double check (total number of effect sizes; N_k)
-count(dat_outgroup) + count(dat_conservatism) + count(dat_rally)
-
-##### 1. Fit empty 3-level model using the meta3L function #####
-
-### To replicate Table 2: call summary() function for each of outcome cluster
-      ## coef(model...)[1] = Fishers' Z correlation coefficients (Zr)
-### To replicate the correlation coefficients mentioned in the text, 
-### call the FisherZinv() function for each outcome cluster.
-
-# Outgroup hostility (Table 2)
-set.seed(1234)
-model_og_LBCI <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
-                       data = dat_outgroup, 
-                       I2=c("I2q", "ICC"),
-                       intervals.type = "LB",
-                       model.name = "3 level outgroup LB")
-summary(model_og_LBCI)#results presented in Table 2, as well as
-#throughout the Supplementary Information (esp. Table B.3).
-FisherZInv(coef(model_og_LBCI)[1])#rho reported in text
-
-# Conservative shift (Table 2)
-set.seed(1234)
-model_cs_LBCI <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
-                       data = dat_conservatism, 
-                       I2=c("I2q", "ICC"),
-                       intervals.type = "LB",
-                       model.name = "3 level conservatism LB")
-summary(model_cs_LBCI)#results presented in Table 2, as well as
-#throughout the Supplementary Information (esp. Table B.3).
-FisherZInv(coef(model_cs_LBCI)[1])#rho reported in text
-
-# Rally-around-the-flag (Table 2)
-set.seed(1234)
-model_rf_LBCI <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
-                       data = dat_rally, 
-                       I2=c("I2q", "ICC"),
-                       intervals.type = "LB",
-                       model.name = "3 level rally LB")
-summary(model_rf_LBCI)#results presented in Table 2, as well as
-#throughout the Supplementary Information (esp. Table B.3).
-FisherZInv(coef(model_rf_LBCI)[1])#rho reported in text
-
-## Substantive interpretation --------------------------------------------------
-## i.e., comparison to 2016 ANES Feeling Thermometers
-anes2016 <- read_dta(file = "/cloud/project/raw/data/anes_timeseries_2016.dta")
-#select variables to summarize
-anes2016 <- anes2016 %>%
-  select(immterm = V162313, 
-         reptherm = V161096) 
-#format(round(psych::describe(anes2016),3), nsmall=3): counts NA's
-#recode NA's (!)
-anes2016$immterm <- ifelse(anes2016$immterm %in% -9:-1, NA, 
-                           identity(anes2016$immterm)) 
-anes2016$reptherm <- ifelse(anes2016$reptherm %in% -99:-1, NA, 
-                            identity(anes2016$reptherm))
-#find correct SDs to use in calculations based on Paluck et al. (2021)
-format(round(psych::describe(anes2016),3), nsmall=3) 
-#the effect of terror on the feeling therm. toward immigrants. 6.9
-cohens_d(r = FisherZInv(coef(model_og_LBCI)[1]))*27.285 
-#the effect of terror on the feeling therm. toward Rep. party: 7.2
-cohens_d(r = FisherZInv(coef(model_cs_LBCI)[1]))*27.330
-
-## Practical implication -------------------------------------------------------
-## i.e., what sample size is recommended based on this meta-analysis?
-# Outgroup hostility
-pwr.r.test(r = FisherZInv(coef(model_og_LBCI)[1]), sig.level = 0.05, power = 0.8) 
-# Conservative shift
-pwr.r.test(r = FisherZInv(coef(model_cs_LBCI)[1]), sig.level = 0.05, power = 0.8) 
-# Rally-around-the-flag
-pwr.r.test(r = FisherZInv(coef(model_rf_LBCI)[1]), sig.level = 0.05, power = 0.8)
-
-```
-
-```{r}
-
-```{r}
-#| label: fig-collection1
-#| fig-cap: "000000000000000000000000000000000000000000000000000000000000"
 #| echo: false
@@
 ```
-```

### 2024-02-15 scripts/00-simulation.R
Simulation

@@ -1,0 +1,121 @@
+#### Preamble ####
+# Purpose: Simulating data on survery results 
+# Authors: Zheng(Zeb) Yang, Jingcheng Yang, Bernice(Yixuan) Bao
+# Contact: zhengzeb.yang@mail.utoronto.ca, jingcheng.yang@mail.utoronto.ca, bernice.bao@mail.utoronto.ca
+# Pre-requisites: -
+
+library(here)
+library(readr)
+
+set.seed(812)
+
+
+Author <- sample(c('Aber et al.','Abrams et al.', 'Aizpurua et al..', 
+                   'Anonymous', 'Argyrides & Downey', 'Arian',
+                   'Arvanitidis, Economou, & Kollias', 'Asbrock & Fritsche', 
+                   'Aytac & Carkoglu'), size = 100, replace = TRUE)
+
+
+year <- sample(c(1989,2019), size = 100, replace = TRUE)
+
+TypeReport <- sample(c(x = 1:4), size = 100, replace = TRUE)
+
+ImpactFactor <- runif(100, 0, 3)
+
+Theory_A <- sample(c('ITT','TMT', 'Us vs Them', 'People Apart Syndrome', 'RWA', 'Conservative shift'), size = 100, replace = TRUE)
+
+Theory_B <- sample(c('Contact theory','Group-threat', 'Leadership and Competence'), size = 100, replace = TRUE)
+
+Theory_C <- sample(c('Rally-around-the-flag','Issue Ownership; TMT'), size = 100, replace = TRUE)
+
+Hypotheses <- sample(c(0,1), size = 100, replace = TRUE)
+
+Definition <- sample(c(0,1), size = 100, replace = TRUE)
+
+ID_S <- sample(c(0,1), size = 100, replace = TRUE)
+
+ID_RS <- sample(c(100011:100881), size = 100, replace = TRUE)
+
+Preregistration <- sample(c(0,1), size = 100, replace = TRUE)
+
+TypeStudy <- sample(c(x = 1:4), size = 100, replace = TRUE)
+
+Country <- sample(c('US', 'Israel', 'Spain', 'Norway', 'Belgium', 'France', 'Germany', 'Turkey'), size = 100, replace = TRUE)
+
+StudyYear <- sample(c(1988,2019), size = 100, replace = TRUE)
+
+SampleSize <- sample(c(x = 99:1500), size = 100, replace = TRUE)
+
+GeneralPop <- sample(c(0,1), size = 100, replace = TRUE)
+
[…]

### 2024-02-15 scripts/00-simulation.R
simulation and tests

@@ -16,7 +16,7 @@ Author <- sample(c('Aber et al.','Abrams et al.', 'Aizpurua et al..',
                    'Aytac & Carkoglu'), size = 100, replace = TRUE)
 
 
-year <- sample(c(1989,2019), size = 100, replace = TRUE)
+year <- sample(c(1989:2019), size = 100, replace = TRUE)
 
 TypeReport <- sample(c(x = 1:4), size = 100, replace = TRUE)
 
@@ -42,7 +42,7 @@ TypeStudy <- sample(c(x = 1:4), size = 100, replace = TRUE)
 
 Country <- sample(c('US', 'Israel', 'Spain', 'Norway', 'Belgium', 'France', 'Germany', 'Turkey'), size = 100, replace = TRUE)
 
-StudyYear <- sample(c(1988,2019), size = 100, replace = TRUE)
+StudyYear <- sample(c(1988:2019), size = 100, replace = TRUE)
 
 SampleSize <- sample(c(x = 99:1500), size = 100, replace = TRUE)
 

### 2024-02-15 scripts/01-test.R

@@ -1,0 +1,20 @@
+#### Preamble ####
+# Purpose: Testing simulated data
+# Authors: Zheng(Zeb) Yang, Jingcheng Yang, Bernice(Yixuan) Bao
+# Contact: zhengzeb.yang@mail.utoronto.ca, jingcheng.yang@mail.utoronto.ca, bernice.bao@mail.utoronto.ca
+# Pre-requisites: -
+
+# read in simulation file
+sim <- read_csv(here::here("inputs/data/sim.csv"), 
+                       show_col_types = FALSE)
+
+
+min(sim$year, na.rm=TRUE) > 0
+
+
+max(sim$year, na.rm=TRUE) <= 2019
+
+
+sim$SampleSize |> min() >= 0
+
+sim$StudyYear |> max() <= 2019

### 2024-02-15 outputs/paper/paper.qmd
edits

@@
 ---
-title: "Start with the literature: assessthe empirical evidence for the relationship between ter-rorism and political attitudes"
+title: "Start with the literature: assess the empirical evidence for the relationship between terrorism and political attitudes"
 author: "Bernice(Yixuan) Bao, Zheng(Zeb) Yang, Jingcheng Yang"
